### 2011-05-05 doc/paper.tex
Program summary written

%% This template can be used to write a paper for
%% Computer Physics Communications using LaTeX.
%% For authors who want to write a computer program description,
%% an example Program Summary is included that only has to be
%% completed and which will give the correct layout in the
%% preprint and the journal.
%% The `elsarticle' style is used and more information on this style
%% can be found at 
%% http://www.elsevier.com/wps/find/authorsview.authors/elsarticle.
%%
%%
\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

%% This list environment is used for the references in the
%% Program Summary
%%
\newcounter{bla}
\newenvironment{refnummer}{%
\list{[\arabic{bla}]}%
{\usecounter{bla}%
 \setlength{\itemindent}{0pt}%
 \setlength{\topsep}{0pt}%
 \setlength{\itemsep}{0pt}%
 \setlength{\labelsep}{2pt}%
 \setlength{\listparindent}{0pt}%
 \settowidth{\labelwidth}{[9]}%
 \setlength{\leftmargin}{\labelwidth}%
 \addtolength{\leftmargin}{\labelsep}%
 \setlength{\rightmargin}{0pt}}}
 {\endlist}

\journal{Computer Physics Communications}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[a,b]{Anton Nazarov\corref{author}}
%\author[a,b]{Second Author}
%\author[b]{Third Author}

\cortext[author] {Corresponding author.\\\textit{E-mail address:} antonnaz@gmail.com}
\address[a]{Department of High Energy Physics, Faculty of physics, SPb State University\\ 198904, Sankt-Petersburg, Russia}
\address[b]{Chebyshev Laboratory, Faculty of Mathematics and Mechanics, SPb State University\\ 199178, Saint-Petersburg, Russia}

\begin{abstract}
%% Text of abstract
We present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras. Algorithms are based upon the properties of weights and Weyl symmetry. Central problems are weight multiplicity computation, branching of representation to representations of subalgebra and tensor product decomposition. These problems has numerous applications in physics.

Unique features of our programs are the treatment of affine Lie algebras and implementation in popular computer algebra system {\it Mathematica}.

% A submitted program is expected to be of benefit to other physicists or physical chemists, or be an exemplar of good programming practice, or illustrate new or novel programming techniques which are of importance to some branch of computational physics or physical chemistry.
%
% Acceptable program descriptions can take different forms. The following Long Write-Up structure is a suggested structure but it is not obligatory. Actual structure will depend on the length of the program, the extent to which the algorithms or software have already been described in literature, and the detail provided in the user manual.

%Your manuscript and figure sources should be submitted through the Elsevier Editorial System (EES) by using the online submission tool at \\
% http://www.ees.elsevier.com/cpc.

%In addition to the manuscript you must supply: the program source code; job control scripts, where applicable; a README file giving the names and a brief description of all the files that make up the package and clear instructions on the installation and execution of the program; sample input and output data for at least one comprehensive test run; and, where appropriate, a user manual. These should be sent, via email as a compressed archive file, to the CPC Program Librarian at cpc@qub.ac.uk.

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
%keyword1; keyword2; keyword3; etc.

Mathematica; Lie algebra; affine Lie algebra; Kac-Moody algebra; root system; weights; irreducible modules, CFT, Integrable systems
\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

% Computer program descriptions should contain the following
% PROGRAM SUMMARY.

{\bf PROGRAM SUMMARY}%/NEW VERSION PROGRAM SUMMARY}
  %Delete as appropriate.

\begin{small}
\noindent
{\em Manuscript Title:}{\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of finite-dimensional and affine Lie algebras                                       \\
{\em Authors:}Anton Nazarov                                                \\
{\em Program Title:}Affine.m                                          \\
{\em Journal Reference:}                                      \\
  %Leave blank, supplied by Elsevier.
{\em Catalogue identifier:}                                   \\
  %Leave blank, supplied by Elsevier.
{\em Licensing provisions:}none                                   \\
  %enter "none" if CPC non-profit use license is sufficient.
{\em Programming language:}Mathematica                                   \\
{\em Computer:}i386-i686, x86\textunderscore 64                                               \\
  %Computer(s) for which program has been designed.
{\em Operating system:} Linux, Windows, MacOS, Solaris                                       \\
  %Operating system(s) for which program has been designed.
{\em RAM:} 5-500 Mb                                              \\
  %RAM in bytes required to execute program with typical data.
%{\em Number of processors used:}                              \\
  %If more than one processor.
%{\em Supplementary material:}                                 \\
  % Fill in if necessary, otherwise leave out.
{\em Keywords:} Mathematica; Lie algebra; affine Lie algebra; Kac-Moody algebra; root system; weights; irreducible modules, CFT, Integrable systems\\
  % Please give some freely chosen keywords that we can use in a
  % cumulative keyword index.
{\em Classification:} 5 Computer Algebra, 4.2 Other algebras and groups                                         \\
  %Classify using CPC Program Library Subject Index, see (
  % http://cpc.cs.qub.ac.uk/subjectIndex/SUBJECT_index.html)
  %e.g. 4.4 Feynman diagrams, 5 Computer Algebra.
%{\em External routines/libraries:}                            \\
  % Fill in if necessary, otherwise leave out.
%{\em Subprograms used:}                                       \\
  %Fill in if necessary, otherwise leave out.
%{\em Catalogue identifier of previous version:}*              \\
  %Only required for a New Version summary, otherwise leave out.
%{\em Journal reference of previous version:}*                  \\
  %Only required for a New Version summary, otherwise leave out.
%{\em Does the new version supersede the previous version?:}*   \\
  %Only required for a New Version summary, otherwise leave out.
{\em Nature of problem:}\\
  %Describe the nature of the problem here.
Representation theory of finite-dimensional Lie algebras has many applications in different branches of physics, including elementary particle physics, molecular physics, nuclear physics. Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory which is used for the description of critical phenomena in two-dimensional systems. Also Lie symmetries play major role in study of quantum integrable systems. 
   \\
{\em Solution method:}\\
  %Describe the method solution here.
We work with weights and roots of finite-dimensional and affine Lie algebras and use Weyl symmetry extensively. Central problems which are the computations of weight multiplicities, branching and fusion coefficients are solved using one general recurrent algorithm based on generalization of Weyl character formula. We also offer alternative implementation based on Freudenthal multiplicity formula which can be faster in some cases. 
   \\
%{\em Reasons for the new version:}*\\
  %Only required for a New Version summary, otherwise leave out.
%   \\
%{\em Summary of revisions:}*\\
  %Only required for a New Version summary, otherwise leave out.
%   \\
{\em Restrictions:}\\
  %Describe any restrictions on the complexity of the problem here.
Computational complexity grows fast  with the rank of algebra, so computations for algebra of rank greater than 8 are non practical. 
   \\
{\em Unusual features:}\\
  %Describe any unusual features of the program/problem here.
We offer the possibility to use traditional mathematical notation for objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in {\it Mathematica} notebook interface. 
   \\
%{\em Additional comments:}\\
  %Provide any additional comments here.
%   \\
{\em Running time:}\\
  %Give an indication of the typical running time here.
From seconds to days depending on rank of algebra and complexity of representations.
   \\

% \begin{thebibliography}{0}
% \bibitem{1}Reference 1         % This list should only contain those items referenced in the                 
% \bibitem{2}Reference 2         % Program Summary section.   
% \bibitem{3}Reference 3         % Type references in text as [1], [2], etc.
%                                % This list is different from the bibliography at the end of 
%                                % the Long Write-Up.
% \end{thebibliography}
% * Items marked with an asterisk are only required for new versions
% of programs previously published in the CPC Program Library.\\
\end{small}

%% main text
\section{Introduction}
\label{intro}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}         ==>>  [#]
%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

%% References with bibTeX database:

\bibliographystyle{elsarticle-num}
\bibliography{bibliography}

%% Authors are advised to submit their bibtex database files. They are
%% requested to list a bibtex style file in the manuscript if they do
%% not want to use elsarticle-num.bst.

%% References without bibTeX database:

% \begin{thebibliography}{00}

%% \bibitem must have the following form:
%%   \bibitem{key}...
%%

% \bibitem{}

% \end{thebibliography}

\end{document}

%%
%% End of file

### 2011-05-05 tests/debug.m
Paths

@@ -1,6 +1,127 @@
-AppendTo[$Path,"/home/anton/study/2011/Articles/AffineLieAlgebras/Mathematica/"];
+AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
-<<datastructures.m;
+<<affine.m;
+
+$Path
+
+Out[16]= {/opt/mathematica8/SystemFiles/Links, 
+ 
+>    /home/anton/.Mathematica/Kernel, /home/anton/.Mathematica/Autoload, 
+ 
+>    /home/anton/.Mathematica/Applications, /usr/share/Mathematica/Kernel, 
+ 
+>    /usr/share/Mathematica/Autoload, /usr/share/Mathematica/Applications, ., 
+ 
+>    /home/anton, /opt/mathematica8/AddOns/Packages, 
+ 
+>    /opt/mathematica8/AddOns/LegacyPackages, 
+ 
+>    /opt/mathematica8/SystemFiles/Autoload, 
+ 
+>    /opt/mathematica8/AddOns/Autoload, 
+ 
+>    /opt/mathematica8/AddOns/Applications, 
+ 
+>    /opt/mathematica8/AddOns/ExtraPackages, 
+ 
+>    /opt/mathematica8/SystemFiles/Kernel/Packages, 
+ 
+>    /opt/mathematica8/Documentation/English/System, 
+ 
+>    /home/anton/programing/Affine/tests../src/, 
+ 
+>    /home/anton/programing/Affine/tests/../src/}
+
+Out[13]= {/opt/mathematica8/SystemFiles/Links, 
+ 
+>    /home/anton/.Mathematica/Kernel, /home/anton/.Mathematica/Autoload, 
+ 
+>    /home/anton/.Mathematica/Applications, /usr/share/Mathematica/Kernel, 
+ 
+>    /usr/share/Mathematica/Autoload, /usr/share/Mathematica/Applications, ., 
+ 
+>    /home/anton, /opt/mathematica8/AddOns/Packages, 
+ 
+>    /opt/mathematica8/AddOns/LegacyPackages, 
+ 
+>    /opt/mathematica8/SystemFiles/Autoload, 
+ 
+>    /opt/mathematica8/AddOns/Autoload, 
+ 
+>    /opt/mathematica8/AddOns/Applications, 
+ 
+>    /opt/mathematica8/AddOns/ExtraPackages, 
+ 
+>    /opt/mathematica8/SystemFiles/Kernel/Packages, 
+ 
[…]

### 2011-05-06 doc/paper.tex
Introduction typed down.

@@
 %% use the graphics package for simple commands
-%% \usepackage{graphics}
+\usepackage{graphics}
+\usepackage{hyperref}
 %% or use the graphicx package for more complicated commands
@@
 
+Representation theory of Lie algebras is of central importance for different areas of physics and mathematics.
+Lie algebras are used to for the description of symmetries of quantum and classical systems.
+Computational method in representation theory have long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
+
+Most popular programs \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{fischbacher2002ilp}, \cite{coxweyl} are created to study representation theory of simple finite-dimensional Lie algebras.
+The main computational problems are the following:
+\begin{enumerate}
+\item Construction of root system which is used for compact description of algebra commutation relations.
+\item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
+\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for the construction and study of representations. 
+\end{enumerate}
+There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}. 
+The third problem is most computation-intensive.
+There are two different recurrent algorithms which are based on Weyl character formula and Freudenthal multiplicity formula.
+In this paper we analyze them.
+
+Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and study of quantum integrable systems.
+But infinite-dimensional algebras are much harder to study and quantity of available computer programs is much smaller.
+
+Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras.
+They are constructed as the central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in the study of Wess-Zumino-Witten and coset models of conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
+
+Construction of affine Lie algebras allows to extend computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
+The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of algebras and representations was published in 1990.
+But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
+We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
+
+Our package can be used for study of root and weight systems, Weyl groups, subalgebras, computations of weight multiplicities, branching and fusion coefficients.
+We describe the features and limitations of the package in present paper and in the manual \cite{affinemanual}.
+In present paper we also provide representation-theoretical background of implemented algorithms and present some example of computations relevant to physics.
+
+The paper is started with overview of Lie algebras and their representation theory (Sec.
+\ref{sec:theor-backgr}).
+Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and their representations (Sec.
+\ref{sec:core-datastructures} and used in implemented algorithms (Sec.
+\ref{sec:comp-algor}).
+Next section consists of physically interesting examples (Sec.
+\ref{sec:examples}).
+The paper is concluded with the discussion of possible extensions and refinements (Sec.
+\ref{sec:conclusion}).
+
+\section{Theoretical background}
+\label{sec:theor-backgr}
+
+\section{Core datastructures}
+\label{sec:core-datastructures}
+
+\section{Computational algorithms}
+\label{sec:comp-algor}
+
+\section{Examples}
+\label{sec:examples}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
 %% The Appendices part is started with the command \appendix;

### 2011-05-06 doc/paper.tex
Some theory

@@
 % \biboptions{}
+\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
+\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
+\newcommand{\co}[1]{\stackrel{\circ }{#1}}
+\newcommand{\pia}{\pi_{\mathfrak{a}}}
+\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
+\newcommand{\gf}{\mathfrak{g}}
+\newcommand{\af}{\mathfrak{a}}
+\newcommand{\afb}{\mathfrak{a}_{\bot}}
+\newcommand{\hf}{\mathfrak{h}}
+\newcommand{\hfg}{\hf_{\gf}}
+\newcommand{\hfb}{\mathfrak{h}_{\bot}}
 
@@
 
+\subsection{Lie algebras of finite and affine type}
+\label{sec:lie-algebras-finite}
+
+Lie algebra $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called commutator.
+If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the structure constants $C_{ijk}$:
+\begin{equation}
+  \label{eq:1}
+  [X_{i},X_{j}]=\sum_{k} C_{ijk} X_{k}
+\end{equation}
+Lie algebra is simple if it contains no non-trivial ideals. Semisimple Lie algebra is a direct sum of simple Lie algebras.
+
+Maximal commutative subalgebra (Cartan subalgebra) of $\gf$ is denoted by $\hfg$. Killing form gives non-degenerate bilinear form on $\hfg$.
+
+Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
+This basis can be encoded by the root system  which is the set of vectors in Euclidean vector space $\hfg^{*}$ satisfying certain properties (See e.g.
+\cite{humphreys1997introduction,humphreys1992reflection} for details).
+
 \section{Core datastructures}

### 2011-05-07 doc/paper.tex
More work on theoretical background

@@
 %% The amssymb package provides various useful mathematical symbols
+\usepackage{amsmath}
 \usepackage{amssymb}
@@
   \label{eq:1}
-  [X_{i},X_{j}]=\sum_{k} C_{ijk} X_{k}
+  [X^{i},X^{j}]=\sum_{k} C^{ij}_{k} X^{k}
 \end{equation}
@@
 
-Maximal commutative subalgebra (Cartan subalgebra) of $\gf$ is denoted by $\hfg$. Killing form gives non-degenerate bilinear form on $\hfg$.
+Maximal commutative subalgebra (Cartan subalgebra) of $\gf$ is denoted by $\hfg$.
+We denote the elements of basis of $\hfg$ by $H^{i}$.
+
+Killing form gives non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be extended to the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
+Weights are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
 
 Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
-This basis can be encoded by the root system  which is the set of vectors in Euclidean vector space $\hfg^{*}$ satisfying certain properties (See e.g.
+This basis can be encoded by the root system  which is the set of vectors in  $\hfg^{*}$ satisfying certain properties (See e.g.
 \cite{humphreys1997introduction,humphreys1992reflection} for details).
+
+Loop algebra $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$ has commutation relations
+\begin{equation}
+  \label{eq:6}
+  [X^{i}t^{n},X^{j}t^{m}]=t^{n_+m}\sum_{k}C^{ij}_{k}X^{k}
+\end{equation}
+Central extension leads to the appearance of additional term in commutation relations
+\begin{equation}
+  \label{eq:7}
+   [X^{i}t^{n}+\alpha c,X^{j}t^{m}+\beta c]=t^{n+m}\sum_{k}C^{ij}_{k}X^{k}+(X^{i},X^{j})n\delta_{n+m,0}c
+\end{equation}
+This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+
+\subsection{Weights and roots}
+\label{sec:weights-roots}
+
+Let $\gf$ be finite-dimensional or affine Lie algebra.
+
+Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
+\begin{equation}
+  \label{eq:2}
+  [x,y]\cdot v = x\cdot(y\cdot v) - y\cdot(x\cdot v), \quad \mbox{for}\; x,y\in \gf, v\in V
+\end{equation}
+Representation of algebra $\gf$ on vector space $V$ is the homomorphism $\gf\to gl(V)$.
+
+For an arbitrary representation it is possible to diagonalize Cartan generators $H^{i}$ simultaneously by special choice of basis $\left\{\left|j\right>\right\}$ in $V$:
+\begin{equation}
+  \label{eq:3}
+  H^{i}\left|j\right>=\nu_{j}^{i}\left|j\right>
+\end{equation}
+Eigenvalues of Cartan generators on element of basis $\left|j\right>$ are given by weight $\nu_{j}\in \hfg^{*}: \nu_{j}(H^{i})=\nu_{j}^{i}$, correspondingly vector $\left|j\right>$ is called weight vector of $\nu_{j}$.
+
+Roots are weights of adjoint representation of $\gf$ on itself.
+They encode the commutation relations of algebra in the following way.
+Denote by $\Delta$ the set of roots.
+For each $\alpha\in \Delta$ there exist root $-\alpha\in \Delta$ and generators $E^{\alpha}, E^{-\alpha}$ such that
+\begin{align}
+  \label{eq:4}
+  &  [H^{i},E^{\alpha}]=\alpha^{i}E^{\alpha} \\
+  &\left[E^{\alpha},E^{\beta}\right]=
+  \begin{cases} 
+    N_{\alpha,\beta} E^{\alpha+\beta}, & \mbox{if}\; \alpha+\beta\in \Delta\\
+    \frac{2}{(\alpha,\alpha)} \sum_{i}\alpha^{i} H^{i},&  \mbox{if}\; \alpha=-\beta\\
+    0,&\mbox{otherwise}
+  \end{cases}
+\end{align}
+
+The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+\begin{equation}
+  \label{eq:5}
+  E^{\alpha}\left|\nu\right> \propto \left|\nu+\alpha\right>
+\end{equation}
+
+In the root system $\Delta$ exist simple roots $\left\{\alpha_{i}\right\}$, such that $\alpha=\sum_{i}n_{i}\alpha_{i},\; \forall\alpha\in \Delta$.
+In case of finite-dimensional Lie algebra $\gf$ $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+Although the full set of roots $\Delta$ is infinite for affine Lie algebra $\hat\gf$ the number of simple roots is finite and are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+Roots system can be reconstructed from the set of simple roots with the use of Weyl group $W_{\gf}$ which is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
+\begin{equation}
+  \label{eq:8}
+  s_{i}\cdot\lambda=\lambda-\frac{2(\alpha_{i},\lambda)}{(\alpha_{i},\alpha_{i})}\alpha_{i}
+\end{equation}
+Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
+In the latter case of $\hat\gf$ Weyl group can be presented as semidirect product of Weyl group $W_{\gf}$ of $\gf$ and translations by the roots of $\hat \gf$.
+
+Fundamental domain $\bar{C}$ for the action of Weyl group $W_{\gf}$ on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
+It is called {\it main Weyl chamber}.
+
+Cartan matrix $A$ is defined by products of simple roots
+\begin{equation}
+  \label{eq:9}
+  A_{ij}=\frac{2(\alpha_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}
+\end{equation}
+and can be used for compact description of Lie algebra commutation relations in Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+\subsection{Highest weight modules}
+\label{sec:high-weight-modul}
 

### 2011-05-11 doc/paper.tex
More work on text

@@
 \newcommand{\af}{\mathfrak{a}}
+\newcommand{\bff}{\mathfrak{b}}
 \newcommand{\afb}{\mathfrak{a}_{\bot}}
@@
 
-For an arbitrary representation it is possible to diagonalize Cartan generators $H^{i}$ simultaneously by special choice of basis $\left\{\left|j\right>\right\}$ in $V$:
+For an arbitrary representation it is possible to diagonalize Cartan generators $H^{i}$ simultaneously by special choice of basis $\{v_{j}\}$ in $V$:
 \begin{equation}
   \label{eq:3}
-  H^{i}\left|j\right>=\nu_{j}^{i}\left|j\right>
+  H^{i}\cdot v_{j}=\nu_{j}^{i}v_{j}
 \end{equation}
-Eigenvalues of Cartan generators on element of basis $\left|j\right>$ are given by weight $\nu_{j}\in \hfg^{*}: \nu_{j}(H^{i})=\nu_{j}^{i}$, correspondingly vector $\left|j\right>$ is called weight vector of $\nu_{j}$.
+Eigenvalues of Cartan generators on element of basis $v_{j}$ are given by weight $\nu_{j}\in \hfg^{*}: \nu_{j}(H^{i})=\nu_{j}^{i}$.
+Vector $v\in V$ is called weight vector of weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$ , weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+Weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of weight subspace.
+
+The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+\begin{equation}
+  \label{eq:5}
+  E^{\alpha}\cdot v_{\lambda} \propto v_{\lambda+\alpha}
+\end{equation}
+It can be encoded by the formal character of module
+\begin{equation}
+  \label{eq:10}
+  \mathrm{ch}V=\sum_{\lambda}m_{\lambda} e^{\lambda}
+\end{equation}
+Character  $\mathrm{ch}V\in \mathcal{E}$. is the element of algebra $\mathcal{E}$ generated by formal exponents of weights.
 
@@
 
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
-\begin{equation}
-  \label{eq:5}
-  E^{\alpha}\left|\nu\right> \propto \left|\nu+\alpha\right>
-\end{equation}
-
 In the root system $\Delta$ exist simple roots $\left\{\alpha_{i}\right\}$, such that $\alpha=\sum_{i}n_{i}\alpha_{i},\; \forall\alpha\in \Delta$.
@@
 \end{equation}
+Note that root multiplicity $\mathrm{mult}(\alpha)$ for affine Lie algebra can be greater than one. Weyl vector is denoted by $\rho=\frac{1}{2}\sum_{\alpha\in \Delta^{+}}\alpha$.
+
 Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
@@
 \label{sec:high-weight-modul}
+
+We consider $\gf$-modules of the category $\mathcal{O}$, i.e.
+such $V$ that $V=\bigoplus_{\lambda\in \hfg^{*}} V_{\lambda}$, where each $V_{\lambda}$ is finite-dimensional and there exists finite set $\lambda_{1},\dots \lambda_{s}$ such that $V_{\lambda}\neq 0 \Rightarrow \lambda=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$, where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
+
+Highest weight module $V^{\mu}$ contains one highest weight $\mu$, all other weights are obtained by the subtraction of linear combination of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z}_{+}$.
+
+The simplest type of highest weight modules is Verma module $M^{\mu}$ which can be defined as the space $U(\gf)\underset{U(\bff_{+})}{\otimes} D_{\lambda}(\bff_{+})$, where $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' left part of tensor product onto the right part.
+Here $\bff_{+}$ is Borel sub-algebra, $D_{\lambda}(\bff_{+})$ is a special representation of $\bff_{+}$, such that $D(E^{\alpha})=0,\; D(h)=\lambda(h)$ for any positive root $\alpha$.
+Elements of $\gf$ act from the left, so we should expand element of $\gf$ in some basis, and then commute all the elements of $\bff_{+}$ to the right, so that they can act on space $D_{\lambda}(\bff_{+})$.
+
+Weight multiplicities of Verma module can be found from Weyl character formula
+\begin{equation}
+  \label{eq:11}
+  \mathrm{ch} M^{\mu}=\frac{e^{\mu}}{\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}}=\frac{e^{\mu}}{\sum_{w\in W} \epsilon(w) e^{w\rho-\rho}}
+\end{equation}
+Here we have used Weyl denominator identity
+\begin{equation}
+  \label{eq:12}
+  \prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
+\end{equation}
+and $\epsilon \left( w\right) :=\det \left( w\right)$ is also equal to the parity of number of Weyl reflections generating $w$.
+
+Verma module $M^{\mu}$ has unique maximal submodule and unique nontrivial simple quotient $L^{\mu}$ which is irreducible highest weight module.
+
+Weyl character formula for irreducible highest weight modules is
+\begin{equation}
+  \label{eq:13}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}
+\end{equation}
+So character of irreducible highest weight module can be seen as the combination of characters of Verma modules, this is connected with Bernstein-Gelfand-Gelfand resolution (\cite{bernstein1976category,bernstein1971structure}, see also \cite{humphreys2008representations}).
+
+We can use Weyl character formula to obtain recurrent relation on weight multiplicities which can be used for calculations \cite{il2010folded,kulish4sfa}:
+
+This formula is a particular case of more general formula related to branching which will discuss soon.
+
+Irreducible highest weight modules, BGG resolution, anomalous element.
 

### 2011-05-11 doc/paper.tex
Freudenthal formula is written

@@
 We can use Weyl character formula to obtain recurrent relation on weight multiplicities which can be used for calculations \cite{il2010folded,kulish4sfa}:
+\begin{equation}
+\label{eq:14}
+m_{\xi }=-\sum_{w\in W\setminus e}\epsilon (w)m_{\xi
+-\left( w(\rho )-\rho \right) }+\sum_{w\in W}\epsilon
+(w)\delta _{\left( w(\mu +\rho )-\rho \right) ,\xi }.  
+\end{equation}
 
@@
 
-Irreducible highest weight modules, BGG resolution, anomalous element.
+Another recurrent formula can be obtained from the study of Casimir elements action on irreducible highest weight modules \cite{humphreys1997introduction}:
+\begin{equation}
+  \label{eq:15}
+  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\gek 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
+\end{equation}
+It is called Freudenthal multiplicity formula. It is valid for irreducible highest weight modules.
 

### 2011-05-12 doc/paper.tex
More text. Theoretical background is mostly completed, bibliography expanded.

@@
 \newcommand{\hfb}{\mathfrak{h}_{\bot}}
+\newcommand{\pf}{\mathfrak{p}}
 
@@
 Character  $\mathrm{ch}V\in \mathcal{E}$. is the element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+It is possible to specialise character by taking its value on some element $\xi$ of $\hf$:
+
+String and branching functions definitions here.
 
@@
 
-The simplest type of highest weight modules is Verma module $M^{\mu}$ which can be defined as the space $U(\gf)\underset{U(\bff_{+})}{\otimes} D_{\lambda}(\bff_{+})$, where $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' left part of tensor product onto the right part.
+The simplest type of highest weight modules is Verma module $M^{\mu}$ which can be defined as the space
+\begin{equation}
+  \label{eq:17}
+  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D_{\lambda}(\bff_{+}),
+\end{equation}
+where $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' left part of tensor product onto the right part.
 Here $\bff_{+}$ is Borel sub-algebra, $D_{\lambda}(\bff_{+})$ is a special representation of $\bff_{+}$, such that $D(E^{\alpha})=0,\; D(h)=\lambda(h)$ for any positive root $\alpha$.
@@
 
+Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by the representation of some parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset of simple roots $I\subset \{\alpha_{1},\dots, \alpha_{r}\}$:
+\begin{equation*}
+M_{I}^{\mu}=U\left( \gf\right)\otimes _{U\left( \pf_{I}\right) }L_{\pf_{I}}^{\mu}.
+\end{equation*}
+Denote formal element $R_{I}:=\prod_{\alpha \in
+\Delta ^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha
+}\right) ^{\mathrm{mult}(\alpha )}$. Then the character of generalized Verma module can be written as
+\begin{equation}
+  \label{eq:18}
+  \mathrm{ch}M_{I}^{\mu}=\frac{1}{R_{I}}\mathrm{ch}L_{\pf_{I}}^{\mu }.
+\end{equation}
+
 Verma module $M^{\mu}$ has unique maximal submodule and unique nontrivial simple quotient $L^{\mu}$ which is irreducible highest weight module. 
-
 Weyl character formula for irreducible highest weight modules is
@@
   \label{eq:13}
-  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
 \end{equation}
@@
 
-This formula is a particular case of more general formula related to branching which will discuss soon.
-
 Another recurrent formula can be obtained from the study of Casimir elements action on irreducible highest weight modules \cite{humphreys1997introduction}:
@@
   \label{eq:15}
-  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\gek 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
+  m_{\lambda}=\frac{2}{(\mu+\rho)^{2}-(\lambda+\rho)^{2}}\sum_{\alpha\in \Delta^{+}}\sum_{k\geq 1} (\lambda+k\alpha,\alpha)m_{\lambda+k\alpha}.
 \end{equation}
-It is called Freudenthal multiplicity formula. It is valid for irreducible highest weight modules.
+It is called Freudenthal multiplicity formula.
+
+Now consider an algebra $\gf$ and subalgebra $\af\subset \gf$.
+Simple roots $\beta_{i}$ of the subalgebra $\af$ can be presented as the linear combinations of algebra roots $\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j} \alpha_{j},\ j=1,\dots,r_{\af}$.
+
+We also need to introduce subalgebra $\afb$. 
+Consider the root subspace $\frak{h}_{\perp \af}^{\ast }$ orthogonal to
+$\af$,
+\begin{equation*}
+\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
+h\in \frak{h}_{\af};\eta \left( h\right) =0\right\} ,
+\end{equation*}
+and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
+to $\af$,
+\begin{eqnarray}
+\Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
+h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
+\label{delta a ort} \\
+\Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
+}^{+}|\forall h\in \frak{h}_{\af};\beta ^{+}\left( h\right) =0\right\} .
+\notag
+\end{eqnarray}
+Let $W_{\afb}$ be the subgroup of $W$ generated by the
+reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
+}}^{+}$. The subsystem $\Delta _{\afb}$ determines the
+subalgebra $\afb$ with the Cartan subalgebra $\frak{h}_{\af%
+_{\perp }}$.
+
+For $\af$ and $\afb$ consider the
+corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
+}} $.
+
+ Form the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
+D}_{\afb}$ of the injection:
+\begin{equation}
+\mathcal{D}_{\af}:=\rho _{\af}-\pi _{\af}\rho , \qquad
+\mathcal{D}_{\afb}:=\rho _{\afb}-\pi _{\af%
+_{\perp }}\rho .  \label{defect-ort}
+\end{equation}
+
+For $\mu \in P^{+}$ consider the linked weights $\left\{
+\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $. Consider the projections to
+$h_{\afb}^{\ast }$ additionally shifted by the defect $-%
+\mathcal{D}_{\afb}$:
+\begin{equation*}
+\mu _{\afb}\left( w\right) :=\pi _{\afb}\left[
+w(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad w\in W.
+\end{equation*}
+Among the weights $\left\{ \mu _{\af_{\perp
+}}\left( w\right) |w\in W\right\} $ one can always choose those located in
+the fundamental chamber $\overline{C_{\afb}}$. Let $U$ be the
+set of representatives $u$ for the classes $W/W_{\afb}$ such
+that
+
+\begin{equation}
+U:=\left\{ u\in W|\quad \mu _{\afb}\left( u\right) \in
+\overline{C_{\afb}}\right\} \quad .  \label{U-def}
+\end{equation}
+Thus we can form the subsets:
+\begin{equation}
+\mu _{\widetilde{\mathfrak{a}}}\left( u\right) :=\pi _{\widetilde{%
+\mathfrak{a}}}\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\af%
+_{\perp }},\quad u\in U,  \label{mu-a}
+\end{equation}
+and
+\begin{equation}
+\mu _{\afb}\left( u\right) :=\pi _{\afb}\left[
+u(\mu +\rho )-\rho \right] -\mathcal{D}_{\afb},\quad u\in U.
+\label{mu-a-tilda}
+\end{equation}
+
+Notice that the subalgebra $\mathfrak{a}_{\bot}$ is regular by definition
+since it is built on a subset of roots of the algebra $\mathfrak{g}$.
+
+Each $\gf$-module is also $\af$-module, although $L^{\mu}_{\gf}$ is not irreducible as $\af$-module. It can be decomposed into the sum of irreducible $\af$-modules:
+\begin{equation}
+  \label{eq:16}
+  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
+\end{equation}
+Coefficients in this decomposition are called branching coefficients. 
+Using Weyl character formula we can write recurrent relation \cite{2010arXiv1007.0318L} for branching coefficients $k_{\xi
+}^{\left( \mu \right) }$ corresponding to the injection $\af\hookrightarrow \gf$:
+\begin{equation}
+\begin{array}{c}
+k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
+\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\afb}^{\mu _{\af%
+_{\perp }}\left( u\right) }\right) \delta _{\xi -\gamma _{0},\pi _{%
+\widetilde{\af}}(u(\mu +\rho )-\rho )}+\right.  \\
+\left. +\sum_{\gamma \in \Gamma _{\widetilde{\af}\rightarrow \gf%
+}}s\left( \gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right)
+}\right) .
+\end{array}
+\label{recurrent-rel}
+\end{equation}
+The recursion is goverened by the set $\Gamma _{\widetilde{\af}\rightarrow \gf}$ called the injection fan. The latter is defined by the
+carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
+coefficient function $s(\xi )$
+\begin{equation*}
+\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}:=\left\{
+\xi \in P_{\widetilde{\af}}|s(\xi )\neq 0\right\}
+\end{equation*}
+appearing in the expansion
+\begin{equation}
+\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
+_{\widetilde{\af}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}%
+_{\af}(\pi _{\widetilde{\af}}\alpha )}=-\sum_{\gamma \in P_{%
+\widetilde{\af}}}s(\gamma )e^{-\gamma };\quad
+\end{equation}
+The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \frak{%
+g}}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
+\right\} $ -- and the zero element is to be eliminated:
+\begin{equation}
+\Gamma _{\widetilde{\af}\rightarrow \gf}=\left\{ \xi -\gamma
+_{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
+\end{equation}
+The formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
+
+If root system of $\afb$ is generated by some subset of algebra $\gf$ simple roots $\alpha_{1},\dots,\alpha_{r}$ then recurrent relation (\ref{recurrent-rel}) is connected with generalized Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules \cite{2011arXiv1102.1702L}.
+
+Another particular case of this formula is connected with tensor product decomposition.
+Consider tensor product of two irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$.
+It is also $\gf$-module but not irreducible in general.
+So
+\begin{equation}
+  \label{eq:19}
+  L^{\mu}\otimes L^{\nu}=\bigoplus_{\gamma} f^{\mu\nu}_{\gamma}L^{\gamma}
+\end{equation}
+The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion coefficients.
+The problem of computation of fusion coefficients is equivalent to branching problem for diagonal subalgebra $\gf\subset \gf\otimes \gf$ (see \cite{LyakhovskyPostnova2011}).
 
@@
 \label{sec:core-datastructures}
+Having introduced required mathematical objects, problems and relations we now describe the related datastructures introduced in {\bf Affine.m}. 
+Although {\it Mathematica} is untyped language it is possible to create structured objects and do type checks with patterns \cite{shifrinmathematica}, \cite{maeder2000computer}. 
+\subsection{Weights}
+\label{sec:weights}
+
+Weights are represented
 

### 2011-05-12 doc/paper.tex
Some examples

@@
 % \biboptions{}
+
+\usepackage{color}
+\usepackage{listings}
+\usepackage{textcomp}
+\definecolor{listinggray}{gray}{0.9}
+\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+\lstset{
+%	backgroundcolor=\color{lbcolor},
+        language=Mathematica,
+	tabsize=2,
+	rulecolor=,
+        basicstyle=\scriptsize,
+        upquote=true,
+%        aboveskip={1.5\baselineskip},
+        columns=fixed,
+        showstringspaces=false,
+        extendedchars=true,
+%        breaklines=true,
+        prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
+%        frame=single,
+        showtabs=false,
+        showspaces=false,
+        showstringspaces=false,
+        identifierstyle=\ttfamily,
+        keywordstyle=\color[rgb]{0,0,1},
+        commentstyle=\color[rgb]{0.133,0.545,0.133},
+        stringstyle=\color[rgb]{0.627,0.126,0.941},
+}
+
 \newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
@@
 
+Sometimes we denote affine Lie algebra by $\gf$ then corresponding finite-dimensional Lie algebra is denoted by $\go$.
+
 \subsection{Weights and roots}
@@
 
-String and branching functions definitions here.
-
 Roots are weights of adjoint representation of $\gf$ on itself.
@@
 Although the full set of roots $\Delta$ is infinite for affine Lie algebra $\hat\gf$ the number of simple roots is finite and are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+The roots $\alpha_1,\dots, \alpha_r$ are equal to the roots of the underlying finite-dimensional Lie algebra $\go$.
+The root $\alpha_0=\delta-\theta$ is equal to the difference of {\it imaginary root} $\delta$ and $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$ -- highest root of algebra $\go$, coefficients $a_i$ are called {\it marks}.
+{\it Comarcs} are equal to $a_i^v=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+
 Roots system can be reconstructed from the set of simple roots with the use of Weyl group $W_{\gf}$ which is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
@@
 and can be used for compact description of Lie algebra commutation relations in Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+Basis conjugate to the basis of simple roots with respect to the product $(\cdot,\cdot)$ is called basis of fundamental weights. We denote its elements by $\omega_i$.
+\begin{equation}
+  \label{eq:20}
+  (\omega_i,\alpha_j)=\delta_{ij}
+\end{equation}
+For finite-dimensional Lie algebra $i=1,\dots, r$.
+For affine Lie algebra $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+Other fundamental weights are equal to $\omega_i=a_i^v \lambda_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of finite-dimensional Lie algebra $\go$.
 
@@
 \end{equation}
-So character of irreducible highest weight module can be seen as the combination of characters of Verma modules, this is connected with Bernstein-Gelfand-Gelfand resolution (\cite{bernstein1976category,bernstein1971structure}, see also \cite{humphreys2008representations}).
+So the character of irreducible highest weight module can be seen as the combination of characters of Verma modules, this is connected with Bernstein-Gelfand-Gelfand resolution (\cite{bernstein1976category,bernstein1971structure}, see also \cite{humphreys2008representations}).
 
@@
 We also need to introduce subalgebra $\afb$. 
-Consider the root subspace $\frak{h}_{\perp \af}^{\ast }$ orthogonal to
+Consider the root subspace $\hf_{\perp \af}^{\ast }$ orthogonal to
 $\af$,
 \begin{equation*}
-\frak{h}_{\perp \af}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
-h\in \frak{h}_{\af};\eta \left( h\right) =0\right\} ,
+\hf_{\perp \af}^{\ast }:=\left\{ \eta \in \hf^{\ast }|\forall
+h\in \hf_{\af};\eta \left( h\right) =0\right\} ,
 \end{equation*}
@@
 \Delta _{\afb} &:&=\left\{ \beta \in \Delta _{\gf}|\forall
-h\in \frak{h}_{\af};\beta \left( h\right) =0\right\} ,
+h\in \hf_{\af};\beta \left( h\right) =0\right\} ,
 \label{delta a ort} \\
 \Delta _{\afb}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\gf%
-}^{+}|\forall h\in \frak{h}_{\af};\beta ^{+}\left( h\right) =0\right\} .
+}^{+}|\forall h\in \hf_{\af};\beta ^{+}\left( h\right) =0\right\} .
 \notag
@@
 }}^{+}$. The subsystem $\Delta _{\afb}$ determines the
-subalgebra $\afb$ with the Cartan subalgebra $\frak{h}_{\af%
+subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
 _{\perp }}$.
@@
 
+In the case of affine Lie algebras $\gf, \af$  multiplicities $m_{\nu}$ and branching coefficients $b_{\nu}$ can be regarded as the coefficients in power series decomposition of string and branching functions correspondingly:
+\begin{align}
+  \label{eq:21}
+  &\sigma_{\nu}(q)=\sum_{n=0}^{\infty} m_{\nu-n\delta} q^n, \quad \nu=\sum_j c_j \omega_j,\quad c_j\geq 0\\
+  & b_{\nu}(q)=\sum_{n=0}^{\infty} b_{\nu-n\delta} q^n,\quad  \nu=\sum_j c_j \omega_j, \quad c_j\geq 0
+\end{align}
+
+String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
+
 \section{Core datastructures}
@@
 
-Weights are represented
+Weights are represented  by two data-structures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.
+
+Internally finite weight is a \lstinline{List} with the \lstinline{Head} \lstinline{finiteWeight}, its components are the coordinates of weight in orthogonal basis of \cite{bourbaki2002lie}.
+
+Affine weight is the extension of finite weight by the addition of level and grade.
+There are number of functions defined for finite and affine weights.
+Complete list can be found in user manual \cite{affinemanual}.
+The most important are the definitions of addition, multiplication by number and scalar product (bilinear form) for weights.
+These definitions allow to use traditional notation when working with {\bf Affine.m}:
+\begin{lstlisting}
+  w=makeFiniteWeight[{1,0,3}];
+  v=makeFiniteWeight[{3,2,1}];
+  2*w+v==makeFiniteWeight[{5,2,7}]
+  w.v==6
+\end{lstlisting}
+
+The use of orthogonal basis in the internal structure of weights allows us to work with weights without complete specification of root system which is useful for study of branching, since roots of the subalgebra can be specified by hand.
+
+\subsection{Root systems}
+\label{sec:root-systems}
+
+To specify an algebra of finite or affine type it is enough to supply its root system.
+Root systems are represented by two datatypes \lstinline{finiteRootSystem} and \lstinline{affineRootSystem}.
+The latter is an extension of the former.
+We offer several different constructors for these datastructures. 
+It is possible to specify the set of simple roots explicitly, for example to study the subalgebra $B_2\subset B_4$ we can use the definition
+\begin{lstlisting}
+  b2b4=makeFiniteRootSystem[ { {1,-1,0,0}, {0,1,0,0} } ]
+\end{lstlisting}
+There are constructors for root systems of simple finite-dimensional Lie algebras:
+\begin{lstlisting}
+  b2=makeSimpleRootSystem[B,2]
+\end{lstlisting}
+We use typographic features of {\it Mathematica} frontend to offer traditional mathematical notation for simple Lie algebras:
+
+$\mathrm{Print}\left[B_2\right]$
+\begin{lstlisting}
+finiteRootSystem[2, 2, {finiteWeight[2, {1, -1}], finiteWeight[2,{0, 1}]}]}
+\end{lstlisting}
+
+Non-twisted affine root systems can be created as affine extensions of finte root systems, e.g.
+\begin{lstlisting}
+  b2affine = makeAffineExtension[b2]
+\end{lstlisting}
+In notebook interface this can be written simply as $\hat{B}_2$.
+
+Semisimple Lie algebras can be created as sums of simple:
+\begin{equation*}
+  \mathrm{Print}[A_1+A_1]
+\end{equation*}
+\begin{lstlisting}
+  finiteRootSystem
+\end{lstlisting}
 

### 2011-05-14 doc/paper.tex
Some code updates, paper outline is finished.

@@
 \end{equation}
-Character  $\mathrm{ch}V\in \mathcal{E}$. is the element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+Character  $\mathrm{ch}V\in \mathcal{E}$ is the element of algebra $\mathcal{E}$ generated by formal exponents of weights.
 It is possible to specialise character by taking its value on some element $\xi$ of $\hf$:
@@
 \end{align}
+Highest weight of adjoint representation.
+
+%%  Given a root system Φ we can always choose (in many ways) a set of positive roots. This is a subset Φ + of Φ such that
+%%  
+%%      * For each root \alpha\in\Phi exactly one of the roots α, –α is contained in Φ + .
+%%      * For any two distinct \alpha, \beta\in \Phi^+ such that α + β is a root, \alpha+\beta\in\Phi^+.
+%%  
+%%  If a set of positive roots Φ + is chosen, elements of –Φ + are called negative roots.
+%%  
+%%  An element of Φ + is called a simple root if it cannot be written as the sum of two elements of Φ + .
+The set Δ of simple roots is a basis of V with the property that every vector in Φ is a linear combination of elements of Δ with all coefficients non-negative, or all coefficients non-positive.
+For each choice of positive roots, the corresponding set of simple roots is the unique set of roots such that the positive roots are exactly those that can be expressed as a combination of them with non-negative coefficients, and such that these combinations are unique.
+%%  
+%%  Ordering. Highest root. Rho=sum of fundamental weights, not half-sum of positive roots.
 
@@
 \end{equation}
-Note that root multiplicity $\mathrm{mult}(\alpha)$ for affine Lie algebra can be greater than one. Weyl vector is denoted by $\rho=\frac{1}{2}\sum_{\alpha\in \Delta^{+}}\alpha$.
+Note that root multiplicity $\mathrm{mult}(\alpha)$ for affine Lie algebra can be greater than one.
 
@@
 
+Weyl vector is denoted by $\rho=\sum_{i} \omega_{i}$, it is of importance for 
 \subsection{Highest weight modules}
@@
 So the character of irreducible highest weight module can be seen as the combination of characters of Verma modules, this is connected with Bernstein-Gelfand-Gelfand resolution (\cite{bernstein1976category,bernstein1971structure}, see also \cite{humphreys2008representations}).
+
+%% Define external border of representation
 
@@
 
-$\mathrm{Print}\left[B_2\right]$
-\begin{lstlisting}
-finiteRootSystem[2, 2, {finiteWeight[2, {1, -1}], finiteWeight[2,{0, 1}]}]}
+\begin{lstlisting}[mathescape=true]
+  $B_2$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, -1}], finiteWeight[2,{0, 1}]}]}
 \end{lstlisting}
@@
 Semisimple Lie algebras can be created as sums of simple:
-\begin{equation*}
-  \mathrm{Print}[A_1+A_1]
-\end{equation*}
+\begin{lstlisting}[mathescape=true]
+  $A_1$+$A_1$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 1}]}]
+\end{lstlisting}
+
+Predicate \lstinline{rootSystemQ} checks if the object is root systems of finite or affine type.
+
+List of simple roots is the property of root system so it is accessed as \lstinline{rs[simpleRoots]}.
+
+We have implemented several functions to get major properties of root systems. Weyl vector is given by the function \lstinline{rho[rs_?rootSystemQ]}:
+\begin{lstlisting}[label=list:1]
+  rho[b2]
+  finiteWeight[2, {3/2, 1/2}]
+\end{lstlisting}
+Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}.
+For affine Lie algebra this and related functions return the list up to fixed grade.
+This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default.
+List of roots (up to \lstinline{gradeLimit}) is returned by \lstinline{roots[rs]}.
+Cartan matrix and fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
+
+It is possible to specify a weight of Lie algebra by its Dynkin label
 \begin{lstlisting}
-  finiteRootSystem
+  weight[b2][1,2,3] == makeFiniteWeight[{2, 1}]
+\end{lstlisting}
+The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of weight \lstinline{wg} in the root system \lstinline{rs}.
+
+Elements of Weyl group are specified by the set of indices of reflections, so element of Weyl group of algebra $B_{2}$ which is equal to $w=s_{1}s_{2}s_{1}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
+Then it can be applied to the weights:
+\begin{lstlisting}
+  w = weylGroupElement[b2][1,2,1];
+  w @ makeFiniteWeight[{1,0}] == makeFiniteWeight[{-1,0}]
+\end{lstlisting}
+
+Computation of ShortLex form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching features of {\it Mathematica}.
+In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
+Our presentation of Weyl group elements is compatible with the code of \cite{KallenShortlex}
+\begin{lstlisting}[mathescape=true]
+  In[1]  = $<<$A3reduce;
+           reduce[s[1,2,1,2,1,3,2,1,1]]
+  Out[1] = s[2, 3, 2]
+
+  In[2]  = (weylGroupElement[$A_{3}$] @@ reduce[s[1,2,1,2,1,3,2,1,1]]) @ weight[$A_{3}$][-1,-2,-1]
+  Out[2] = finiteWeight[4, {-2, 2, 1, -1}]
+
+  In[3]  = dynkinLabels[$A_{3}$][Out[2]]
+  Out[3] = {-4, 1, 2}
+\end{lstlisting}
+
+\subsection{Formal elements}
+\label{sec:formal-elements}
+
+We represent formal characters of representations by special structure \lstinline{formalElements}.
+This structure is a hash-table implemented with \lstinline{DownValues}.
+The keys are weights at the exponents and the values are corresponding multiplicities.
+\lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
+creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of formal algebra $\mathcal{E}$.
+The operations of formal algebra $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by number or exponent of weight.
+There is also multiplication of formal elements but no division.
+\begin{lstlisting}[mathescape=true]
+  In[1]  = makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}] *
+             (2 * Exp[makeFiniteWeight[{1,0}]] *
+             makeFormalElement[{makeFiniteWeight[{1,1}],makeFiniteWeight[{0,0}]},{1,2}]);
+  In[2]  = In[1][weights]
+  Out[2] = {finiteWeight[2, {1, 0}], finiteWeight[2, {2, 1}], finiteWeight[2, {3, 2}]}
+
+  In[3]  = In[1][multiplicities]
+  Out[3]= {8, 8, 2}
 \end{lstlisting}
@@
 
+As we have already stated in section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules.
+Both algorithms proceed in the following way to calculate weight multiplicities:
+\begin{enumerate}
+\item Create the list of weights in main Weyl chamber by subtraction of all possible combinations of simple roots from the highest weight (e.g.
+for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
+\item Sort the list of weights by their product with Weyl vector.
+\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use Weyl symmetry. 
+\end{enumerate}
+The difference in performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
+For recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in Weyl group (if we are far from the boundary of representation diagram).
+When Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
+So Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
+But Freudenthal formula is of no use if we are interested in Verma modules.
+
+In the calculation of branching coefficients use of Freudenthal formula requires full construction of formal characters of algebra representation and all the representations of subalgebra.
+It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebra.
+
+Branching algorithm \cite{2010arXiv1007.0318L}
+\subsection{Performance testing}
+\label{sec:performance-testing}
+
+We have made some experiments with our implementations of Freudenthal formula and formula \eqref{eq:15} and have got the following graphs \ref{freudenthal-racah-times}.
+
+\begin{figure}[h]
+  \label{freudenthal-racah-times}
+  \noindent\centering{
+ %   \includegraphics[width=80mm]{figure1.eps}
+  }
+  \caption{Freudenthal run time with the number of weights in $\bar C$.}
+
+  \noindent\centering{
+ %   \includegraphics[width=80mm]{figure1.eps}
+  }
+  \caption{Racah run time with the number of weights in $\bar C$.}
+
+  \noindent\centering{
+ %   \includegraphics[width=80mm]{figure1.eps}
+  }
+  \caption{Freudenthal run time with rank of the algebra}
+
+  \noindent\centering{
+ %   \includegraphics[width=80mm]{figure1.eps}
+  }
+  \caption{Racah run time with rank of the algebra}
+\end{figure}
+
+Measurements for branching computations for $\hat B_{3}\subset \hat B_{4}$ are shown at the Fig. \ref{fig:branching}.
+\begin{figure}[h]
+  \label{fig:branching}
+  \noindent\centering{
+ %   \includegraphics[width=80mm]{figure1.eps}
+  }
+  \caption{Branching}
+\end{figure}
+
 \section{Examples}
 \label{sec:examples}
+In this section we present some examples of computations available with {\bf Affine.m} with the code required to produce these results.
 
@@
 \label{sec:conclusion}
+We present the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
+The package is available from {\it github} and is also submitted to the library.
 

### 2011-05-14 src/affine.m

@@ -342,10 +342,10 @@ weylGroupElement::"usage"=
     "weylGroupElement[x__Integer][rs_?rootSystemQ] represents element of Weyl group composed of basic reflecetions x \n
     of root system rs. Example: weylGroupElement[1,2,1][makeSimpleRootSystem[B,2]] = s1 s2 s1";
 clear[weylGroupElement];
-weylGroupElement[x__Integer][rs_?rootSystemQ]:=Function[z,Fold[revApply,z,reflection /@ rs[simpleRoot]/@{x}]];
+weylGroupElement[rs_?rootSystemQ][x__Integer]:=Function[z,Fold[revApply,z,reflection /@ rs[simpleRoot]/@{x}]];
 
 Expect["Weyl reflection s1 s2 s1 in algebra B2",True,
-       weylGroupElement[1,2,1][makeSimpleRootSystem[B,2]][makeFiniteWeight[{1,0}]]==
+       weylGroupElement[makeSimpleRootSystem[B,2]][1,2,1][makeFiniteWeight[{1,0}]]==
        makeFiniteWeight[{-1,0}]]
 
 fundamentalWeights::"usage"=
@@ -633,6 +633,8 @@ weight::"usage"=
     "weight[rs_?rootSystemQ][labels__Integer] constructs weight defined by Dynkin labels";
 weight[rs_?rootSystemQ][labels__Integer]:=fundamentalWeights[rs].{labels}
 
+dynkinLabels[rs_?rootSystemQ][wg_?weightQ]:=(#.wg)& /@ rs[simpleRoots];
+
 orthogonalSubsystem::"usage"=
     "orthogonalSubsystem[rs_?rootSystemQ,subs_?rootSystemQ] returns subset of positive roots of root system rs, which 
     are orthogonal to simple roots of subsystem subs";
@@ -689,6 +691,8 @@ formalElement/:x_formalElement*Exp[w_?weightQ]:=
     Module[{ws},
 	   ws=Select[(#+w)&/@x[weights],checkGrade[x]];
 	   makeFormalElement[ws,(x[#-w])&/@ws]]
+
+formalElement/:x_formalElement * y_formalElement:=Plus @@ ((y[#]*(x*Exp[#]))& /@ y[weights]);
 
 (* formalElement/:orbit[rs_?rootSystemQ][fe_formalElement]:= *)
 

### 2011-05-16 src/affine.m
Some documentation added

@@ -468,6 +468,9 @@ Map[Print,orbit[makeSimpleRootSystem[B, 2]][rho[makeSimpleRootSystem[B, 2]]],2]
 SubValues[finiteWeight]
 *)
 
+
+dimension::"usage"=
+    "dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra highest weight representation";
 dimension[{pr__?weightQ}][hweight_?weightQ]:=
     Module[{rh=rho[{pr}]},
 	   Plus@@((#.(hweight+rh)/rh.#)&/@{pr})];
@@ -577,11 +580,9 @@ makeAffineExtension::"usage"=
     is extension of given finite-dimensional root system";
 makeAffineExtension[fs_finiteRootSystem]:=affineRootSystem[fs[rank],fs,makeAffineWeight[-higestRoot[fs],0,1],(makeAffineWeight[#,0,0]&)/@fs[simpleRoots]]
 
+OverHat::"usage"=
+    "OverHat[rs_finiteRootSystem] creates affine extension of root system rs, it is equivalent makeAffineExtension[rs], but uses mathematical notation in notebook interface";
 OverHat[rs_finiteRootSystem]:=makeAffineExtension[rs];
-
-Append[makeAffineExtension[makeSimpleRootSystem[B,2]][simpleRoots],makeAffineExtension[makeSimpleRootSystem[B,2]][[3]]]
-
-(* makeAffineExtension[makeSimpleRootSystem[B,2]][simpleRoot][0] *)
 
 
 affineRootSystem::"usage"=
@@ -641,7 +642,8 @@ orthogonalSubsystem::"usage"=
 orthogonalSubsystem[rs_?rootSystemQ,subs_?rootSystemQ]:=Cases[positiveRoots[rs], z_ /; And @@ (z.#==0& /@ subs[simpleRoots])]
 
 projection::"usage"=
-    "projection[rs_?rootSystemQ][weights__?weightQ] projects given weight to the root (sub)system";
+    "projection[rs_?rootSystemQ][weights__?weightQ] projects given weight to the root (sub)system\n
+    projection[rs_?rootSystemQ][fe_formalElement] projects the formal elements";
 projection[rs_finiteRootSystem][{weights__?weightQ}]:= 
[…]

### 2011-05-17 src/affine.m
Couple of tests added

@@ -622,6 +622,11 @@ toFundamentalChamber[rs_affineRootSystem][vec_affineWeight]:=
 marks::"usage"="marks[rs_affineRootSystem] returns marks of affine Lie algebra";
 marks[rs_affineRootSystem]:=Prepend[Inverse[cartanMatrix[rs[finiteRootSystem]]].(-2*#.rs[simpleRoot][0]/(#.#)&)/@rs[realRoots],1]
 
+Expect["Marks for affine A_3", {1,1,1,1},marks[OverHat[Subscript[A,3]]]];
+
+Expect["Marks for affine C_4", {1, 2, 2, 2, 1},marks[OverHat[Subscript[C,4]]]];
+
+
 marks::"usage"="comarks[rs_affineRootSystem] returns comarks of affine Lie algebra";
 comarks[rs_affineRootSystem]:=marks[rs]*Map[#.#/2&,rs[simpleRoots]]
 

### 2011-05-18 src/affine.m
?

@@ -468,6 +468,9 @@ Map[Print,orbit[makeSimpleRootSystem[B, 2]][rho[makeSimpleRootSystem[B, 2]]],2]
 SubValues[finiteWeight]
 *)
 
+
+dimension::"usage"=
+    "dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra highest weight representation";
 dimension[{pr__?weightQ}][hweight_?weightQ]:=
     Module[{rh=rho[{pr}]},
 	   Plus@@((#.(hweight+rh)/rh.#)&/@{pr})];
@@ -577,11 +580,9 @@ makeAffineExtension::"usage"=
     is extension of given finite-dimensional root system";
 makeAffineExtension[fs_finiteRootSystem]:=affineRootSystem[fs[rank],fs,makeAffineWeight[-higestRoot[fs],0,1],(makeAffineWeight[#,0,0]&)/@fs[simpleRoots]]
 
+OverHat::"usage"=
+    "OverHat[rs_finiteRootSystem] creates affine extension of root system rs, it is equivalent makeAffineExtension[rs], but uses mathematical notation in notebook interface";
 OverHat[rs_finiteRootSystem]:=makeAffineExtension[rs];
-
-Append[makeAffineExtension[makeSimpleRootSystem[B,2]][simpleRoots],makeAffineExtension[makeSimpleRootSystem[B,2]][[3]]]
-
-(* makeAffineExtension[makeSimpleRootSystem[B,2]][simpleRoot][0] *)
 
 
 affineRootSystem::"usage"=
@@ -641,7 +642,8 @@ orthogonalSubsystem::"usage"=
 orthogonalSubsystem[rs_?rootSystemQ,subs_?rootSystemQ]:=Cases[positiveRoots[rs], z_ /; And @@ (z.#==0& /@ subs[simpleRoots])]
 
 projection::"usage"=
-    "projection[rs_?rootSystemQ][weights__?weightQ] projects given weight to the root (sub)system";
+    "projection[rs_?rootSystemQ][weights__?weightQ] projects given weight to the root (sub)system\n
+    projection[rs_?rootSystemQ][fe_formalElement] projects the formal elements";
 projection[rs_finiteRootSystem][{weights__?weightQ}]:= 
[…]

### 2011-05-18 doc/paper.tex

@@
 
-Basis conjugate to the basis of simple roots with respect to the product $(\cdot,\cdot)$ is called basis of fundamental weights. We denote its elements by $\omega_i$.
+The form \eqref{eq:9} induces the basis in ${\cal L}P$ dual  to the simple
+roots basis. It is called the fundamental weights basis. We denote
+its elements by $\omega_i$.
 \begin{equation}
   \label{eq:20}
-  (\omega_i,\alpha_j)=\delta_{ij}
+  \langle\omega_i,\alpha_j\rangele=\frac{(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
 \end{equation}
@@
 
-The simplest type of highest weight modules is Verma module $M^{\mu}$ which can be defined as the space
+The simplest type of highest weight modules is the Verma module
+$M^{\mu}$ who's space can be defined as the space
 \begin{equation}
@@
 
-Weight multiplicities of Verma module can be found from Weyl character formula
+Weight multiplicities in Verma module can be found from the Weyl
+character formula
 \begin{equation}
@@
 \end{equation}
-Here we have used Weyl denominator identity
+Here we have used the Weyl denominator identity
 \begin{equation}
@@
 \end{equation}
-and $\epsilon \left( w\right) :=\det \left( w\right)$ is also equal to the parity of number of Weyl reflections generating $w$.
+and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to
+the parity of number of Weyl reflections generating $w$.
 
@@
 \end{equation*}
-Denote formal element $R_{I}:=\prod_{\alpha \in
-\Delta ^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha
-}\right) ^{\mathrm{mult}(\alpha )}$. Then the character of generalized Verma module can be written as
+Denote a formal element $R_{I}:=\prod_{\alpha \in \Delta
+^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
+^{\mathrm{mult}(\alpha )}$. Then the character of generalized
+Verma module can be written as
 \begin{equation}
@@
 
-Verma module $M^{\mu}$ has unique maximal submodule and unique nontrivial simple quotient $L^{\mu}$ which is irreducible highest weight module. 
-Weyl character formula for irreducible highest weight modules is
+Verma module $M^{\mu}$ has the unique maximal submodule and the
+unique nontrivial simple quotient $L^{\mu}$ which is an
+irreducible highest weight module. Weyl character formula for
+irreducible highest weight modules is
 \begin{equation}
@@
 \end{equation}
-So the character of irreducible highest weight module can be seen as the combination of characters of Verma modules, this is connected with Bernstein-Gelfand-Gelfand resolution (\cite{bernstein1976category,bernstein1971structure}, see also \cite{humphreys2008representations}).
+Thus the character of an irreducible highest weight module can be
+seen as the combination of characters of Verma modules. ( This
+fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
+(\cite{bernstein1976category,bernstein1971structure}, see also
+\cite{humphreys2008representations}).)
 
-%% Define external border of representation
+%% Define external border of irreducible representation here
 
@@
 
-Another recurrent formula can be obtained from the study of Casimir elements action on irreducible highest weight modules \cite{humphreys1997introduction}:
+Other recurrent formula can be obtained from the study of Casimir
+elements action on irreducible highest weight modules
+\cite{humphreys1997introduction}:
 \begin{equation}
@@
 \end{equation}
-It is called Freudenthal multiplicity formula.
+It is called the Freudenthal multiplicity formula.
 
-Now consider an algebra $\gf$ and subalgebra $\af\subset \gf$.
-Simple roots $\beta_{i}$ of the subalgebra $\af$ can be presented as the linear combinations of algebra roots $\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j} \alpha_{j},\ j=1,\dots,r_{\af}$.
+Now consider an algebra $\gf$ and a reductive subalgebra
+$\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
+can be presented as linear combinations of algebra roots
+$\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
+\alpha_{j},\ j=1,\dots,r_{\af}$.
 
-We also need to introduce subalgebra $\afb$. 
-Consider the root subspace $\hf_{\perp \af}^{\ast }$ orthogonal to
-$\af$,
+For a subalgebra $\af\subset \gf$ we introduce a subalgebra
+$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
+orthogonal to $\af$,
 \begin{equation*}
@@
 
- Form the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
+Compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
 D}_{\afb}$ of the injection:
@@
 
-For $\mu \in P^{+}$ consider the linked weights $\left\{
-\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $. Consider the projections to
+For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
+w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections
+to
 $h_{\afb}^{\ast }$ additionally shifted by the defect $-%
@@
 
-Each $\gf$-module is also $\af$-module, although $L^{\mu}_{\gf}$ is not irreducible as $\af$-module. It can be decomposed into the sum of irreducible $\af$-modules:
+Each $\gf$-module is also an $\af$-module, although
+$L^{\mu}_{\gf}$ is not irreducible as $\af$-module. It can be
+decomposed into the sum of irreducible $\af$-modules:
 \begin{equation}
@@
 \end{equation}
-Coefficients in this decomposition are called branching coefficients. 
-Using Weyl character formula we can write recurrent relation \cite{2010arXiv1007.0318L} for branching coefficients $k_{\xi
-}^{\left( \mu \right) }$ corresponding to the injection $\af\hookrightarrow \gf$:
+Coefficients in this decomposition are called the branching
+coefficients. Using the Weyl character formula we can write a
+recurrent relation \cite{2010arXiv1007.0318L} for branching
+coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
+injection $\af\hookrightarrow \gf$:
 \begin{equation}
@@
 
-If root system of $\afb$ is generated by some subset of algebra $\gf$ simple roots $\alpha_{1},\dots,\alpha_{r}$ then recurrent relation (\ref{recurrent-rel}) is connected with generalized Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules \cite{2011arXiv1102.1702L}.
+If the root system of $\afb$ is generated by some subset of $\gf$
+simple roots $\alpha_{1},\dots,\alpha_{r}$ then the recurrent
+relation (\ref{recurrent-rel}) is connected with the generalized
+Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
+\cite{2011arXiv1102.1702L}.
 
-Another particular case of this formula is connected with tensor product decomposition.
-Consider tensor product of two irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$.
-It is also $\gf$-module but not irreducible in general.
-So
+Another particular case of this formula is connected with tensor
+product decomposition. Consider the tensor product of two
+irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
+$\gf$-module but not irreducible in general. So
 \begin{equation}
@@
 \end{equation}
-The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion coefficients.
-The problem of computation of fusion coefficients is equivalent to branching problem for diagonal subalgebra $\gf\subset \gf\otimes \gf$ (see \cite{LyakhovskyPostnova2011}).
+The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
+coefficients. The problem of computation of fusion coefficients is
+equivalent to branching problem for the diagonal subalgebra
+$\gf\subset \gf\otimes \gf$ (see \cite{LyakhovskyPostnova2011}).
 
-In the case of affine Lie algebras $\gf, \af$  multiplicities $m_{\nu}$ and branching coefficients $b_{\nu}$ can be regarded as the coefficients in power series decomposition of string and branching functions correspondingly:
+In the case of affine Lie algebras $\gf, \af$  the multiplicities
+$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
+can be regarded as the coefficients in power series decomposition
+of string and branching functions correspondingly:
 \begin{align}
@@
 \section{Core datastructures}
-\label{sec:core-datastructures}
-Having introduced required mathematical objects, problems and relations we now describe the related datastructures introduced in {\bf Affine.m}. 
-Although {\it Mathematica} is untyped language it is possible to create structured objects and do type checks with patterns \cite{shifrinmathematica}, \cite{maeder2000computer}. 
+\label{sec:core-datastructures} Having introduced necessary
+mathematical objects, problems and relations we now describe the
+related datastructures introduced in {\bf Affine.m}. Although {\it
+Mathematica} is untyped language it is possible to create
+structured objects and do type checks with patterns
+\cite{shifrinmathematica}, \cite{maeder2000computer}.
 \subsection{Weights}
@@
 
-Internally finite weight is a \lstinline{List} with the \lstinline{Head} \lstinline{finiteWeight}, its components are the coordinates of weight in orthogonal basis of \cite{bourbaki2002lie}.
+Internally the finite weight is a \lstinline{List} with the
+\lstinline{Head} \lstinline{finiteWeight}, its components are the
+coordinates of the weight in the orthogonal basis of
+\cite{bourbaki2002lie}.
 
-Affine weight is the extension of finite weight by the addition of level and grade.
-There are number of functions defined for finite and affine weights.
-Complete list can be found in user manual \cite{affinemanual}.
-The most important are the definitions of addition, multiplication by number and scalar product (bilinear form) for weights.
-These definitions allow to use traditional notation when working with {\bf Affine.m}:
+Affine weight is an extension of a finite weight by supplying it
+with level and grade coordinates. There is a set of functions
+defined for finite and affine weights. The complete list can be
+found in the user manual \cite{affinemanual}. The most important
+are the definitions of addition, multiplication by number and
+scalar product (bilinear form) for weights. These definitions
+allow to use traditional notation when working with {\bf
+Affine.m}:
 \begin{lstlisting}
@@
 
-To specify an algebra of finite or affine type it is enough to supply its root system.
-Root systems are represented by two datatypes \lstinline{finiteRootSystem} and \lstinline{affineRootSystem}.
-The latter is an extension of the former.
-We offer several different constructors for these datastructures. 
-It is possible to specify the set of simple roots explicitly, for example to study the subalgebra $B_2\subset B_4$ we can use the definition
+To specify an algebra of finite or affine type it is enough to fix 
+its root system. Root systems are represented by two datatypes
+\lstinline{finiteRootSystem} and \lstinline{affineRootSystem}. The
+latter is an extension of the former. We offer several different
+constructors for these datastructures. It is possible to specify
+the set of simple roots explicitly, for example to study the
+subalgebra $B_2\subset B_4$ we can use the definition
 \begin{lstlisting}

### 2011-05-18 src/affine.m
Some work on debugging and graphics, see debug2.m

@@ -473,11 +473,11 @@ dimension::"usage"=
     "dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra highest weight representation";
 dimension[{pr__?weightQ}][hweight_?weightQ]:=
     Module[{rh=rho[{pr}]},
-	   Plus@@((#.(hweight+rh)/rh.#)&/@{pr})];
+	   Times@@((  (#.(hweight+rh))/(rh.#) )&/@{pr})];
 
 Expect["Dimension",5, dimension[{makeFiniteWeight[{1,1}]}][makeFiniteWeight[{2,2}]]];
 
-dimension[rs_?rootSystemQ][hweight_?weightQ]:=dimension[positiveRoots[rs]][hweight];
+dimension[rs_?rootSystemQ][hweight_?weightQ]:=dimension[positiveRoots[rs]][toFundamentalChamber[rs][hweight]];
 
 Expect["Dimension",5, dimension[makeSimpleRootSystem[A,1]][makeFiniteWeight[{2}]]];
 
@@ -749,6 +749,14 @@ getOrderedWeightsProjectedToWeylChamber[{algroots__?weightQ},subs_?rootSystemQ,h
 	   Sort[
 	       Flatten[weightSystem[projection[subs][{algroots}]][projection[subs][{hweight}][[1]]]],
 	       #1.rh>#2.rh&]];
+
+extendedAnomElement[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
+    Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0},
+	   orth=orthogonalSubsystem[rs,subs];
+	   anomW=anomalousWeights[rs][highestWeight];
+	   selW=(#-rho[rs])& /@ Select[(#+rho[rs])& /@ anomW[weights],mainChamberQ[orth]];
+	   selWM=makeFormalElement[projection[subs][selW],(anomW[#]*dimension[orth][#])&/@selW];
+	   {selW,selWM}]
 
 ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
     Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0},

### 2011-05-18 tests/debug2.m

@@ -1,0 +1,133 @@
+AppendTo[$Path,$InitialDirectory <> "/../src/"];
+
+<<affine.m;
+
+b4=Subscript[B,4];
+al=b4[simpleRoots];
+b={al[[3]],al[[4]]};
+b2=makeFiniteRootSystem[b];
+
+f=fan[b4,b2];
+
+Export["/home/anton/programing/Affine/tests/graph.png",Graphics[Text[f[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ f[weights]]]
+
+wg=weight[b4][0,1,0,2]; (* makeFiniteWeight[{2,2,1,1}] *)
+aw=projection[b2][anomalousWeights[b4][wg]];
+
+Export["/home/anton/programing/Affine/tests/anom.png",Graphics[Text[aw[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ aw[weights]]]
+
+Out[23]= /home/anton/programing/Affine/tests/anom.png
+
+Out[20]= /home/anton/programing/Affine/tests/anom.png
+
+extendedAnomElement[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
+    Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0},
+	   orth=orthogonalSubsystem[rs,subs];
+	   anomW=anomalousWeights[rs][highestWeight];
+	   selW=Select[anomW[weights],mainChamberQ[orth]]; (* <---- !!!!!! *)
+	   selWM=makeFormalElement[projection[subs][selW],(anomW[#]*dimension[orth][#])&/@selW];
+	   {selW,selWM}]
+
+
+
+
+
+eae=extendedAnomElement[b4,b2][wg][[2]];
+
+Export["/home/anton/programing/Affine/tests/eanom.png",Graphics[Text[eae[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ eae[weights]]]
+
+Out[63]= /home/anton/programing/Affine/tests/eanom.png
+
+Out[60]= /home/anton/programing/Affine/tests/eanom.png
+
+br=ourBranching[b4,b2][wg+rho[b4]]
+
[…]

### 2011-05-18 src/affine.m
Anomalous weights for branching seem to be correct

@@ -649,11 +649,14 @@ orthogonalSubsystem[rs_?rootSystemQ,subs_?rootSystemQ]:=Cases[positiveRoots[rs],
 projection::"usage"=
     "projection[rs_?rootSystemQ][weights__?weightQ] projects given weight to the root (sub)system\n
     projection[rs_?rootSystemQ][fe_formalElement] projects the formal elements";
+
 projection[rs_finiteRootSystem][{weights__?weightQ}]:= 
     Map[Function[w,(Inverse[cartanMatrix[rs]]. ( 2*(w.#/(#.#))& /@ rs[simpleRoots])).rs[simpleRoots]],{weights}]
 
 projection[rs_affineRootSystem][{weights__?weightQ}]:= 
     Map[makeAffineWeight[projection[rs[finiteRootSystem]][#[finitePart]],#[level],#[grade]]&,{weights}]
+
+projection[rs_?rootSystemQ][wg_?weightQ]:=projection[rs][{wg}][[1]];
 
 (*    Map[Apply[Plus,#]&,Outer[(#1.#2)/(#2.#2)*#2&,{weights},rs[simpleRoots]]] *)
 
@@ -750,27 +753,23 @@ getOrderedWeightsProjectedToWeylChamber[{algroots__?weightQ},subs_?rootSystemQ,h
 	       Flatten[weightSystem[projection[subs][{algroots}]][projection[subs][{hweight}][[1]]]],
 	       #1.rh>#2.rh&]];
 
+
 extendedAnomElement[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
-    Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0},
+    Module[{anomW,selW,selWM,rh=rho[rs],orth,ortrh},
 	   orth=orthogonalSubsystem[rs,subs];
+	   ortrh=rho[orth];
 	   anomW=anomalousWeights[rs][highestWeight];
-	   selW=(#-rho[rs])& /@ Select[(#+rho[rs])& /@ anomW[weights],mainChamberQ[orth]];
-	   selWM=makeFormalElement[projection[subs][selW],(anomW[#]*dimension[orth][#])&/@selW];
-	   {selW,selWM}]
+	   selW=Select[anomW[weights],Function[x,mainChamberQ[orth][x+rh-projection[subs][x+rh]]]];
[…]

### 2011-05-18 tests/debug2.m

@@ -9,7 +9,9 @@ b2=makeFiniteRootSystem[b];
 
 f=fan[b4,b2];
 
-Export["/home/anton/programing/Affine/tests/graph.png",Graphics[Text[f[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ f[weights]]]
+Export["/home/anton/programing/Affine/tests/fan.png",Graphics[Text[f[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ f[weights]]]
+
+Out[5]= /home/anton/programing/Affine/tests/fan.png
 
 wg=weight[b4][0,1,0,2]; (* makeFiniteWeight[{2,2,1,1}] *)
 aw=projection[b2][anomalousWeights[b4][wg]];
@@ -20,94 +22,50 @@ Out[23]= /home/anton/programing/Affine/tests/anom.png
 
 Out[20]= /home/anton/programing/Affine/tests/anom.png
 
+
 extendedAnomElement[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
-    Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0},
+    Module[{anomW,selW,selWM,rh=rho[rs],orth,ortrh},
 	   orth=orthogonalSubsystem[rs,subs];
+	   ortrh=rho[orth];
 	   anomW=anomalousWeights[rs][highestWeight];
-	   selW=Select[anomW[weights],mainChamberQ[orth]]; (* <---- !!!!!! *)
-	   selWM=makeFormalElement[projection[subs][selW],(anomW[#]*dimension[orth][#])&/@selW];
-	   {selW,selWM}]
+	   selW=Select[anomW[weights],Function[x,mainChamberQ[orth][x+rh-projection[subs][x+rh]]]];
+	   selWM=makeFormalElement[projection[subs][selW],(anomW[#]*dimension[orth][#+rh-ortrh])&/@selW];
+	   selWM];
 
 
+eae=extendedAnomElement[b4,b2][wg];
 
+Part::partw: Part 2 of formalElement[table$655] does not exist.
 
+Part::partw: Part 2 of formalElement[table$655] does not exist.
 
-eae=extendedAnomElement[b4,b2][wg][[2]];
[…]

### 2011-05-18 src/affine.m
More debug

@@ -773,10 +773,10 @@ ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 	   rh=rho[rs];
 	   subrh=rho[subs];
 
-	   gamma0=Sort[fn[weights],#1.rh<#2.rh&][[1]];
+	   gamma0=Sort[fn[weights],#1.subrh<#2.subrh&][[1]];
 	   sgamma0=fn[gamma0];
 	   Print[gamma0,sgamma0];
-	   fn=fn- makeFormalElement[{gamma0},{sgamma0}];
+	   (*fn=fn- makeFormalElement[{gamma0},{sgamma0}];*)
 
 	   def=subrh-projection[subs][{rh}][[1]];
 (*	   Print[def];*)
@@ -787,7 +787,7 @@ ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 (*			 Print[v];
 			 Print[(fn[weights] /. x_?weightQ :> {v+x,res[toFC[v+x]],fn[x],selWM[v]})];*)
 			 res[v]=-1/sgamma0*(
-			 -selWM[v-gamma0]+
+			 selWM[v-gamma0]+
 			 Plus@@(fn[weights] /. x_?weightQ :> If[insideQ[v+x],fn[x]*res[toFC[v+x]],0]));
 (*			 Print[res[v]];*)
 			],

### 2011-05-18 tests/debug2.m

@@ -46,14 +46,9 @@ finiteWeight[4, {-, -, -, -}]
 Export["/home/anton/programing/Affine/tests/eanom.png",Graphics[Text[eae[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ eae[weights]]]
 
 
-br=ourBranching[b4,b2][wg+rho[b4]]
-
-finiteWeight[4, {0, 0, -2, -2}]1
-
-Out[34]= formalElement[table$911]
+br=ourBranching[b4,b2][wg]
 
 Export["/home/anton/programing/Affine/tests/brc.png",Graphics[Text[br[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ br[weights]]]
-
 
 br0=simpleBranching[b4,b2][wg]
 

### 2011-05-19 src/affine.m
We need to have toFundamentalChamber with parity

@@ -778,8 +778,9 @@ ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 	   Print[gamma0,sgamma0];
 	   (*fn=fn- makeFormalElement[{gamma0},{sgamma0}];*)
 
-	   def=subrh-projection[subs][{rh}][[1]];
-(*	   Print[def];*)
+(*	   def=subrh-projection[subs][{rh}][[1]];
+	   Print[def];*)
+	   def=-subrh;
 	   toFC=(toFundamentalChamber[subs][#-def]+def)&;
 	   res=makeHashtable[{},{}];
 	   insideQ:=NumberQ[res[toFC[#]]]&;

### 2011-05-20 src/affine.m
More debug. I need to implement branching without folding.

@@ -374,6 +374,12 @@ toFundamentalChamber[rs_?rootSystemQ][vec_?weightQ]:=
 		    vec,
 		    Head[#]=!=reflection[Null]&]]
 
+toFundamentalChamberWithParity[rs_?rootSystemQ][vec_?weightQ]:=
+    ({#[[1]][[1]],-#[[2]]})& @ NestWhile[Function[v,
+			     {reflection[Scan[If[#.v[[1]]<0,Return[#]]&,rs[simpleRoots]]][v[[1]]],-v[[2]]}],
+		    {vec,1},
+		    Head[#[[1]]]=!=reflection[Null]&]
+
 Expect["To fundamental chamber",True,makeFiniteWeight[{1,1/2}]==toFundamentalChamber[makeSimpleRootSystem[B,2]][makeFiniteWeight[{-1,1/2}]]]
 
 Expect["We can use this and other functions for mapping",True,
@@ -750,7 +756,7 @@ fan[rs_?rootSystemQ,subs_?rootSystemQ]:=
 getOrderedWeightsProjectedToWeylChamber[{algroots__?weightQ},subs_?rootSystemQ,hweight_?weightQ]:=
     Module[{rh=rho[subs]},
 	   Sort[
-	       Flatten[weightSystem[projection[subs][{algroots}]][projection[subs][{hweight}][[1]]]],
+	       Union[Flatten[weightSystem[Select[projection[subs][{algroots}],(#.rh>=0)&]][projection[subs][{hweight}][[1]]]]],
 	       #1.rh>#2.rh&]];
 
 
@@ -764,33 +770,37 @@ extendedAnomElement[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 	   selWM];
 
 ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
-    Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0},
+    Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0,hw},
 	   orth=orthogonalSubsystem[rs,subs];
 	   selWM=extendedAnomElement[rs,subs][highestWeight];
[…]

### 2011-05-20 tests/debug2.m

@@ -7,6 +7,36 @@ al=b4[simpleRoots];
 b={al[[3]],al[[4]]};
 b2=makeFiniteRootSystem[b];
 
+toFundamentalChamber[rs_?rootSystemQ][vec_?weightQ]:=
+    NestWhile[Function[v,
+			     reflection[Scan[If[#.v<0,Return[#]]&,rs[simpleRoots]]][v]],
+		    vec,
+		    Head[#]=!=reflection[Null]&]
+
+?NestWhile
+
+toFundamentalChamberWithParity[rs_?rootSystemQ][vec_?weightQ]:=
+    ({#[[1]][[1]],-#[[2]]})& @ NestWhile[Function[v,
+			     {reflection[Scan[If[#.v[[1]]<0,Return[#]]&,rs[simpleRoots]]][v[[1]]],-v[[2]]}],
+		    {vec,1},
+		    Head[#[[1]]]=!=reflection[Null]&]
+
+
+tmp=toFundamentalChamberWithParity[b2][makeFiniteWeight[{0,0,1,1}]]
+
+
+Out[15]= reflection[Null][finiteWeight[4, {0, 0, 1, 1}]]
+
+toFundamentalChamber[b2][makeFiniteWeight[{0,0,-1,-1}]]
+
+
+finiteWeight[4, {0, 0, -1, -1}]
+finiteWeight[4, {0, 0, -1, 1}]
+finiteWeight[4, {0, 0, 1, -1}]
+finiteWeight[4, {0, 0, 1, 1}]
+
+Out[12]= finiteWeight[4, {0, 0, 1, 1}]
+
 f=fan[b4,b2];
 
 Export["/home/anton/programing/Affine/tests/fan.png",Graphics[Text[f[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ f[weights]]]
@@ -17,11 +47,6 @@ wg=weight[b4][0,1,0,2]; (* makeFiniteWeight[{2,2,1,1}] *)
 aw=projection[b2][anomalousWeights[b4][wg]];
 
 Export["/home/anton/programing/Affine/tests/anom.png",Graphics[Text[aw[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ aw[weights]]]
[…]

### 2011-05-25 src/affine.m
B_2\subset B_4 example works correctly

@@ -785,6 +785,7 @@ ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 
 	   gamma0=Sort[fn[weights],#1.subrh<#2.subrh&][[1]];
 	   sgamma0=fn[gamma0];
+	   fn=fn*Exp[-gamma0];
 (*	   Print[gamma0,sgamma0];*)
 	   (*fn=fn- makeFormalElement[{gamma0},{sgamma0}];*)
 
@@ -792,15 +793,51 @@ ourBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 	   Print[def];*)
 	   def=-projection[subs][rh];
 	   toFC=Function[z,Module[{tmp=toFundamentalChamberWithParity[subs][z-def]},{tmp[[1]]+def,tmp[[2]]}]];
-	   res=makeHashtable[{},{}];
+	   res=makeHashtable[reprw,Table[0,{Length[reprw]}]];
 	   insideQ:=NumberQ[res[toFC[#][[1]]]]&;
 	   Scan[Function[v,
 			 Print[v];
-			 Print[(fn[weights] /. x_?weightQ :> {v+x,toFC[v+x],fn[x],fn[x]*res[toFC[v+x][[1]]]*toFC[v+x][[2]]})];
+(*			 Print[(fn[weights] /. x_?weightQ :> {v+x,toFC[v+x],fn[x],fn[x]*res[toFC[v+x][[1]]]*toFC[v+x][[2]]})];*)
 			 res[v]=-1/sgamma0*(
 			     -selWM[v-gamma0]+
 			     Plus@@(fn[weights] /. x_?weightQ :> If[insideQ[v+x],fn[x]*res[toFC[v+x][[1]]]*toFC[v+x][[2]],0]));
 			 Print[res[v]];
+			],
+		reprw];
+	   makeFormalElement[keys[res],values[res]]
+	  ]
+
+
+branching2[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
+    Module[{anomW,selW,selWM,fn,reprw,orth,res,toFC,rh,subrh,gamma0,sgamma0,hw},
+	   orth=orthogonalSubsystem[rs,subs];
+	   selWM=extendedAnomElement[rs,subs][highestWeight];
+
+	   rh=rho[rs];
+	   subrh=rho[subs];
[…]

### 2011-05-25 tests/debug2.m

@@ -39,14 +39,14 @@ Out[12]= finiteWeight[4, {0, 0, 1, 1}]
 
 f=fan[b4,b2];
 
-Export["/home/anton/programing/Affine/tests/fan.png",Graphics[Text[f[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ f[weights]]]
+Export["/home/anton/programing/Affine/tests/fan.png",Graphics[Text[f[#],{#[standardBase][[4]],#[standardBase][[3]]}] & /@ f[weights]]]
 
 Out[5]= /home/anton/programing/Affine/tests/fan.png
 
 wg=weight[b4][0,1,0,2]; (* makeFiniteWeight[{2,2,1,1}] *)
 aw=projection[b2][anomalousWeights[b4][wg]];
 
-Export["/home/anton/programing/Affine/tests/anom.png",Graphics[Text[aw[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ aw[weights]]]
+Export["/home/anton/programing/Affine/tests/anom.png",Graphics[Text[aw[#],{#[standardBase][[4]],#[standardBase][[3]]}] & /@ aw[weights]]]
 
 extendedAnomElement[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
     Module[{anomW,selW,selWM,rh=rho[rs],orth,ortrh},
@@ -60,15 +60,128 @@ extendedAnomElement[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 
 eae=extendedAnomElement[b4,b2][wg];
 
-Export["/home/anton/programing/Affine/tests/eanom.png",Graphics[Text[eae[#],{#[standardBase][[3]],#[standardBase][[4]]}] & /@ eae[weights],Axes->True]]
+Export["/home/anton/programing/Affine/tests/eanom.png",Graphics[Text[eae[#],{#[standardBase][[4]],#[standardBase][[3]]}] & /@ eae[weights],Axes->True]]
+
+
+rh=rho[b4]
+
+def=projection[b2][{rh}][[1]]
+
+[Calculating...]
+
[…]

### 2011-05-25 doc/paper.tex
Some changes in theoretical part.

@@
 Algorithms are based upon the properties of weights and Weyl symmetry.
-Central problems are weight multiplicity computation, branching of representation to representations of subalgebra and tensor product decomposition.
+Weight multiplicity computation, branching of representation to representations of subalgebra and tensor product decomposition are the most important problems that we treat.
 These problems has numerous applications in physics.
 
-Unique features of our programs are the treatment of affine Lie algebras and implementation in popular computer algebra system {\it Mathematica}.
+The program is implemented in popular  computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
 
@@
 Representation theory of finite-dimensional Lie algebras has many applications in different branches of physics, including elementary particle physics, molecular physics, nuclear physics.
-Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory which is used for the description of critical phenomena in two-dimensional systems.
+Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory used for the description of critical phenomena in two-dimensional systems.
 Also Lie symmetries play major role in study of quantum integrable systems.
@@
 Lie algebras are used to for the description of symmetries of quantum and classical systems.
-Computational method in representation theory have long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
+Computational method in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
 
@@
 \begin{enumerate}
-\item Construction of root system which is used for compact description of algebra commutation relations.
+\item Construction of root system which determine the properties of Lie algebra including its algebra commutation relations.
 \item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
-\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for the construction and study of representations. 
+\item Calculation of weight multiplicities, branching and fusion coefficients, which are essential for construction and study of representations. 
 \end{enumerate}
@@
 
-Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and study of quantum integrable systems.
+Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and study of number integrable systems.
 But infinite-dimensional algebras are much harder to study and quantity of available computer programs is much smaller.
@@
 
-Construction of affine Lie algebras allows to extend computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
+The structure of affine Lie algebras allows to extend computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
 The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of algebras and representations was published in 1990.
@@
 We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
+We describe the features and limitations of the package in present paper and in the manual \cite{affinemanual}.
+In present paper we also provide representation-theoretical background of implemented algorithms and present some examples of computations relevant to physics.
 
-Our package can be used for study of root and weight systems, Weyl groups, subalgebras, computations of weight multiplicities, branching and fusion coefficients.
-We describe the features and limitations of the package in present paper and in the manual \cite{affinemanual}.
-In present paper we also provide representation-theoretical background of implemented algorithms and present some example of computations relevant to physics.
-
-The paper is started with overview of Lie algebras and their representation theory (Sec.
+The paper is started with an overview of Lie algebras and their representation theory (Sec.
 \ref{sec:theor-backgr}).
@@
 
-\subsection{Lie algebras of finite and affine type}
+\subsection{Lie algebras of finite and affine types}
 \label{sec:lie-algebras-finite}
@@
 
-Killing form gives non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be extended to the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
+Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
 Weights are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
@@
 Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
-This basis can be encoded by the root system  which is the set of vectors in  $\hfg^{*}$ satisfying certain properties (See e.g.
-\cite{humphreys1997introduction,humphreys1992reflection} for details).
+This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
 
@@
 \end{equation}
-Central extension leads to the appearance of additional term in commutation relations
+Central extension leads to the appearance of additional term 
 \begin{equation}
@@
 \end{equation}
-Representation of algebra $\gf$ on vector space $V$ is the homomorphism $\gf\to gl(V)$.
+Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$.
 
-For an arbitrary representation it is possible to diagonalize Cartan generators $H^{i}$ simultaneously by special choice of basis $\{v_{j}\}$ in $V$:
+For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by special choice of basis $\{v_{j}\}$ in $V$:
 \begin{equation}
@@
 \end{equation}
-Eigenvalues of Cartan generators on element of basis $v_{j}$ are given by weight $\nu_{j}\in \hfg^{*}: \nu_{j}(H^{i})=\nu_{j}^{i}$.
+Eigenvalues $\nu^{i}_{j}$ of Cartan generators on element of basis $v_{j}$ determine weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
 Vector $v\in V$ is called weight vector of weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$ , weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
@@
 
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on a weight vectors is
 \begin{equation}
@@
 \end{equation}
-Character  $\mathrm{ch}V\in \mathcal{E}$ is the element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-It is possible to specialise character by taking its value on some element $\xi$ of $\hf$:
+Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+Character can be specialized by taking its value on some element $\xi$ of $\hf$:
 
@@
 Denote by $\Delta$ the set of roots.
-For each $\alpha\in \Delta$ there exist root $-\alpha\in \Delta$ and generators $E^{\alpha}, E^{-\alpha}$ such that
+For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and generators $E^{\alpha}, E^{-\alpha}$ such that
 \begin{align}
@@
 
-%%  Given a root system Φ we can always choose (in many ways) a set of positive roots. This is a subset Φ + of Φ such that
-%%  
-%%      * For each root \alpha\in\Phi exactly one of the roots α, –α is contained in Φ + .
-%%      * For any two distinct \alpha, \beta\in \Phi^+ such that α + β is a root, \alpha+\beta\in\Phi^+.
-%%  
-%%  If a set of positive roots Φ + is chosen, elements of –Φ + are called negative roots.
-%%  
-%%  An element of Φ + is called a simple root if it cannot be written as the sum of two elements of Φ + .
-The set Δ of simple roots is a basis of V with the property that every vector in Φ is a linear combination of elements of Δ with all coefficients non-negative, or all coefficients non-positive.
-For each choice of positive roots, the corresponding set of simple roots is the unique set of roots such that the positive roots are exactly those that can be expressed as a combination of them with non-negative coefficients, and such that these combinations are unique.
-%%  
-%%  Ordering. Highest root. Rho=sum of fundamental weights, not half-sum of positive roots.
+Given a root system $\Delta$ we can choose a set of positive roots.
+This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
+Elements of $-\Delta^{+}$ are called negative roots.
 
-In the root system $\Delta$ exist simple roots $\left\{\alpha_{i}\right\}$, such that $\alpha=\sum_{i}n_{i}\alpha_{i},\; \forall\alpha\in \Delta$.
-In case of finite-dimensional Lie algebra $\gf$ $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-Although the full set of roots $\Delta$ is infinite for affine Lie algebra $\hat\gf$ the number of simple roots is finite and are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
-The roots $\alpha_1,\dots, \alpha_r$ are equal to the roots of the underlying finite-dimensional Lie algebra $\go$.
-The root $\alpha_0=\delta-\theta$ is equal to the difference of {\it imaginary root} $\delta$ and $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$ -- highest root of algebra $\go$, coefficients $a_i$ are called {\it marks}.
-{\it Comarcs} are equal to $a_i^v=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+A positive root is simple if it cannot be written as the sum of positive roots.
+The set of simple roots $\left\{\alpha_{i}\right\}$ is a basis of $\hfg$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive.
+In case of finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to rank of the algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+By numbering simple roots with an index $i$ we introduce an ordering on the root system $\Delta$.
+Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
+{\it Comarcs} are equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
 
-Roots system can be reconstructed from the set of simple roots with the use of Weyl group $W_{\gf}$ which is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
+Although the full set of roots $\Delta$ is infinite for affine Lie algebra $\hat\gf$ the number of simple roots is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
+The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- highest root of the algebra $\go$.
+
+Sub-algebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for $\alpha\in \Delta^{+}$ positive is called Borel sub-algebra.
+
+{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
+
+{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ which is a subset of set of simple roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{\Theta\}$ with the addition of highest root.
+
+The Weyl group $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
 \begin{equation}
@@
 
+Root system and characters of representation are invariant with respect to the action of Weyl group. Root system can be reconstructed from the set of simple roots with the action of Weyl group.
+
 Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
-In the latter case of $\hat\gf$ Weyl group can be presented as semidirect product of Weyl group $W_{\gf}$ of $\gf$ and translations by the roots of $\hat \gf$.
+
+Consider an action of element $s_{0}s_{i}s_{0}$ of Weyl group of affine Lie algebra  $\hat\gf$.
+Using the definition \eqref{eq:8} it is easy to see that $s_{0}s_{i}s_{0}\cdot \lambda=\lambda+\alpha_{i}$, so Weyl group can be presented as semidirect product of Weyl group $W_{\gf}$ of $\gf$ and translations by the roots of $\hat \gf$.
 
@@
 
-Cartan matrix $A$ is defined by products of simple roots
+The Cartan matrix $A$ is defined by products of simple roots
 \begin{equation}
@@
 
-The form \eqref{eq:9} induces the basis in ${\cal L}P$ dual  to the simple
+The form \eqref{eq:9} induces the basis dual  to the simple
 roots basis. It is called the fundamental weights basis. We denote
-its elements by $\omega_i$.
+its elements by $\omega_i$:
 \begin{equation}
   \label{eq:20}
-  \langle\omega_i,\alpha_j\rangele=\frac{(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
+  \langle\omega_i,\alpha_j\rangle=\frac{(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
 \end{equation}
-For finite-dimensional Lie algebra $i=1,\dots, r$.
-For affine Lie algebra $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+For finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
+For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
 Other fundamental weights are equal to $\omega_i=a_i^v \lambda_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of finite-dimensional Lie algebra $\go$.
@@
 
-We consider $\gf$-modules of the category $\mathcal{O}$, i.e.
-such $V$ that $V=\bigoplus_{\lambda\in \hfg^{*}} V_{\lambda}$, where each $V_{\lambda}$ is finite-dimensional and there exists finite set $\lambda_{1},\dots \lambda_{s}$ such that $V_{\lambda}\neq 0 \Rightarrow \lambda=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$, where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
+We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates weight system of $V$, i.e.
+if $V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
 
@@
   \label{eq:17}
-  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D_{\lambda}(\bff_{+}),
+  M^{\mu}=U(\gf)\underset{U(\bff_{+})}{\otimes} D^{\mu}(\bff_{+}),
 \end{equation}
-where $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' left part of tensor product onto the right part.
-Here $\bff_{+}$ is Borel sub-algebra, $D_{\lambda}(\bff_{+})$ is a special representation of $\bff_{+}$, such that $D(E^{\alpha})=0,\; D(h)=\lambda(h)$ for any positive root $\alpha$.
-Elements of $\gf$ act from the left, so we should expand element of $\gf$ in some basis, and then commute all the elements of $\bff_{+}$ to the right, so that they can act on space $D_{\lambda}(\bff_{+})$.
+with respect to the multiplication in $U(\gf)$, 
+where $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
+Here $\bff_{+}$ is Borel sub-algebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
+Elements of $\gf$ act from the left and we should all the elements of $\bff_{+}$ to the right, so that they can act on the space $D_{\lambda}(\bff_{+})$.
 
@@
 
-Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by the representation of some parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset of simple roots $I\subset \{\alpha_{1},\dots, \alpha_{r}\}$:
+Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by the representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
 \begin{equation*}

### 2011-05-26 src/affine.m
Some unit tests

@@ -221,13 +221,13 @@ prependZeros::"usage"=
     "prependZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by prepending num zeros to its coordinates";
 prependZeros[num_Integer,vec_finiteWeight]:=makeFiniteWeight[Join[Table[0,{num}],vec[standardBase]]];
 
-Expect["prependZeros",True,makeFiniteWeight[{0,0,1,1}]==prependZeros[2,makeFiniteWeight[{1,1}]]];
+Expect["prependZeros",True,makeFiniteWeight[{0,0,1,1}]==prependZeros[2,makeFiniteWeight[{1,1}]]]
 
 appendZeros::"usage"=
     "appendZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by appending num zeros to its coordinates";
 appendZeros[num_Integer,vec_finiteWeight]:=makeFiniteWeight[Join[vec[standardBase],Table[0,{num}]]];
 
-Expect["appendZeros",True,makeFiniteWeight[{1,1,0,0,0}]==appendZeros[3,makeFiniteWeight[{1,1}]]];
+Expect["appendZeros",True,makeFiniteWeight[{1,1,0,0,0}]==appendZeros[3,makeFiniteWeight[{1,1}]]]
 
 Plus::"usage"=Plus::"usage" <> "\n Direct sum of finite-dimensional and affine Lie algebras can be specified as sum of root systems";
 finiteRootSystem/:x_finiteRootSystem+y_finiteRootSystem:=makeFiniteRootSystem[Join[Map[appendZeros[y[dimension],#]&,x[simpleRoots]],
@@ -239,7 +239,7 @@ Module[{b2=makeSimpleRootSystem[B,2],a3=makeSimpleRootSystem[A,3]},
 					   {0,1,0,0,0,0},
 					   {0,0,1,-1,0,0},
 					   {0,0,0,1,-1,0},
-					   {0,0,0,0,1,-1}}]]];
+					   {0,0,0,0,1,-1}}]]]
 
 
 affineRootSystem/:x_affineRootSystem+y_affineRootSystem:=makeAffineExtension[x[finiteRootSystem]+y[finiteRootSystem]];
@@ -250,7 +250,7 @@ Module[{b2=makeSimpleRootSystem[B,2],a3=makeSimpleRootSystem[A,3]},
 					   {0,1,0,0,0,0},
 					   {0,0,1,-1,0,0},
 					   {0,0,0,1,-1,0},
[…]

### 2011-05-26 tests/debug2.m
Some tests

@@ -2,10 +2,126 @@ AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
 <<affine.m;
 
+
+
+Throw::nocatch: 
+   Uncaught Throw[Dynkin labels of sl(3) root: GOT UNEXPECTED VALUE False
+      INSTEAD OF True, assertion exception] returned to top level.
+
+Out[45]= Hold[Throw[Dynkin labels of sl(3) root: GOT UNEXPECTED VALUE False\
+ 
+>      INSTEAD OF True, assertion exception]]
+
+Module[{rs=makeSimpleRootSystem[B,2]},dynkinLabels[rs][rs[simpleRoot][1]]=={2,-2}]
+
+dynkinLabels[makeSimpleRootSystem[B,2]][makeSimpleRootSystem[B,2][simpleRoot][1]]
+
+Out[50]= {2, -2}
+
+Out[46]= {1, -1}
+
+fundamentalWeights[makeSimpleRootSystem[B,2]]
+
+makeSimpleRootSystem[B,2][simpleRoots]
+
+Out[44]= {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}
+
+                                                    1  1
+Out[43]= {finiteWeight[2, {1, 0}], finiteWeight[2, {-, -}]}
+                                                    2  2
+
+Out[42]= {2, -1}
+
+Out[41]= {2, 0, -1}
+
+Out[40]= False
+
+Throw::nocatch: 
+   Uncaught Throw[Dynkin labels of so(5) root: GOT UNEXPECTED VALUE False
+      INSTEAD OF True, assertion exception] returned to top level.
+
+Out[39]= Hold[Throw[Dynkin labels of so(5) root: GOT UNEXPECTED VALUE False\
+ 
+>      INSTEAD OF True, assertion exception]]
+
 b4=Subscript[B,4];
 al=b4[simpleRoots];
 b={al[[3]],al[[4]]};
 b2=makeFiniteRootSystem[b];
+
+b2=makeAffineExtension[makeSimpleRootSystem[B,2]];
+
+weylGroupElement[b2][0,0,0] @ makeAffineWeight[{1,2},1,1]
+
+Out[15]= affineWeight[2, finiteWeight[2, {-1, 0}], 1, 3]
+
[…]

### 2011-05-26 src/affine.m
regular subalgebra

@@ -214,6 +214,7 @@ makeFiniteRootSystem[{roots__List}]:=makeFiniteRootSystem[makeFiniteWeight/@{roo
 finiteRootSystem/:x_finiteRootSystem[rank]:=x[[1]];
 finiteRootSystem/:x_finiteRootSystem[dimension]:=x[[2]];
 finiteRootSystem/:x_finiteRootSystem[simpleRoots]:=x[[3]];
+finiteRootSystem/:x_finiteRootSystem[simpleRoot][0]:=highestRoot[x];
 finiteRootSystem/:x_finiteRootSystem[simpleRoot][n_Integer]:=x[[3]][[n]];
 
 
@@ -362,7 +363,7 @@ rho::"usage"=
     "rho[rs_?rootSystemQ] - Weyl vector of root system rs (sum of fundamental weights)";
 rho[rs_?rootSystemQ]:=Plus@@fundamentalWeights[rs];
 
-rho[{posroots__?weightQ}]:=1/2*(Plus@@{posroots});
+rho[{posroots__finiteWeight}]=1/2*(Plus@@{posroots});
 
 Expect["Weyl vector for B2",True,makeFiniteWeight[{3/2,1/2}]==rho[makeSimpleRootSystem[B,2]]]
 
@@ -488,21 +489,21 @@ dimension[rs_?rootSystemQ][hweight_?weightQ]:=dimension[positiveRoots[rs]][toFun
 Expect["Dimension",5, dimension[makeSimpleRootSystem[A,1]][makeFiniteWeight[{2}]]];
 
 weightSystem::"usage"=
-    "weightSystem[rs_?rootSystemQ][higestWeight_?weightQ] returns the set of dominant weights in the highest weight module. \n
+    "weightSystem[rs_?rootSystemQ][highestWeight_?weightQ] returns the set of dominant weights in the highest weight module. \n
     The list is split in pieces by number of root substractions";
 
-weightSystem[{posroots__?weightQ}][higestWeight_?weightQ]:=Module[{minusPosRoots=-{posroots},mgrade=Max[grade/@{posroots}]},
+weightSystem[{posroots__?weightQ}][highestWeight_?weightQ]:=Module[{minusPosRoots=-{posroots},mgrade=Max[grade/@{posroots}]},
 (*								  Throw["_TODO_","not implemented"];*)
[…]

### 2011-05-26 src/affine.m
Almost full test-coverage. Slowness is discovered.

@@ -363,9 +363,11 @@ rho::"usage"=
     "rho[rs_?rootSystemQ] - Weyl vector of root system rs (sum of fundamental weights)";
 rho[rs_?rootSystemQ]:=Plus@@fundamentalWeights[rs];
 
-rho[{posroots__finiteWeight}]=1/2*(Plus@@{posroots});
+rho[{posroots__finiteWeight}]:=1/2*(Plus@@{posroots});
 
 Expect["Weyl vector for B2",True,makeFiniteWeight[{3/2,1/2}]==rho[makeSimpleRootSystem[B,2]]]
+
+Expect["Weyl vector for B2",True,makeFiniteWeight[{3/2,1/2}]==rho[positiveRoots[makeSimpleRootSystem[B,2]]]]
 
 toFundamentalChamber::"usage"=
     "toFundamentalChamber[rs_?rootSystemQ][vec_?weightQ] acts on a weight vec by simple reflections of rs till it gets to main Weyl chamber";
@@ -714,11 +716,15 @@ formalElement/:fe_formalElement[weights]:=keys[fe[[1]]];
 
 formalElement/:fe_formalElement[multiplicities]:=values[fe[[1]]];
 
+formalElement/:x_formalElement==y_formalElement:=x[weights]==y[weights] && x[multiplicities]==y[multiplicities];
+
 makeFormalElement::"usage"=
     "makeFormalElement[{weights___?weightQ},{multiplicities___?NumberQ}] creates formal element with given weights and corresponding multiplicities\n
     makeFormalElement[{weights__?weightQ}] creates formal element where weight multiplicity is calculated as the number of appearances of weight in arguments list"
 
 makeFormalElement[{weights___?weightQ},{multiplicities___?NumberQ}]:=formalElement[makeHashtable[{weights},{multiplicities}]];
+
+Expect["Formal element construction", 2, makeFormalElement[{makeFiniteWeight[{1,2}],makeFiniteWeight[{3,4}]},{2,3}][makeFiniteWeight[{1,2}]]]
 
 makeFormalElement[{weights__?weightQ}]:=
     Module[{res},
@@ -726,7 +732,13 @@ makeFormalElement[{weights__?weightQ}]:=
[…]

### 2011-05-26 tests/debug2.m

@@ -2,6 +2,180 @@ AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
 <<affine.m;
 
+Module::lvsym: Local variable specification 
+    {b4 = makeSimpleRootSystem[B, 4], b2, wg, fe . mcw} contains fe . mcw
+    , which is not a symbol or an assignment to a symbol.
+
+Expect["Our branching", True, 
+       Module[{b4=makeSimpleRootSystem[B,4],b2,wg},
+	      b2=regularSubalgebra[b4][3,4];
+	      wg=weight[b4][0,1,0,2];
+	      Union[ourBranching[b4,b2][wg][multiplicities]]=={0,6,10,19,30,40,60}]]
+
+Expect["branching2", True, 
+
+
+       Module[{b4=makeSimpleRootSystem[B,4],b2,wg},
+	      b2=regularSubalgebra[b4][3,4];
+	      wg=weight[b4][0,1,0,2];
+	      branching2[b4,b2][wg][multiplicities]]
+
+       Module[{b4=makeSimpleRootSystem[B,4],b2,wg,fe,mcw},
+	      b2=regularSubalgebra[b4][3,4];
+	      wg=weight[b4][0,1,0,2];
+	      fe=branching2[b4,b2][wg];
+	      mcw=Select[fe[weights],mainChamberQ[b2]];
+	      Union[fe/@mcw]]
+
+                                             
+Out[10]= {0, 6, 10, 19, 30, 40, 60}
+
+                                        
+Union::normal: Nonatomic expression expected at position 1 in Union[mcs].
+
+Out[9]= Union[mcs]
+
+                                        
+Module::lvsym: Local variable specification 
+    {b4 = makeSimpleRootSystem[B, 4], b2, wg, fe . mcw} contains fe . mcw
+    , which is not a symbol or an assignment to a symbol.
+
+Out[8]= Module[{b4 = makeSimpleRootSystem[B, 4], b2, wg, fe . mcw}, 
+ 
+>    b2 = regularSubalgebra[b4][3, 4]; wg = weight[b4][0, 1, 0, 2]; 
+ 
+>     fe = branching2[b4, b2][wg]; 
+ 
+>     mcw = Select[fe[weights], mainChamberQ[b2]]; Union[fe /@ mcs]]
+
+
+                        
[…]

### 2011-05-27 src/affine.m
Optimisation and plotting

@@ -55,25 +55,27 @@ Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
 
 Dot::"usage"=Dot::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";
 
-finiteWeight/:x_finiteWeight . y_finiteWeight/;x[dimension]==y[dimension]:=x[standardBase].y[standardBase]
+finiteWeight/:x_finiteWeight . y_finiteWeight:=x[standardBase].y[standardBase]
 
 Expect["Scalar product for vectors from weight space of finite-dimensional Lie algebras",
        10,makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1}]]
 
+(*
 Expect["Scalar product for vectors from different spaces are left unevaluated",True,
        MatchQ[makeFiniteWeight[{1,2,3}].
 	      makeFiniteWeight[{3,2,1,2}],x_finiteWeight . y_finiteWeight]]
-
+*)
 Plus::"usage"=Plus::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";
 
-finiteWeight/:x_finiteWeight+y_finiteWeight/;x[dimension]==y[dimension]:=
+finiteWeight/:x_finiteWeight+y_finiteWeight:=
     makeFiniteWeight[x[standardBase]+y[standardBase]]
 
 Expect["Plus for finite-dimensional weights",{2,4,6},(makeFiniteWeight[{1,2,3}]+makeFiniteWeight[{1,2,3}])[standardBase]]
 
-Expect["Plus product for vectors from different spaces are left unevaluated",True,
+(*
+Expect["Plus  for vectors from different spaces are left unevaluated",True,
        MatchQ[makeFiniteWeight[{1,2,3}]+makeFiniteWeight[{3,2,1,2}],x_finiteWeight + y_finiteWeight]]
-
+*)
 Equal::"usage"=Equal::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";
 
 finiteWeight/:x_finiteWeight==y_finiteWeight:=x[standardBase]==y[standardBase]
@@ -141,7 +143,7 @@ Expect["Equal for affine weights compares finite parts, levels and grades", True
 
[…]

### 2011-05-27 tests/debug2.m

@@ -1,16 +1,142 @@
 AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
+Mathematica 8.0 for Linux x86 (64-bit)
+Copyright 1988-2010 Wolfram Research, Inc.
+
 <<affine.m;
+
+b4=makeSimpleRootSystem[B,10]
+
+pr=positiveRoots[b4];
+
+Length[pr]
+
+Out[5]= 100
+
+[Calculating...]
+
+rho[b4]
+
+
+
+                          19  17  15  13  11  9  7  5  3  1
+Out[6]= finiteWeight[10, {--, --, --, --, --, -, -, -, -, -}]
+                          2   2   2   2   2   2  2  2  2  2
+
+Out[8]= $Aborted
+
+                         15  13  11  9  7  5  3  1
+Out[6]= finiteWeight[8, {--, --, --, -, -, -, -, -}]
+                         2   2   2   2  2  2  2  2
+
+                         7  5  3  1
+Out[4]= finiteWeight[4, {-, -, -, -}]
+                         2  2  2  2
+
+Out[3]= finiteRootSystem[4, 4, {finiteWeight[4, {1, -1, 0, 0}], 
+ 
+>     finiteWeight[4, {0, 1, -1, 0}], finiteWeight[4, {0, 0, 1, -1}], 
+ 
+>     finiteWeight[4, {0, 0, 0, 1}]}]
+
+Dot::dotsh: Tensors {1, 2} and {3, 2, 1} have incompatible shapes.
+
+Throw::nocatch: 
+   Uncaught Throw[We compare dimensions of vectors before product calculation,
+      the expression is left unevaluated in case of dimension mismatch : GOT
+      UNEXPECTED VALUE False INSTEAD OF True, ass<<13>>ion] returned to top
+     level.
+
+Out[2]= Hold[Throw[We compare dimensions of vectors before product\
+ 
+>      calculation, the expression is left unevaluated in case of dimension\
+ 
+>      mismatch : GOT UNEXPECTED VALUE False INSTEAD OF True, 
+ 
+>     assertion exception]]
+
+Thread::tdlen: Objects of unequal length in {1, 2} + {3, 2, 1}
+     cannot be combined.
+
+Throw::nocatch: 
+   Uncaught Throw[We compare dimensions of vectors before sum calculation, the
+      expression is left unevaluated in case of dimension mismatch : GOT
[…]

### 2011-05-27 doc/paper.tex
First premature pictures in the paper. Some optimisation of affine.m

@@
 We have made some experiments with our implementations of Freudenthal formula and formula \eqref{eq:15} and have got the following graphs \ref{freudenthal-racah-times}.
+\begin{figure}[h]
+  \label{freudenthal-racah-times}
+  \noindent\centering{
+    \includegraphics[width=80mm]{timing.pdf}
+  }
+  \caption{Running time of algorithms based on recurrent formula \eqref{eq:15} (in blue) and \eqref{eq:14} (in red) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
+\end{figure}
 
@@
 
+\begin{figure}[h]
+  \label{branching-b4-b2}
+  \noindent\centering{
+    \includegraphics[width=80mm]{branching.pdf}
+  }
+  \caption{Branching coefficients of module $L^{\left[0,1,0,2\right]}$ for regular embedding $B_{2}\subset B_{4}$ displayed in the basis $\left\{e_3,e_4\right\}$}
+\end{figure}
+
 \section{Conclusion}
@@
 
+\newpage
 %% The Appendices part is started with the command \appendix;

### 2011-05-27 src/affine.m

@@ -49,7 +49,8 @@ finiteWeight/:x_finiteWeight[finitePart]:=x;
 makeFiniteWeight::"usage"=
     "makeFiniteWeight[{coordinates__?NumberQ}] creates finiteWeight with given coordinates in standard base";
 
-makeFiniteWeight[{coordinates__?NumberQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}
+(*makeFiniteWeight[{coordinates__?NumberQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}*)
+makeFiniteWeight[{coordinates__}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}
 
 Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
 
@@ -67,8 +68,13 @@ Expect["Scalar product for vectors from different spaces are left unevaluated",T
 *)
 Plus::"usage"=Plus::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";
 
+finiteWeight/:Plus[wgs__finiteWeight]:=
+    makeFiniteWeight[Plus @@ (#[standardBase]&/@ {wgs})]
+    
+(*
 finiteWeight/:x_finiteWeight+y_finiteWeight:=
     makeFiniteWeight[x[standardBase]+y[standardBase]]
+*)
 
 Expect["Plus for finite-dimensional weights",{2,4,6},(makeFiniteWeight[{1,2,3}]+makeFiniteWeight[{1,2,3}])[standardBase]]
 
@@ -469,7 +475,8 @@ SubValues[finiteWeight]
 
 dimension::"usage"=
     "dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra highest weight representation";
-dimension[{pr__?weightQ}][hweight_?weightQ]:=
+(*dimension[{pr__?weightQ}][hweight_?weightQ]:=*)
+dimension[{pr__}][hweight_]:=
     Module[{rh=rho[{pr}]},
 	   Times@@((  (#.(hweight+rh))/(rh.#) )&/@{pr})];
 
@@ -932,7 +939,9 @@ Expect["branching2", True,
 
 
 drawPlaneProjection[axe1_,axe2_,f_formalElement]:=
[…]

### 2011-05-27 tests/debug2.m

@@ -5,7 +5,511 @@ Copyright 1988-2010 Wolfram Research, Inc.
 
 <<affine.m;
 
-b4=makeSimpleRootSystem[B,10]
+b4=makeSimpleRootSystem[B,4];
+
+wg=weight[b4][0,1,0,2];
+
+pr=positiveRoots[b4];
+
+dimension[pr][wg]
+
+Out[11]= 2772
+
+Out[6]= $Aborted
+
+rho[pr]//Timing
+
+                              7  5  3  1
+Out[9]= {0., finiteWeight[4, {-, -, -, -}]}
+                              2  2  2  2
+
+                         7  5  3  1
+Out[8]= finiteWeight[4, {-, -, -, -}]
+                         2  2  2  2
+
+rho[b4]
+
+                         7  5  3  1
+Out[6]= finiteWeight[4, {-, -, -, -}]
+                         2  2  2  2
+
+
+
+Plus @@ Table[makeFiniteWeight[{i,i}],{i,120}]//Timing
+
+Out[4]= {0.012001, finiteWeight[2, {7260, 7260}]}
+
+Out[3]= {0., finiteWeight[2, {78, 78}]}
+
+Out[27]= {1.25208, finiteWeight[2, {78, 78}]}
+
+Out[26]= {0.408026, finiteWeight[2, {66, 66}]}
+
+         finiteWeight[2, {66, 66}]
+Out[25]= -------------------------
+                  Timing
+
+Out[24]= finiteWeight[2, {66, 66}]
+
+Out[23]= finiteWeight[2, {55, 55}]
+
+Out[22]= finiteWeight[2, {45, 45}]
+
+Out[21]= finiteWeight[2, {15, 15}]
+
+finiteWeight/:Plus[wgs__finiteWeight]:=
+    makeFiniteWeight[Total[ (#[standardBase]&/@ {wgs})]]
+
+
+
+
+makeFiniteWeight[Total[(#[standardBase]&/@Table[makeFiniteWeight[{i,i}],{i,154}])]]
+
+Out[17]= finiteWeight[2, {11935, 11935}]
+
+Out[16]= {11935, 11935}
+
+Out[15]= {11325, 11325}
+
[…]

### 2011-05-30 src/affine.m
Trying to optimize formalElement

@@ -192,6 +192,8 @@ keys = DownValues[#,Sort->False][[All,1,1,1]]&;
 values::"usage"="values[hashtable] gives all the values in hashtable (in the same order as keys)";
 values = Function[ht,(ht[#]&)/@keys[ht]]
 
+hasKey[hashtable_,key_]:=hashtable[key]=!=Unevaluated[hashtable[key]]
+
 makeHashtable::"usage"=
     "makeHashtable[keys_List,values_List] creates hashtable from the list keys and list of values";
 makeHashtable[keys_List,values_List]/; Length[keys]==Length[values] :=
@@ -721,8 +723,9 @@ formalElement::"usage"=
     fe_formalElement[hashtable] returns formalElement's data as hashtable\n
 "
 
-formalElement/:fe_formalElement[weight_?weightQ]/;NumberQ[fe[[1]][weight]]:=fe[[1]][weight];
-formalElement/:fe_formalElement[weight_?weightQ]:=0;
+(* formalElement/:fe_formalElement[weight_?weightQ]/;NumberQ[fe[[1]][weight]]:=fe[[1]][weight];*)
+
+formalElement/:fe_formalElement[weight_?weightQ]:=If[hasKey[fe[[1]],weight], fe[[1]][weight], 0]
 
 formalElement/:fe_formalElement[weights]:=keys[fe[[1]]];
 

### 2011-05-31 doc/paper.tex
Trying to optimize formalElement
CirclePlus for direct sum of the algebras. List of examples in the paper. Entrance for paper of Lyakhovsky and Postnova in the bibliography.

@@
 
-Weyl vector is denoted by $\rho=\sum_{i} \omega_{i}$, it is of importance for 
+We need to introduce Weyl vector denoted by $\rho=\sum_{i} \omega_{i}$. It is of importance for the construction of algebra modules.
+
 \subsection{Highest weight modules}
@@
 
+\subsection{Tensor product decompositon for finite-dimensional Lie algebras}
+\label{sec:tens-prod-decomp}
+
+Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
+For example, we can consider spin of composite system such as atom.
+Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of Lie algebra $\gf$ with $\gf$-invariant Hamiltonian $H$, describing nearest-neighbour spin-spin interaction.
+In order to solve such system, i.e.
+find eigenstates of Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
+
+For fundamental representations of simple Lie algebras it is sometimes possible to get analytic result for the dependence of decomposition coefficients on $N$ (See \cite{2011LyakhovskyPostnova}).
+Our code give numerical values and can be used to check this analytic results.
+
+\begin{figure}[h]
+  \label{tensor-product-decomposition-b2}
+  \noindent\centering{
+    \includegraphics[width=80mm]{branching.pdf}
+  }
+  \caption{Fusion coefficients for $\left(L^{(1,0)}\right)^{\otimes 10}$}
+\end{figure}
+
+\subsection{Branchig and parabolic Verma modules}
+\label{sec:branch-parab-verma}
+
+We illustrate the connection of branching with generalized BGG-resolution with the sequence of parabolic Verma modules which appear in the study of branching of irreducible $B_{2}$-modules to the modules of subalgebra $A_{1}$.
+Root of the subalgebra $A_{1}$ in this case is equal to the highest root $\Theta$ of algebra $B_{2}$.
+In this case orthogonal sub-algebra $\afb$ gives rise to the parabolic Verma modules \cite{2011arXiv1102.1702L}.
+
+\begin{figure}[h]
+  \label{branching-bgg}
+  \noindent\centering{
+    \includegraphics[width=80mm]{branching.pdf}
+  }
+  \caption{Parabolic Verma modules from branching}
+\end{figure}
+
+\subsection{String functions of affine Lie algebras and CFT models}
+\label{sec:string-funct-affine}
+
+String functions can be used to present the formal character of affine Lie algebra highest weight representation.
+They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.
+
+String functions can be given physical meaning if we consider coset models of two-dimensional conformal field theory \cite{Goddard198588}, \cite{difrancesco1997cft}.
+String functions of $\hat\gf$ are equal to branching functions in the case of subalgebra $\hat{u(1)}$ and can be seen as the partition functions of $\hat\gf/\hat{u(1)}$ coset model on the torus.
+
+{\bf Affine.m} produces power series decomposition for string functions.
+Consider affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ highest weight module $L^{(1,0,0)}$.
+To get string functions we can use the code:
+\begin{lstlisting}[mathescape=true]
+stringFunciton[$\hat A_2$][weight[$\hat A_{2}$][1,0,0]][weight[$\hat A_{2}$][0,1,0]]
+$1+q^2 +q^{3}+\dots$
+\end{lstlisting}
+
+\subsection{Branching functions and coset models of conformal field theory}
+\label{sec:branch-funct-coset}
+
+More complex models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$. These models can be studied as gauge theories \cite{Hwang:1994yr}.
+
+Branching functions of the embedding $\af\subset\gf$ are the partition functions of CFT on the torus.
+
 \begin{figure}[h]

### 2011-05-31 src/affine.m

@@ -243,24 +243,24 @@ appendZeros[num_Integer,vec_finiteWeight]:=makeFiniteWeight[Join[vec[standardBas
 
 Expect["appendZeros",True,makeFiniteWeight[{1,1,0,0,0}]==appendZeros[3,makeFiniteWeight[{1,1}]]]
 
-Plus::"usage"=Plus::"usage" <> "\n Direct sum of finite-dimensional and affine Lie algebras can be specified as sum of root systems";
-finiteRootSystem/:x_finiteRootSystem+y_finiteRootSystem:=makeFiniteRootSystem[Join[Map[appendZeros[y[dimension],#]&,x[simpleRoots]],
+CirclePlus::"usage"=CirclePlus::"usage" <> "\n Direct sum of finite-dimensional and affine Lie algebras can be specified as sum of root systems";
+finiteRootSystem/:CirclePlus[x_finiteRootSystem,y_finiteRootSystem]:=makeFiniteRootSystem[Join[Map[appendZeros[y[dimension],#]&,x[simpleRoots]],
 										   Map[prependZeros[x[dimension],#]&,y[simpleRoots]]]];
 
 Module[{b2=makeSimpleRootSystem[B,2],a3=makeSimpleRootSystem[A,3]},
        Expect["Direct sum of finite-dimensional Lie algebras",True,
-	      b2+a3==makeFiniteRootSystem[{{1,-1,0,0,0,0},
+	      CirclePlus[b2,a3]==makeFiniteRootSystem[{{1,-1,0,0,0,0},
 					   {0,1,0,0,0,0},
 					   {0,0,1,-1,0,0},
 					   {0,0,0,1,-1,0},
 					   {0,0,0,0,1,-1}}]]]
 
 
-affineRootSystem/:x_affineRootSystem+y_affineRootSystem:=makeAffineExtension[x[finiteRootSystem]+y[finiteRootSystem]];
+affineRootSystem/:CirclePlus[x_affineRootSystem,y_affineRootSystem]:=makeAffineExtension[CirclePlus[x[finiteRootSystem],y[finiteRootSystem]]];
 
 Module[{b2=makeSimpleRootSystem[B,2],a3=makeSimpleRootSystem[A,3]},
        Expect["Direct sum of affine Lie algebras",True,
[…]

### 2011-05-31 tests/debug2.m

@@ -5,13 +5,118 @@ Copyright 1988-2010 Wolfram Research, Inc.
 
 <<affine.m;
 
+
+Hello!
+
+Throw::nocatch: 
+   Uncaught Throw[Formal element construction: GOT UNEXPECTED VALUE 0 INSTEAD
+      OF 2, assertion exception] returned to top level.
+
+Out[2]= Hold[Throw[Formal element construction: GOT UNEXPECTED VALUE 0\
+ 
+>      INSTEAD OF 2, assertion exception]]
+
+formalElement/:fe_formalElement[weight_?(hasKey[fe[[1]],#])&]:=fe[[1]][weight];
+
+fe=makeFormalElement[{makeFiniteWeight[{1,1}]},{3}]
+
+fe[makeFiniteWeight[{1,1}]]
+
+Out[5]= 0
+
+Out[4]= formalElement[table$127]
+
+Throw::nocatch: 
+   Uncaught Throw[Formal element construction: GOT UNEXPECTED VALUE 0 INSTEAD
+      OF 2, assertion exception] returned to top level.
+
+Out[2]= Hold[Throw[Formal element construction: GOT UNEXPECTED VALUE 0\
+ 
+>      INSTEAD OF 2, assertion exception]]
+
+
+fm=makeFormalElement[{makeFiniteWeight[{1,2}],makeFiniteWeight[{3,4}]},{2,3}]
+
+fm[makeFiniteWeight[{3,4}]]
+
+?DownValues
+
+f[x]=f[x]
+
+f[x]
+
+
+hasKey[hashtable_,key_]:=hashtable[key]=!=Unevaluated[hashtable[key]]
+
+
+h=makeHashtable[{a,b,c},{2,3,4}]
+
+h[q]
+
+hasKey[h,a]
+
+Out[20]= True
+
+Out[19]= False
+
+Out[18]= table$132[q]
+
+Out[17]= 3
+
+Out[16]= table$132
+
+Out[14]= f[x]
+
+Out[13]= f[x]
+
+Out[12]= f[x]
+
+Out[11]= f[x]
+
+DownValues[f] gives a list of transformation rules corresponding to all
+     downvalues defined for the symbol f. 
+
+Out[9]= 0
+
+Out[8]= 0
+
+fm[multiplicities]
+
+Out[7]= {2, 3}
+
[…]

### 2011-05-31 doc/paper.tex
Appendix added.

@@
 
-\newpage
 %% The Appendices part is started with the command \appendix;
 %% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+\appendix
+
+\section{Software package}
+\label{package}
+The package can be freely downloaded from {\it github}. Latest release can be found here. To get the development code use the command
+\begin{lstlisting}[language=bash]
+ git clone git://github.com/naa/Affine.git
+\end{lstlisting}
+
+Contents of the package:
+\begin{verbatim}
+  /home/anton/programing/Affine:
+  total used in directory 32 available 106878020
+  drwxr-xr-x  7 anton anton 4096 Apr 27 19:35 .
+  drwxr-xr-x 70 anton anton 4096 Apr 27 18:41 ..
+  drwxr-xr-x  2 anton anton 4096 May 25 23:49 demo
+  drwxr-xr-x  4 anton anton 4096 May 27 16:01 doc
+  drwxr-xr-x  8 anton anton 4096 May 27 16:03 .git
+  -rw-r--r--  1 anton anton    0 Apr 27 18:00 README~
+  -rw-r--r--  1 anton anton  838 Apr 27 19:35 README.markdown
+  drwxr-xr-x  2 anton anton 4096 May 27 15:56 src
+  drwxr-xr-x  2 anton anton 4096 May 27 16:03 tests
+
+  /home/anton/programing/Affine/demo:
+  total used in directory 84 available 106829532
+  drwxr-xr-x 2 anton anton  4096 May 25 23:49 .
+  drwxr-xr-x 7 anton anton  4096 Apr 27 19:35 ..
+  -rw-r--r-- 1 anton anton 21700 May 21 18:52 demo.nb
+  -rw-r--r-- 1 anton anton  8384 May 25 23:40 paper1.nb
+  -rw-r--r-- 1 anton anton 13110 May 30 10:53 paper.nb
+  -rw-r--r-- 1 anton anton  8385 May 25 23:39 Untitled-3.nb
+  -rw-r--r-- 1 anton anton  9298 May 25 23:49 Untitled-6.nb
+
+  /home/anton/programing/Affine/doc:
+  total used in directory 1100 available 106829532
+  drwxr-xr-x 4 anton anton   4096 May 31 14:13 .
+  drwxr-xr-x 7 anton anton   4096 Apr 27 19:35 ..
+  drwxr-xr-x 2 anton anton   4096 May 31 14:11 auto
+  -rw-r--r-- 1 anton anton  39978 May 31 14:02 bibliography.bib
+  -rw-r--r-- 1 anton anton  38052 May  5 16:21 bibliography.bib~
+  -rw-r--r-- 1 anton anton   1656 May 27 15:56 branching.pdf
+  -rw-r--r-- 1 anton anton      0 Apr 27 19:36 manual.tex
+  -rw-r--r-- 1 anton anton  11874 May 31 14:02 paper.aux
+  -rw-r--r-- 1 anton anton   7752 May 31 14:02 paper.bbl
+  -rw-r--r-- 1 anton anton   1788 May 31 14:02 paper.blg
+  -rw------- 1 anton anton  41053 May 16 14:03 paper corr from 2-3.tex
+  -rw-r--r-- 1 anton anton 116700 May 27 15:43 paper.dvi
+  -rw-r--r-- 1 anton anton  23735 May 31 14:02 paper.log
+  -rw-r--r-- 1 anton anton   1139 May 31 14:02 paper.out
+  -rw-r--r-- 1 anton anton 448209 May 31 14:02 paper.pdf
+  -rw-r--r-- 1 anton anton      0 May 31 14:02 paper.spl
+  lrwxrwxrwx 1 anton anton     38 May 31 14:11 .#paper.tex -> anton@netbook.blun.ch.28480:1306055748
+  -rw-r--r-- 1 anton anton  53281 May 31 14:13 #paper.tex#
+  -rw-r--r-- 1 anton anton  53109 May 31 14:11 paper.tex
+  -rw-r--r-- 1 anton anton      0 Apr 27 19:36 paper.tex~
+  -rw-r--r-- 1 anton anton  18490 May 22 21:56 prv_paper.log
+  -rw-r--r-- 1 anton anton 116960 May 22 21:56 _region_.log
+  drwxr-xr-x 3 anton anton   4096 May 27 15:29 _region_.prv
+  -rw-r--r-- 1 anton anton      0 May 22 21:56 _region_.spl
+  -rw-r--r-- 1 anton anton  48355 May 22 21:56 _region_.tex
+  -rw-r--r-- 1 anton anton   2509 May 27 15:43 timing.pdf
+  -rw-r--r-- 1 anton anton    488 May 31 14:07 TODO.org
+  -rw-r--r-- 1 anton anton    118 May 31 13:00 TODO.org~
+  -rw-r--r-- 1 anton anton  23893 May  5 16:21 utphys.bst
+
+  /home/anton/programing/Affine/src:
+  total used in directory 176 available 106829532
+  drwxr-xr-x 2 anton anton  4096 May 31 13:19 .
+  drwxr-xr-x 7 anton anton  4096 Apr 27 19:35 ..
+  -rw-r--r-- 1 anton anton 44264 May 31 13:19 affine.m
+  -rw-r--r-- 1 anton anton 38785 May 27 02:31 affine.m.~067bbb376d59bac3e36b73d793efea0ca5004918~
+  -rw-r--r-- 1 anton anton 40536 May 27 02:31 affine.m.~087b49ca835f88c54a5523cabe7c85ace8cbabf1~
+  -rw-r--r-- 1 anton anton 38876 May 27 02:30 affine.m.~19be799ef01b730efdad672442cdcb09d874a7ad~
+  -rw-r--r-- 1 anton anton  2509 May 27 15:41 timing.pdf
+
+  /home/anton/programing/Affine/tests:
+  total used in directory 948 available 106829532
+  drwxr-xr-x 2 anton anton   4096 May 31 14:09 .
+  drwxr-xr-x 7 anton anton   4096 Apr 27 19:35 ..
+  -rw-r--r-- 1 anton anton    722 May 14 16:26 A3reduce
+  -rw-r--r-- 1 anton anton   3295 May 20 01:13 anom.png
+  -rw-r--r-- 1 anton anton   1536 May 27 15:50 br1.pdf
+  -rw-r--r-- 1 anton anton   3132 May 27 13:15 br1.png
+  -rw-r--r-- 1 anton anton   1408 May 27 15:50 br2.pdf
+  -rw-r--r-- 1 anton anton   2654 May 27 13:15 br2.png
+  -rw-r--r-- 1 anton anton  35119 May 27 15:50 br3.pdf
+  -rw-r--r-- 1 anton anton   7170 May 27 13:16 br3.png
+  -rw-r--r-- 1 anton anton   5354 May 27 13:27 br4.png
+  -rw-r--r-- 1 anton anton   1656 May 27 15:56 branching.pdf
+  -rw-r--r-- 1 anton anton   8483 May 24 23:19 brc1.png
+  -rw-r--r-- 1 anton anton   5330 May 20 21:24 brc.png
+  -rw-r--r-- 1 anton anton 260600 Apr 27 18:23 debug1.m
+  -rw-r--r-- 1 anton anton  53187 May 31 13:18 #debug2.m#
+  -rw-r--r-- 1 anton anton  52658 May 31 13:08 debug2.m
+  -rw-r--r-- 1 anton anton   1481 May 16 21:44 debug2.m~
+  -rw-r--r-- 1 anton anton 228485 May 14 17:21 #debug.m#
+  -rw-r--r-- 1 anton anton 221743 May  6 01:50 debug.m
+  -rw-r--r-- 1 anton anton   8060 May 24 20:59 eanom.png
+  -rw-r--r-- 1 anton anton   4038 May 20 01:13 fan.png
+
+\end{verbatim}
 

### 2011-05-31 src/affine.m
Started transition of affine.m to package structure

@@ -1,115 +1,38 @@
-(* 
-
-   finiteWeight[dimension]=dimension_Integer
-   finiteWeight[standardBase]=List[x__Integer]
-   
-   affineWeight[finitePart]=x_finiteWeight
-   affineWeight[grade]=grade_Integer
-   affineWeight[level]=level_Integer
-   
-
-   Finite Weight: finiteWeight[dimension][<id>][dimension]
-                                              [standardBase]
-   Affine Weight: affineWeight[dimension][<id>][finitePart]
-   Affine Weight: affineWeight[dimension][<id>][level]
-   Affine Weight: affineWeight[dimension][<id>][grade]
-   
-   *)
-
-Clear[finiteWeight,affineWeight,dimension,standardBase,simpleRootBase,level,grade,Expect];
+BeginPackage["Affine`"]
 
 Expect::"usage"="Expect[comment,value,expression] is used for unit tests. If expression != value it throws exception.";
-Expect[ description_, val_, expr_ ] := 
-If[
-    val != expr,
-    Throw[
-        StringJoin[ ToString[description],": GOT UNEXPECTED VALUE ", ToString[expr], 
-        " INSTEAD OF ", ToString[val] ]
-        , "assertion exception"
-    ]
-]
 
 standardBase::"usage"=
     "standardBase[coordinates] represents weight vector in standard (Bourbaki) coordinates.\
-    E.g. simple roots for B2 are standardBase[1,-1] and standardBase[0,1]"
-
-(* finiteWeight[dimension,coordinates] *)
+    E.g. simple roots for B2 are standardBase[1,-1] and standardBase[0,1]";
 
 finiteWeight::"usage"=
     "finiteWeight[dimension_?NumberQ,coordinates_standardBase] represents\ 
     vector in weight space of finite-dimensional Lie algebra.\n 
     finiteWeight[dimension] returns dimension of the space, where weight vector is embedded\ 
     (i.e. for sl_n it is n+1).\n 
-     finiteWeight[standardBase] returns standard base coordinates of weight of finite-dimensional Lie algebra";
[…]

### 2011-05-31 tests/debug2.m

@@ -1,10 +1,123 @@
 AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
-Mathematica 8.0 for Linux x86 (64-bit)
-Copyright 1988-2010 Wolfram Research, Inc.
-
 <<affine.m;
 
+Hello!
+
+?dimension
+
+dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra
+   highest weight representation
+
+Message::name: Message name MessageName[finiteWeight[dimension], usage]
+     is not of the form symbol::name or symbol::name::language.
+Hello!
+
+finitePart[finiteWeight[2,{1,2}]]
+
+Out[7]= finiteWeight[2, {1, 2}]
+
+Out[6]= {1, 2}
+
+Out[5]= {1, 2}
+
+Out[4]= 2
+
+Out[3]= 2
+
+Out[5]= finiteWeight[2, {1, 2}][dimension]
+
+Out[4]= finiteWeight[2, {1, 2}]
+
+Out[3]= makeFiniteWeight[{1, 2}]
+
+Hello!
+
+Context[formalElement]
+
+?BeginPackage
+
+?Plus
+
+??formalElement
+
+Datastructure to represent formal elements of the ring of characters (linear
+   combinations of formal exponents of weights).
+
+    Internally the data is held in hashtable.
+
+    fe_formalElement[weight_?weightQ] returns multiplicity of a given weight
+   (coefficient in front of Exp[weight])
+
+    fe_formalElement[weights] returns list of weights
+
+    fe_formalElement[multiplicities] returns list of multiplicities
+    formalElements can be added, multiplied by number, Exp[wg_?weightQ] and by
+   formaElements
+
+    fe_formalElement[hashtable] returns formalElement's data as hashtable
+
+
+
+(fe_formalElement)[(weight_)?weightQ] := If[hasKey[fe[[1]], weight], 
+    fe[[1]][weight], 0]
+ 
+(fe_formalElement)[weights] := keys[fe[[1]]]
+ 
+(fe_formalElement)[multiplicities] := values[fe[[1]]]
+ 
+(fe_formalElement)[hashtable] := fe[[1]]
+ 
+(x_formalElement) == (y_formalElement) ^:= x[weights] == y[weights] && 
+    x[multiplicities] == y[multiplicities]
+ 
+(x_formalElement) + (y_formalElement) ^:= 
[…]

### 2011-05-31 tests/tests.m

@@ -1,0 +1,63 @@
+AppendTo[$Path,$InitialDirectory <> "/../src/"];
+
+<<affine.m;
+
+Expect["Dimension equals to length",3,makeFiniteWeight[{1,2,3}][dimension]]
+
+Expect["Scalar product for vectors from weight space of finite-dimensional Lie algebras",
+       10,makeFiniteWeight[{1,2,3}].makeFiniteWeight[{3,2,1}]]
+
+Expect["Plus for finite-dimensional weights",{2,4,6},(makeFiniteWeight[{1,2,3}]+makeFiniteWeight[{1,2,3}])[standardBase]]
+
+(*
+Expect["Plus  for vectors from different spaces are left unevaluated",True,
+       MatchQ[makeFiniteWeight[{1,2,3}]+makeFiniteWeight[{3,2,1,2}],x_finiteWeight + y_finiteWeight]]
+*)
+
+Expect["Equal for finite weights compares standard base representations", 
+       False,
+       makeFiniteWeight[{1,2,3}]==makeFiniteWeight[{1,3,2}]]
+
+Expect["Equal for finite weights compares standard base representations", 
+       True,
+       makeFiniteWeight[{1,2,3}]==makeFiniteWeight[{1,2,3}]]
+
+Expect["Equal for finite weights compares standard base representations", 
+       False,
+       makeFiniteWeight[{1,2,3}]==makeFiniteWeight[{1,2,3,4}]]
+
+Expect["Multiplication by scalar", True,makeFiniteWeight[{1,2,3}]*2==makeFiniteWeight[{2,4,6}]]
+
+Expect["Multiplication by scalar", True,2*makeFiniteWeight[{1,2,3}]==makeFiniteWeight[{2,4,6}]]
+
+Expect["Affine weight has the same real dimension as the finite-dimensional part, since we hold level and grade separetely",
+       True,makeAffineWeight[makeFiniteWeight[{1,2,3,4,5}],1,2][dimension]==Length[{1,2,3,4,5}]]
+
+Expect["Shortened constructor",
+       True,makeAffineWeight[{1,2,3,4,5},1,2][dimension]==Length[{1,2,3,4,5}]]
+
+
+Expect["Equal for affine weights compares finite parts, levels and grades", True,makeAffineWeight[makeFiniteWeight[{1,2,3}],1,2]==makeAffineWeight[makeFiniteWeight[{1,2,3}],1,2]]
+
[…]

### 2011-05-31 src/affine.m
More work on Package structure

@@ -59,6 +59,53 @@ makeHashtable::"usage"=
 keys::"usage"="keys[hashtable] gives all the keys in hashtable";
 values::"usage"="values[hashtable] gives all the values in hashtable (in the same order as keys)";
 
+finiteRootSystem::"usage"=
+    "finiteRootSystem[rank_Integer,{roots_finiteWeight}] represents root system of finite-dimensional Lie algebra.\n
+    finiteRootSystem[rank] returns rank of the root system\n
+    finiteRootSystem[dimension] returns the dimension of the space where the roors are realized as the vectors\n
+    finiteRootSystem[simpleRoots] returns unsorted list of simple roots in the root system.\n
+    finiteRootSystem[simpleRoot][n_Integer] returns n'th simple root"
+
+makeFiniteRootSystem::"usage"=
+    "makeFiniteRootSystem[{roots__finiteWeight}] creates finiteRootSystem structure from the List of simple roots\n
+    makeFiniteRootSystem[{roots__finiteWeight}] creates  finiteRootSystem structure from the List of simple roots\n
+    given as the lists of coordinates";
+
+rank::"usage"=
+    "rank[rs_?rootSystemQ] or rs[rank] returns rank of root system. Rank of affine root system is equal to rank of underlying \n
+    finite-dimensional root system";
+
+simpleRoot::"usage"=
+    "simpleRoot[rs_?rootSystemQ][i_Integer] or rs[simpleRoot][i_Integer] returns simple root with the index i. For affine root system i can be zero";
+
+simpleRoots::"usage"=
+    "simpleRoots[rs_?rootSystemQ] or rs[simpleRoots] returns unsorted list of simple roots";
+
+prependZeros::"usage"=
+    "prependZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by prepending num zeros to its coordinates";
+
+appendZeros::"usage"=
+    "appendZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by appending num zeros to its coordinates";
+
[…]

### 2011-05-31 tests/debug2.m

@@ -4,6 +4,22 @@ AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
 Hello!
 
+?Integer
+
+f[i_Integer]:=i+1
+
+f[0]
+
+FullForm[x_Integer|x_Rational]
+
+Out[7]//FullForm= 
+ 
+>   Alternatives[Pattern[x, Blank[Integer]], Pattern[x, Blank[Rational]]]
+
+Out[6]= 1
+
+Integer is the head used for integers. 
+
 ?dimension
 
 dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra

### 2011-05-31 tests/tests.m

@@ -60,4 +60,34 @@ Expect["Scalar product for vectors from weight space of affine Lie algebras",20,
 
 Expect["Multiplication by scalar", True,makeAffineWeight[makeFiniteWeight[{1,2,3}],1,2]*2==makeAffineWeight[makeFiniteWeight[{2,4,6}],2,4]]
 
+Module[{ht,tt},
+       ht=makeHashtable[{"a",2,tt},{1,2,3}];
+       Expect["Hashtable test",1,ht["a"]];
+       Expect["Hashtable test",3,ht[tt]];
+       Expect["Hashtable test",2,ht[2]]]
+
+Expect["prependZeros",True,makeFiniteWeight[{0,0,1,1}]==prependZeros[2,makeFiniteWeight[{1,1}]]]
+
+Expect["appendZeros",True,makeFiniteWeight[{1,1,0,0,0}]==appendZeros[3,makeFiniteWeight[{1,1}]]]
+
+Module[{b2=makeSimpleRootSystem[B,2],a3=makeSimpleRootSystem[A,3]},
+       Expect["Direct sum of finite-dimensional Lie algebras",True,
+	      CirclePlus[b2,a3]==makeFiniteRootSystem[{{1,-1,0,0,0,0},
+						       {0,1,0,0,0,0},
+						       {0,0,1,-1,0,0},
+						       {0,0,0,1,-1,0},
+						       {0,0,0,0,1,-1}}]]]
+
+Module[{b2=makeSimpleRootSystem[B,2],a3=makeSimpleRootSystem[A,3]},
+       Expect["Direct sum of affine Lie algebras",True,
+	      CirclePlus[makeAffineExtension[b2] , makeAffineExtension[a3]]==makeAffineExtension[makeFiniteRootSystem[{{1,-1,0,0,0,0},
+														       {0,1,0,0,0,0},
+														       {0,0,1,-1,0,0},
+														       {0,0,0,1,-1,0},
+														       {0,0,0,0,1,-1}}]]]]
+Expect["B2:",True,makeSimpleRootSystem[B,2][simpleRoots][[1]]==makeFiniteWeight[{1,-1}]]
+
+Expect["B2: rank",2,makeSimpleRootSystem[B,2][rank]]
+
+
 Print["Hi!"]

### 2011-06-01 src/affine.m
Tests and internal documentation are separated from the implementation

@@ -106,6 +106,163 @@ E::"usage"="represents root systems of series E";
 weightQ::"usage"=
     "Weight predicate"
 
+checkGrade::"usage"=
+    "computations for affine Lie algebras are limited by some grade, by default it is equal to 10. To change it set rs[gradeLimit].\n
+    checkGrade[rs_?rootSystemQ][w_?weightQ] checks if given weight has absolute value of grade less then gradeLimit. Returns true 
+    for finite-dimensional case";
+
+gradeLimit::"usage"=
+    "Limits computation for affine Lie algebras, i.e. b2a=OverHat[Subscript[B,2]]; b2a[gradeLimit]=15";
+
+reflection::"usage"=
+    "reflection[x_finiteWeight] represents reflection in the hyperplane, orthogonal to the given root x\n
+    reflection[x_affineWeight] represents affine reflection in the hyperplane, orthogonal to the given root x\n
+    reflection[x][y] reflects y in the hyperplane, orthogonal to x"
+
+coroot::"usage"="returns coroot of given root"
+
+cartanMatrix::"usage"=
+    "cartanMatrix[rs_?rootSystemQ] returns Cartan matrix of root system rs";
+
+rootSystemQ::"usage"=
+    "Predicate for root system data structures";
+
+weylGroupElement::"usage"=
+    "weylGroupElement[x__Integer][rs_?rootSystemQ] represents element of Weyl group composed of basic reflecetions x \n
+    of root system rs. Example: weylGroupElement[1,2,1][makeSimpleRootSystem[B,2]] = s1 s2 s1";
+
+fundamentalWeights::"usage"=
+    "fundamentalWeights[rs_?rootSystemQ] calculates fundamental weights of given root system rs";
+
+rho::"usage"=
+    "rho[rs_?rootSystemQ] - Weyl vector of root system rs (sum of fundamental weights)";
+
+toFundamentalChamber::"usage"=
+    "toFundamentalChamber[rs_?rootSystemQ][vec_?weightQ] acts on a weight vec by simple reflections of rs till it gets to main Weyl chamber";
+
+mainChamberQ::"usage"=
+    "mainChamberQ[rs_?rootSystemQ][wg_?weightQ] tells if weights wg lies inside the main Weyl chamber of root system rs or not";
+
+partialOrbit::"usage"=
[…]

### 2011-06-01 tests/tests.m

@@ -89,5 +89,204 @@ Expect["B2:",True,makeSimpleRootSystem[B,2][simpleRoots][[1]]==makeFiniteWeight[
 
 Expect["B2: rank",2,makeSimpleRootSystem[B,2][rank]]
 
+Expect["checkGrade finite dimensional Lie algebra", True, Affine`Private`checkGrade[makeSimpleRootSystem[B,2]][makeFiniteWeight[{2,1}]]]
+
+Expect["checkGrade affine Lie algebra", False, Affine`Private`checkGrade[makeAffineExtension[makeSimpleRootSystem[A,2]]][makeAffineWeight[{2,1,1},1,10]]]
+
+Module[{b2a=makeAffineExtension[makeSimpleRootSystem[B,2]]},
+       b2a[gradeLimit]=15;
+       Expect["checkGrade affine Lie algebra", True, Affine`Private`checkGrade[b2a][makeAffineWeight[{2,1},1,10]]];
+       b2a[gradeLimit]=.;]
+
+Expect["weight predicate on finite weights", True, weightQ[makeFiniteWeight[{1,2,3}]]]
+
+Expect["weight predicate on finite weights", False, weightQ[makeFiniteWeight[1,2,3]]]
+
+Expect["weight predicate on affine weights", True, weightQ[makeAffineWeight[{1,2,3},1,1]]]
+
+Expect["weight predicate on affine weights", False, weightQ[makeAffineWeight[1,2,3]]]
+
+Expect["Reflection for finite weights", True,reflection[makeFiniteWeight[{1,0}]][makeFiniteWeight[{1,1}]]==makeFiniteWeight[{-1,1}]]
+
+Expect["Co root of [1,0]", True, coroot[makeFiniteWeight[{1,0}]]==makeFiniteWeight[{2,0}]]
+
+Expect["Co root of affine [1,0]", True, coroot[makeAffineWeight[{1,0},1,0]]==makeAffineWeight[{2,0},2,0]]
+
+Expect["Cartan matrix of B2",{{2, -1}, {-2, 2}},cartanMatrix[makeSimpleRootSystem[B,2]]]
+
+Expect["Predicate for finite and affine root systems",True,rootSystemQ[makeSimpleRootSystem[B,2]]]
+
+Expect["Weyl reflection s1 s2 s1 in algebra B2",True,
[…]

### 2011-06-01 src/affine.m
Start of work on string and branching functions.

@@ -224,7 +224,8 @@ formalElement::"usage"=
     fe_formalElement[hashtable] returns formalElement's data as hashtable\n
     "
 
-
+hashtable::"usage"=
+    "hashtable[fe_formalElement] or fe[hashtable] returns weights and multiplicities of formal element as a hash table";
 
 makeFormalElement::"usage"=
     "makeFormalElement[{weights___?weightQ},{multiplicities___?NumberQ}] creates formal element with given weights and corresponding multiplicities\n
@@ -262,6 +263,15 @@ drawPlaneProjection::"usage"=
 draw3dProjection::"usage"=
     "draw3dProjection[axe1_,axe2_,axe3_,f_formalElement] draws projection to the 3d space of axe1, axe2, axe3 (e.g. 1,2,3 or 1,3,4 etc) of some formal element
     \n(branching, multiplicities, tensor product coefficients)"
+
+tensorProduct::"usage"=
+    "calculate tensor product decomposition coefficients"
+
+stringFunction::"usage"=
+    "stringFunciton[rs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of string function"
+
+branchingFunction::"usage"=
+    "branchingFunciton[rs_affineRootSystem,subs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of branching function"
 
 Begin["`Private`"]
 
@@ -591,6 +601,8 @@ subElement[fe_formalElement,{weights___?weightQ}]:=makeFormalElement[{weights},f
 
 formalElement/:fe_formalElement[hashtable]:=fe[[1]];
 
+hashtable[fe_formalElement]=fe[hashtable];
+
 formalElement/:x_formalElement + y_formalElement:=Module[{res},
 							 res=makeFormalElement[makeHashtable[{},{}]];
 							 Scan[(res[hashtable][#]:=x[#]+y[#])&,Union[x[weights],y[weights]]];
@@ -716,6 +728,16 @@ drawPlaneProjection[axe1_,axe2_,f_formalElement]:=
 
 draw3dProjection[axe1_,axe2_,axe3_,f_formalElement]:=
     Graphics3D[(Text[f[#],{#[standardBase][[axe1]],#[standardBase][[axe2]], #[standardBase][[axe3]]}]) & /@ f[weights]]
+
+
+tensorProduct::"usage"=
+    "calculate tensor product decomposition coefficients"
+
+stringFunction::"usage"=
[…]

### 2011-06-01 tests/tests.m

@@ -278,6 +278,7 @@ Expect["Our branching", True,
        Module[{b4=makeSimpleRootSystem[B,4],b2,wg},
 	      b2=regularSubalgebra[b4][3,4];
 	      wg=weight[b4][0,1,0,2];
+	      Print[wg];
 	      Union[ourBranching[b4,b2][wg][multiplicities]]=={0,6,10,19,30,40,60}]]
 
 Expect["branching2", True, 
@@ -286,6 +287,7 @@ Expect["branching2", True,
 	      wg=weight[b4][0,1,0,2];
 	      fe=branching2[b4,b2][wg];
 	      mcw=Select[fe[weights],mainChamberQ[b2]];
+	      Print[fe/@mcw];
 	      Union[fe/@mcw]=={0,6,10,19,30,40,60}]]
 
 

### 2011-06-01 src/affine.m
String functions

@@ -387,6 +387,8 @@ Subscript[B,n_Integer]:=makeSimpleRootSystem[B,n];
 Subscript[C,n_Integer]:=makeSimpleRootSystem[C,n];
 Subscript[D,n_Integer]:=makeSimpleRootSystem[D,n];
 
+affineRootSystem/:rs_affineRootSystem[gradeLimit]=10;
+
 checkGrade[rs_][w_finiteWeight]=True;
 checkGrade[rs_][w_affineWeight]:=(Abs[w[grade]]<rs[gradeLimit]) /. rs[gradeLimit]->10;
 checkGrade[gr_NumberQ][w_affineWeight]:=Abs[w[grade]]<=gr;
@@ -736,9 +738,14 @@ tensorProduct::"usage"=
 stringFunction::"usage"=
     "stringFunciton[rs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of string function"
 
+
+stringFunction[rs_affineRootSystem][hweight_affineWeight,wg_affineWeight]:=
+    Module[{fe=makeFormalElement[freudenthalMultiplicities[rs][hweight]]},
+	   Plus @@ Table[(q^i)*fe[makeAffineWeight[wg[finitePart],wg[level],-i]],{i,0,rs[gradeLimit]}]]
+(*
 branchingFunction::"usage"=
     "branchingFunciton[rs_affineRootSystem,subs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of branching function"
-
+*)
 End[]
 
 EndPackage[]

### 2011-06-01 tests/tests.m

@@ -278,7 +278,7 @@ Expect["Our branching", True,
        Module[{b4=makeSimpleRootSystem[B,4],b2,wg},
 	      b2=regularSubalgebra[b4][3,4];
 	      wg=weight[b4][0,1,0,2];
-	      Print[wg];
+(*	      Print[wg];*)
 	      Union[ourBranching[b4,b2][wg][multiplicities]]=={0,6,10,19,30,40,60}]]
 
 Expect["branching2", True, 
@@ -287,8 +287,30 @@ Expect["branching2", True,
 	      wg=weight[b4][0,1,0,2];
 	      fe=branching2[b4,b2][wg];
 	      mcw=Select[fe[weights],mainChamberQ[b2]];
-	      Print[fe/@mcw];
+(*	      Print[fe/@mcw];*)
 	      Union[fe/@mcw]=={0,6,10,19,30,40,60}]]
 
 
-Print["Hi!"]
+
+a1=makeAffineExtension[makeSimpleRootSystem[A,1]]
+
+a1[gradeLimit]=40
+
+stringFunction[a1][weight[a1][1,0],weight[a1][1,0]]
+
+
+a2=makeAffineExtension[makeSimpleRootSystem[A,2]]
+
+
+stringFunction[a2][weight[a2][1,0,0],weight[a2][1,0,0]]
+
+                                                   2                      3
+Out[6]= 1 + 2 Affine`Private`q + 5 Affine`Private`q  + 10 Affine`Private`q  + 
+ 
+                        4                      5                      6
+>    20 Affine`Private`q  + 36 Affine`Private`q  + 65 Affine`Private`q  + 
+ 
+                         7                       8                       9
+>    110 Affine`Private`q  + 185 Affine`Private`q  + 300 Affine`Private`q
+
+Print["All tests completed"]

### 2011-06-02 doc/manual.tex
String and branching functions, multiplicity functions return formalElements, start on work on manual, contents of software package in the paper, comma fix in bibliography.

\documentclass[preprint,12pt]{article}

\usepackage{graphicx}
\usepackage{hyperref}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{color}
\usepackage{listings}
\usepackage{textcomp}
\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
%	backgroundcolor=\color{lbcolor},
        language=Mathematica,
	tabsize=2,
	rulecolor=,
        basicstyle=\scriptsize,
        upquote=true,
%        aboveskip={1.5\baselineskip},
        columns=fixed,
        showstringspaces=false,
        extendedchars=true,
%        breaklines=true,
        prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
%        frame=single,
        showtabs=false,
        showspaces=false,
        showstringspaces=false,
        identifierstyle=\ttfamily,
        keywordstyle=\color[rgb]{0,0,1},
        commentstyle=\color[rgb]{0.133,0.545,0.133},
        stringstyle=\color[rgb]{0.627,0.126,0.941},
}

\newcommand{\go}{\stackrel{\circ }{\mathfrak{g}}}
\newcommand{\ao}{\stackrel{\circ }{\mathfrak{a}}}
\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\pia}{\pi_{\mathfrak{a}}}
\newcommand{\piab}{\pi_{\mathfrak{a}_{\bot}}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfg}{\hf_{\gf}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\begin{document}

\title{{\bf Affine.m} reference manual}
\author{Anton Nazarov}

\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:introduction-1}

\section{Download and installation}
\label{sec:downl-inst}

\subsection{Contents of software package}
\label{sec:cont-softw-pack}

\section{Software package}
\label{package}
The package can be freely downloaded from {\it github}. Latest release can be found here. To get the development code use the command
\begin{lstlisting}[language=bash]
 git clone git://github.com/naa/Affine.git
\end{lstlisting}

Contents of the package:
\begin{verbatim}
    Affine/                                root folder
      demo/                                  demonstrations
        demo.nb                                demo notebook
        paper.nb                               code from the paper
      doc/                                 documentation folder
        figures/                             figures in paper and manual
          timing.pdf                           diagram showing performance
          branching.pdf                        branching coefficients
        bibliography.bib                     bibliographic database
        manual.pdf                           manual
        manual.tex                           manual source
        paper.pdf                            paper
        paper.tex                            paper source
        TODO.org                             list of issues
      src/                                 source folder
        affine.m                             main software package
      tests/                               unit tests folder
        tests.m                              unit tests
      README.markdown                      short description of software
\end{verbatim}

\section{Usage}
\label{sec:usage}

\section{Function reference}
\label{sec:reference}
\begin{lstlisting}

Expect::"usage"="Expect[comment,value,expression] is used for unit tests. If expression != value it throws exception.";

standardBase::"usage"=
    "standardBase[coordinates] represents weight vector in standard (Bourbaki) coordinates.\
    E.g. simple roots for B2 are standardBase[1,-1] and standardBase[0,1]";

finiteWeight::"usage"=
    "finiteWeight[dimension_?NumberQ,coordinates_standardBase] represents\ 
    vector in weight space of finite-dimensional Lie algebra.\n 
    finiteWeight[dimension] returns dimension of the space, where weight vector is embedded\ 
    (i.e. for sl_n it is n+1).\n 
    finiteWeight[standardBase] returns standard base coordinates of weight of finite-dimensional Lie algebra";

dimension::"usage"=
    "dimension[wg_?weightQ] returns the dimension of the space, where finite part of weight lives";

finitePart::"usage"=
    "finitePart[wg_?weightQ] returns finite part of weight";

standardBase::"usage"=
    "standardBase[wg_?weightQ] returns coorinates of finite part of finite part of weight in standard (Bourbaki) basis";

makeFiniteWeight::"usage"=
    "makeFiniteWeight[{coordinates__?NumberQ}] creates finiteWeight with given coordinates in standard base";

Dot::"usage"=Dot::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";

Plus::"usage"=Plus::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";

Equal::"usage"=Equal::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";

Times::"usage"=Times::"usage"<>"\n\n Mutliplication by numbers is defined for the elements of weight space of affine and finite-dimensional Lie algebras.\ 
    \n For example makeFiniteWeight[{1,2,3}]*2==makeFiniteWeight[{2,4,6}]]";

affineWeight::"usage"=
    "affineWeight[dimension_?NumberQ,fw_finiteWeigt,level_?NumberQ, grade_?NumberQ] represents\ 
    vector in weight space of affine Lie algebra.\n 
    affineWeight[dimension] returns dimension of the space of real roots, where finite weight vector is embedded\ 
    (i.e. for sl_n it is n+1).\n 
    affineWeight[finitePart] returns finite part of weight as finiteWeight structure\n
    affineWeight[level] returns level of affine weight\n
    affineWeight[grade] returns grade of affine weight";

level::"usage"=
    "level[w_affineWeight] or w[level] returns level of weight of affine Lie algebra";

grade::"usage"=
    "grade[w_affineWeight] or w[grade] returns grade of weight of affine Lie algebra";

makeAffineWeight::"usage"= 
    "makeAffineWeight[fw_finiteWeight,level_?NumberQ,grade_?NumberQ] creates affine weight with the given finite part fw, level and grade\n
    makeAffineWeight[{fw__?NumberQ},level_?NumberQ,grade_?NumberQ] creates affine weight with the given finite part fw, level and grade
    ";

makeHashtable::"usage"=
    "makeHashtable[keys_List,values_List] creates hashtable from the list keys and list of values";
keys::"usage"="keys[hashtable] gives all the keys in hashtable";
values::"usage"="values[hashtable] gives all the values in hashtable (in the same order as keys)";

finiteRootSystem::"usage"=
    "finiteRootSystem[rank_Integer,{roots_finiteWeight}] represents root system of finite-dimensional Lie algebra.\n
    finiteRootSystem[rank] returns rank of the root system\n
    finiteRootSystem[dimension] returns the dimension of the space where the roors are realized as the vectors\n
    finiteRootSystem[simpleRoots] returns unsorted list of simple roots in the root system.\n
    finiteRootSystem[simpleRoot][n_Integer] returns n'th simple root"

makeFiniteRootSystem::"usage"=
    "makeFiniteRootSystem[{roots__finiteWeight}] creates finiteRootSystem structure from the List of simple roots\n
    makeFiniteRootSystem[{roots__finiteWeight}] creates  finiteRootSystem structure from the List of simple roots\n
    given as the lists of coordinates";

rank::"usage"=
    "rank[rs_?rootSystemQ] or rs[rank] returns rank of root system. Rank of affine root system is equal to rank of underlying \n
    finite-dimensional root system";

simpleRoot::"usage"=
    "simpleRoot[rs_?rootSystemQ][i_Integer] or rs[simpleRoot][i_Integer] returns simple root with the index i. For affine root system i can be zero";

simpleRoots::"usage"=
    "simpleRoots[rs_?rootSystemQ] or rs[simpleRoots] returns unsorted list of simple roots";

prependZeros::"usage"=
    "prependZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by prepending num zeros to its coordinates";

appendZeros::"usage"=
    "appendZeros[num_Integer,vec_finiteWeight] embeds vec to bigger space by appending num zeros to its coordinates";

CirclePlus::"usage"=CirclePlus::"usage" <> "\n Direct sum of finite-dimensional and affine Lie algebras can be specified as sum of root systems";

makeSimpleRootSystem::"usage"=
    "makeSimpleRootSystem[series, rank] creates root system of the algebra from given series with given rank.\n
    Exceptional Lie algebras are not supported yet";

Subscript::"usage"=Subscript::"usage" <>
    "\n Subscript[A|B|C|D|E,n_Integer] creates root system of the algebra from given series with given rank. \n
    It is an equivalent to makeSimpleRootsSystem, but looks better in notebook interface."

A::"usage"="represents root systems of series A";
B::"usage"="represents root systems of series B";
C::"usage"="represents root systems of series C";
D::"usage"="represents root systems of series D";
E::"usage"="represents root systems of series E";

weightQ::"usage"=
    "Weight predicate"

checkGrade::"usage"=
    "computations for affine Lie algebras are limited by some grade, by default it is equal to 10. To change it set rs[gradeLimit].\n
    checkGrade[rs_?rootSystemQ][w_?weightQ] checks if given weight has absolute value of grade less then gradeLimit. Returns true 
    for finite-dimensional case";

gradeLimit::"usage"=
    "Limits computation for affine Lie algebras, i.e. b2a=OverHat[Subscript[B,2]]; b2a[gradeLimit]=15";

reflection::"usage"=
    "reflection[x_finiteWeight] represents reflection in the hyperplane, orthogonal to the given root x\n
    reflection[x_affineWeight] represents affine reflection in the hyperplane, orthogonal to the given root x\n
    reflection[x][y] reflects y in the hyperplane, orthogonal to x"

coroot::"usage"="returns coroot of given root"

cartanMatrix::"usage"=
    "cartanMatrix[rs_?rootSystemQ] returns Cartan matrix of root system rs";

rootSystemQ::"usage"=
    "Predicate for root system data structures";

weylGroupElement::"usage"=
    "weylGroupElement[x__Integer][rs_?rootSystemQ] represents element of Weyl group composed of basic reflecetions x \n
    of root system rs. Example: weylGroupElement[1,2,1][makeSimpleRootSystem[B,2]] = s1 s2 s1";

fundamentalWeights::"usage"=
    "fundamentalWeights[rs_?rootSystemQ] calculates fundamental weights of given root system rs";

rho::"usage"=
    "rho[rs_?rootSystemQ] - Weyl vector of root system rs (sum of fundamental weights)";

toFundamentalChamber::"usage"=
    "toFundamentalChamber[rs_?rootSystemQ][vec_?weightQ] acts on a weight vec by simple reflections of rs till it gets to main Weyl chamber";

mainChamberQ::"usage"=
    "mainChamberQ[rs_?rootSystemQ][wg_?weightQ] tells if weights wg lies inside the main Weyl chamber of root system rs or not";

partialOrbit::"usage"=
    "partialOrbit[rs_finiteRootSystem][{weights__finiteWeight}] constructs Weyl partial orbit of given set of weights. \n
    It starts with the list of weights and reflects them away from main Weyl chamber.\n
    For w in fundamental chamber it gives the whole orbit.";

orbit::"usage"=
    "orbit[rs_?rootSystemQ][wg_?weightQ] returns the weight of Weyl orbit, containing given weight wg. \n
    Orbit is given as the list of lists starting with the weight in dominant Weyl chamber\n
    orbit[rs_?rootSystemQ][{wg_?weightQ}] works for a list of weights";

positiveRoots::"usage"=
    "positiveRoots[rs_?rootSystemQ] returns positive roots of root system rs";

dimension::"usage"=
    "dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra highest weight representation";

weightSystem::"usage"=
    "weightSystem[rs_?rootSystemQ][highestWeight_?weightQ] returns the set of dominant weights in the highest weight module. \n
    The list is split in pieces by number of root substractions";

freudenthalMultiplicities::"usage"=
    "freudenthalMultiplicities[rs_finiteRootSystem][highestWeight_finiteWeight] returns hashtable with the multiplicities of 
    weights in the highest weight module";

orbitWithEps::"usage"="returns orbit with the determinants of Weyl reflections";

racahMultiplicities::"usage"=
    "racahMultiplicities[rs_?rootSystemQ] returns hashtable with the multiplicities of 
    weights in the highest weight module. It uses recurrent relation similar to Racah formula";

highestRoot::"usage"="returns highest root of root system";

makeAffineExtension::"usage"=
    "makeAffineExtension[fs_finiteRootSystem] creates root system of affine Lie algebra which 
    is extension of given finite-dimensional root system";

OverHat::"usage"=
    "OverHat[rs_finiteRootSystem] creates affine extension of root system rs, it is equivalent makeAffineExtension[rs], but uses mathematical notation in notebook interface";

affineRootSystem::"usage"=
    "affineRootSystem[rank_Integer,finiteRootSystem_finiteRootSystem,imaginaryRoot_affineWeight,realRoots_List] 
    represents root system of affine Lie algebra.\n
    affineRootSystem[rank] returns rank of the root system\n
    affineRootSystem[imaginaryRoot] returns imaginary (zeroth) root\n
    affineRootSystem[realRoots] returns list of real roots (roots of finite-dimensional subalgebra)
    affineRootSystem[dimension] returns the dimension of the space where the roots are realized as the vectors\n
    affineRootSystem[simpleRoots] returns unsorted list of simple roots in the root system.\n
    affineRootSystem[simpleRoot][n_Integer] returns n'th simple root"

zeroWeight::"usage"="zeroWeight[rs_?rootSystemQ] returns zero root of root system rs (zero of rs[dimension]-dimemsional space)";

marks::"usage"="marks[rs_affineRootSystem] returns marks of affine Lie algebra";

marks::"usage"="comarks[rs_affineRootSystem] returns comarks of affine Lie algebra";

weight::"usage"=
    "weight[rs_?rootSystemQ][labels__Integer] constructs weight defined by Dynkin labels";

dynkinLabels::"usage"=
    "dynkinLabels[rs_?rootSystemQ][wg_?weightQ] returns Dynkin labels of weight (coefficients of its decomposition to the sum of fundamental weights) ";

orthogonalSubsystem::"usage"=
    "orthogonalSubsystem[rs_?rootSystemQ,subs_?rootSystemQ] returns subset of positive roots of root system rs, which 
    are orthogonal to simple roots of subsystem subs";

projection::"usage"=
    "projection[rs_?rootSystemQ][weights__?weightQ] projects given weight to the root (sub)system\n
    projection[rs_?rootSystemQ][fe_formalElement] projects the formal elements";

formalElement::"usage"=
    "Datastructure to represent formal elements of the ring of characters (linear combinations of formal exponents of weights).\n
    Internally the data is held in hashtable.\n
    fe_formalElement[weight_?weightQ] returns multiplicity of a given weight (coefficient in front of Exp[weight])\n
    fe_formalElement[weights] returns list of weights\n
    fe_formalElement[multiplicities] returns list of multiplicities
    formalElements can be added, multiplied by number, Exp[wg_?weightQ] and by formaElements\n
    fe_formalElement[hashtable] returns formalElement's data as hashtable\n
    "

hashtable::"usage"=
    "hashtable[fe_formalElement] or fe[hashtable] returns weights and multiplicities of formal element as a hash table";

makeFormalElement::"usage"=
    "makeFormalElement[{weights___?weightQ},{multiplicities___?NumberQ}] creates formal element with given weights and corresponding multiplicities\n
    makeFormalElement[{weights__?weightQ}] creates formal element where weight multiplicity is calculated as the number of appearances of weight in arguments list"

subElement::"usage"=
    "subElement[fe_formalElement,{weights___?weightQ}] creates formalElement with the given subset of weights";

regularSubalgebra::"usage"=
    "regularSubalgebra[rs_finiteRootSystem][rootIndices__?NumberQ] returns root system of regular subalgebra obtained by removing all unlisted nodes \n
    from Dynkn diagram of the algebra";

simpleBranching::"usage"=
    "Calculate branching coefficients with simple algorithm, which constructs all the modules of subalgebra with Freudenthal formula";

anomalousWeights::"usage"="
    anomalousWeights[rs_?rootSystemQ][hweight_?weightQ] returns the formal element, consisting of anomalous weights";

fan::"usage"=
    "Constructs fan of the embedding";

ourBranching::"usage"=
    "Calculate branching coefficients with alternative algorithm";

branching2::"usage"=
    "Calculate branching coefficients with alternative algorithm without folding to main Weyl chamber";

drawPlaneProjection::"usage"=
    "drawPlaneProjection[axe1_,axe2_,f_formalElement] draws projection to the plane of axe1, axe2 (e.g. 1,2 or 3,4, or 1,4 etc) of some formal element
    \n(branching, multiplicities, tensor product coefficients)";

draw3dProjection::"usage"=
    "draw3dProjection[axe1_,axe2_,axe3_,f_formalElement] draws projection to the 3d space of axe1, axe2, axe3 (e.g. 1,2,3 or 1,3,4 etc) of some formal element
    \n(branching, multiplicities, tensor product coefficients)"

tensorProduct::"usage"=
    "calculate tensor product decomposition coefficients"

stringFunction::"usage"=
    "stringFunciton[rs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of string function"

branchingFunction::"usage"=
    "branchingFunciton[rs_affineRootSystem,subs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of branching function"

\end{lstlisting}

  \end{document}

### 2011-06-02 doc/paper.tex
String and branching functions, multiplicity functions return formalElements, start on work on manual, contents of software package in the paper, comma fix in bibliography.

--- 2011-05-31 doc/paper.tex
@@
 
-More complex models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$. These models can be studied as gauge theories \cite{Hwang:1994yr}.
+More complex models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$. These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
 
@@
 
-\newpage
 %% The Appendices part is started with the command \appendix;
 %% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
+\appendix
+
+\section{Software package}
+\label{package}
+The package can be freely downloaded from {\it github}. Latest release can be found here. To get the development code use the command
+\begin{lstlisting}[language=bash]
+ git clone git://github.com/naa/Affine.git
+\end{lstlisting}
+
+Contents of the package:
+\begin{verbatim}
+    Affine/                                root folder
+      demo/                                  demonstrations
+        demo.nb                                demo notebook
+        paper.nb                               code from the paper
+      doc/                                 documentation folder
+        figures/                             figures in paper and manual
+          timing.pdf                           diagram showing performance
+          branching.pdf                        branching coefficients
+        bibliography.bib                     bibliographic database
+        manual.pdf                           manual
+        manual.tex                           manual source
+        paper.pdf                            paper
+        paper.tex                            paper source
+        TODO.org                             list of issues
+      src/                                 source folder
+        affine.m                             main software package
+      tests/                               unit tests folder
+        tests.m                              unit tests
+      README.markdown                      short description of software
+\end{verbatim}
 
@@
 
+\section*{References}
+\label{sec:references}
+
+\bibliography{bibliography}
 \bibliographystyle{elsarticle-num}
-\bibliography{bibliography}
+%\bibliographystyle{model1-num-names}
 

### 2011-06-02 src/affine.m

@@ -273,6 +273,9 @@ stringFunction::"usage"=
 branchingFunction::"usage"=
     "branchingFunciton[rs_affineRootSystem,subs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of branching function"
 
+
+q::"usage"="formal variable for string and branching funcitons";
+
 Begin["`Private`"]
 
 Expect[ description_, val_, expr_ ] := 
@@ -496,7 +499,7 @@ freudenthalMultiplicities[rs_?rootSystemQ][highestWeight_?weightQ]:=
 								   insideQ[#[[1]]+r]&]]]]
 			     ,posroots]],
 		weights];
-	   mults];
+	   makeFormalElement[mults]];
 
 (* freudenthalMultiplicities[makeSimpleRootSystem[B,2]][makeFiniteWeight[{5,5}]] *)
 orbitWithEps[rs_?rootSystemQ][weight_?weightQ]:=Flatten[MapIndexed[Function[{x,i},Map[{#,(-1)^(i[[1]]+1)}&,x]],orbit[rs][weight]],1];
@@ -513,7 +516,7 @@ racahMultiplicities[rs_?rootSystemQ][highestWeight_?weightQ]:=
 			 mults[v]=
 			 Plus@@(fan /. {x_?weightQ,e_Integer}:> If[insideQ[v+x],-e*mults[toFC[v+x]],0])],
 		weights];
-	   mults]
+	   makeFormalElement[mults]]
 
 
 (* racahMultiplicities[makeSimpleRootSystem[B,2]][makeFiniteWeight[{5,5}]] *)
@@ -631,12 +634,12 @@ regularSubalgebra[rs_finiteRootSystem][rootIndices__?NumberQ]:=makeFiniteRootSys
 
 simpleBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
     Module[{mults,pmults,rh=rho[subs],res,wgs},
-	   mults=makeFormalElement[freudenthalMultiplicities[rs][highestWeight]];
+	   mults=freudenthalMultiplicities[rs][highestWeight];
 	   Scan[(mults[hashtable][#]=mults[toFundamentalChamber[rs][#]])&,Flatten[orbit[rs][mults[weights]]]];
 	   pmults=projection[subs][mults];
 	   res=makeFormalElement[makeHashtable[{},{}]];
[…]

### 2011-06-02 tests/tests.m

@@ -166,15 +166,15 @@ Module[{b2=makeSimpleRootSystem[B,2]},
 Module[{b2=makeSimpleRootSystem[B,2],fm},
        fm=freudenthalMultiplicities[b2][makeFiniteWeight[{2,1}]];
        Expect["Mutliplicites of [2,1] B2 representation",{1, 1, 2, 3, 3},
-	      fm[#]&/@keys[fm]]]
+	      fm[multiplicities]]]
 
 (* Expect["orbitWithEps __TODO__",False,True] *)
 
 Module[{b2=makeSimpleRootSystem[B,2],fm,rm},
        fm=freudenthalMultiplicities[b2][makeFiniteWeight[{2,1}]];
        rm=freudenthalMultiplicities[b2][makeFiniteWeight[{2,1}]];
-       Expect["Racah and Freudenthal formulae should give the same result",rm[#]&/@keys[rm],
-	      fm[#]&/@keys[fm]]]
+       Expect["Racah and Freudenthal formulae should give the same result",rm[multiplicities],
+	      fm[multiplicities]]]
 
 Expect["Highest root for B2",makeFiniteWeight[{1, 1}],highestRoot[makeSimpleRootSystem[B,2]]]
 
@@ -290,7 +290,7 @@ Expect["branching2", True,
 (*	      Print[fe/@mcw];*)
 	      Union[fe/@mcw]=={0,6,10,19,30,40,60}]]
 
-
+(*
 
 a1=makeAffineExtension[makeSimpleRootSystem[A,1]]
 
@@ -312,5 +312,6 @@ Out[6]= 1 + 2 Affine`Private`q + 5 Affine`Private`q  + 10 Affine`Private`q  +
  
                          7                       8                       9
 >    110 Affine`Private`q  + 185 Affine`Private`q  + 300 Affine`Private`q
+ *)
 
 Print["All tests completed"]

### 2011-06-04 doc/paper.tex
Some text on the branching algorithm. Two new definitions in affine.m which should have proper description.

@@
 
-Branching algorithm \cite{2010arXiv1007.0318L}
+Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L} proceeds as follows:
+It contains the following steps:
+
+\begin{enumerate}
+\item  Construct the root system $\Delta _{\af}$ for the embedding $%
+\af\rightarrow \frak{g}$.
+
+\item  Select all positive roots $\alpha \in \Delta ^{+}$ orthogonal
+to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
+
+\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
+ (\ref{eq:6}) defines the sign function
+ $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
+ $\gamma_0$ is to be subtracted to get the fan (\ref{fan-defined}):
+ $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
+\af\subset \frak{g}}\right\} \setminus \left\{ 0\right\}$.
+
+\item  Construct the set $\widehat{\Psi ^{(\mu )}}=\left\{ w (\mu +\rho
+)-\rho ;\;w \in W\right\} $ of singular weights for the $\frak{g}$%
+-module $L^{(\mu )}$.
+
+\item  Select the weights $\left\{ \mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) =\pi _{\widetilde{\af_{\perp }}}\left[ w(\mu +\rho
+)-\rho \right] -\mathcal{D}_{\af_{\perp }}\in \overline{C_{\widetilde{%
+\af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
+we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
+}\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
+\af_{\perp }}}}$ (by computing its scalar product with the fundamental
+weights of $\afb^{+}$).
+
+\item  For the weights $\mu _{\widetilde{\af_{\perp }}}\left( w\right) $
+calculate dimensions of the corresponding modules, $\mathrm{\dim }\left(
+L_{\widetilde{\af_{\perp }}}^{\mu _{\widetilde{\af_{\perp }}%
+}\left( u\right) }\right) $, using the Weyl dimension formula and construct
+the singular element $\Psi ^{\left( \mu \right) }_{\left(  \af, \afb \right)}$.
+
+\item  Calculate the anomalous branching coefficients using the
+recurrent relation (\ref{recurrent-relation}) and select among them those
+corresponding to the weights in the main Weyl
+chamber $\overline{C_{\af}}$.
+\end{enumerate}
+
+We can speed up the algorithm by
+one-time computation of the representatives of the conjugate classes $%
+W/W_{\afb }$.
+
+Consider the regular embedding $B_{2}\subset B_{4}$.
+In this case fan consists of 24 elements.
+In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of subalgebra $B_{2}$.
+Full set of singular weights consists of 384 elements.
+Required subset contains at most 48 elements.
+So time of the construction of required subset is negligible if the number of branching coefficients is greater than that.
+We may estimate the total number of required operations for the computation of branching coefficients as the product of number of elements in main Weyl chamber of subalgebra with non-zero branching coefficients and number of elements in fan.
+In the case of direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than square of number of elements in main Weyl chamber of subalgebra with non-zero branching coefficients.
+To further illustrate this performance issue we include the Figure \ref{fig:branching} where we show the time required for computations.
+
 \subsection{Performance testing}

### 2011-06-04 src/affine.m

@@ -273,6 +273,8 @@ stringFunction::"usage"=
 branchingFunction::"usage"=
     "branchingFunciton[rs_affineRootSystem,subs_affineRootSystem][hweigth_affineWeight,wg_affineWeight] returns power series decomposition of branching function"
 
+weights::"usage"="";
+multiplicities::"usage"="";
 
 q::"usage"="formal variable for string and branching funcitons";
 

### 2011-06-08 doc/paper.tex
Minor changes in the beginning of the paper, functions and datastructure for highest weight modules are introduced (but not implemented) in the code

@@
 We present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras.
+It can be used to study irreducible, Verma and parabolic Verma modules.
 Algorithms are based upon the properties of weights and Weyl symmetry.
@@
 Representation theory of Lie algebras is of central importance for different areas of physics and mathematics.
-Lie algebras are used to for the description of symmetries of quantum and classical systems.
-Computational method in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
+In physics Lie algebras are used for the description of symmetries of quantum and classical systems.
+Computational methods in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
 
@@
 \begin{enumerate}
-\item Construction of root system which determine the properties of Lie algebra including its algebra commutation relations.
+\item Construction of root system which determine the properties of Lie algebra including its commutation relations.
 \item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.
@@
 
-Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and study of number integrable systems.
-But infinite-dimensional algebras are much harder to study and quantity of available computer programs is much smaller.
+Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and study of  integrable systems.
+But infinite-dimensional algebras are much harder to study and number of available computer programs is much smaller.
 

### 2011-06-08 src/affine.m

@@ -102,6 +102,8 @@ B::"usage"="represents root systems of series B";
 C::"usage"="represents root systems of series C";
 D::"usage"="represents root systems of series D";
 E::"usage"="represents root systems of series E";
+F::"usage"="represents root systems of series F";
+G::"usage"="represents root systems of series G";
 
 weightQ::"usage"=
     "Weight predicate"
@@ -153,25 +155,10 @@ orbit::"usage"=
     Orbit is given as the list of lists starting with the weight in dominant Weyl chamber\n
     orbit[rs_?rootSystemQ][{wg_?weightQ}] works for a list of weights";
 
-positiveRoots::"usage"=
-    "positiveRoots[rs_?rootSystemQ] returns positive roots of root system rs";
-
-dimension::"usage"=
-    "dimension[rs_?rootSystemQ][hweight_?weightQ] returns dimension of Lie algebra highest weight representation";
-
-weightSystem::"usage"=
-    "weightSystem[rs_?rootSystemQ][highestWeight_?weightQ] returns the set of dominant weights in the highest weight module. \n
-    The list is split in pieces by number of root substractions";
-
-freudenthalMultiplicities::"usage"=
-    "freudenthalMultiplicities[rs_finiteRootSystem][highestWeight_finiteWeight] returns hashtable with the multiplicities of 
-    weights in the highest weight module";
-
 orbitWithEps::"usage"="returns orbit with the determinants of Weyl reflections";
 
-racahMultiplicities::"usage"=
-    "racahMultiplicities[rs_?rootSystemQ] returns hashtable with the multiplicities of 
-    weights in the highest weight module. It uses recurrent relation similar to Racah formula";
+positiveRoots::"usage"=
+    "positiveRoots[rs_?rootSystemQ] returns positive roots of root system rs";
 
 highestRoot::"usage"="returns highest root of root system";
 
@@ -213,7 +200,6 @@ projection::"usage"=
     projection[rs_?rootSystemQ][fe_formalElement] projects the formal elements";
 
 
-
 formalElement::"usage"=
     "Datastructure to represent formal elements of the ring of characters (linear combinations of formal exponents of weights).\n
[…]

### 2011-06-08 tests/debug2.m

@@ -2,6 +2,112 @@ AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
 <<affine.m;
 
+Table[{i*j},{i,10},{j,10}]
+
+makeSimpleRootSystem[E,rank_Integer]/; (rank>=3) && (rank<=8):=True
+
+makeSimpleRootSystem[E,8]
+
+1/2*{1,-1,-1,-1}
+
+f[x_,y_:x]:=x+y
+
+fn[i_]:=NestWhileList[Function[x,x+1],1,#<i&]//Timing
+
+Table[{i,fn[i][[1]]},{i,1000,1010}]
+
+Out[21]= {{1000, 0.020001}, {1001, 0.008001}, {1002, 0.012001}, 
+ 
+>    {1003, 0.012}, {1004, 0.012001}, {1005, 0.012001}, {1006, 0.012001}, 
+ 
+>    {1007, 0.008}, {1008, 0.012001}, {1009, 0.024001}, {1010, 0.016001}}
+
+Export["listtiming2.png",ListPlot[Out[21]]]
+
+Out[22]= listtiming2.png
+
+Out[20]= {{1, 0.}, {2, 0.}, {3, 0.}, {4, 0.}, {5, 0.}, {6, 0.}, {7, 0.}, 
+ 
+>    {8, 0.}, {9, 0.}, {10, 0.}}
+
+Export["listtiming.png",ListPlot[Table[{i*200,fn[i*200][[1]]},{i,200}]]]
+
+Out[26]= listtiming.png
+
+Out[25]= $Aborted
+
+Out[24]= $Aborted
+
+Out[23]= listtiming.png
+
+Out[19]= listtiming.png
+
+Out[18]= listtiming.png
+
+?ListPlot
+
+ListPlot[{y , y , ...}] plots points corresponding to a list of values,
+           1   2
+     assumed to correspond to x coordinates 1, 2, .... 
+
+     ListPlot[{{x , y }, {x , y }, ...}]
+                 1   1     2   2
+      plots a list of points with specified x
+       and y coordinates. ListPlot[{list , list , ...}]
+                                        1      2
+         plots several lists of points. 
+
[…]

### 2011-06-11 src/affine.m
Characters of Verma, parabolic Verma and irreducible modules can be constructed

@@ -66,6 +66,9 @@ finiteRootSystem::"usage"=
     finiteRootSystem[simpleRoots] returns unsorted list of simple roots in the root system.\n
     finiteRootSystem[simpleRoot][n_Integer] returns n'th simple root"
 
+emptyRootSystem::"usage"=
+    "represents trivial (empty) root system";
+
 makeFiniteRootSystem::"usage"=
     "makeFiniteRootSystem[{roots__finiteWeight}] creates finiteRootSystem structure from the List of simple roots\n
     makeFiniteRootSystem[{roots__finiteWeight}] creates  finiteRootSystem structure from the List of simple roots\n
@@ -157,6 +160,8 @@ orbit::"usage"=
 
 orbitWithEps::"usage"="returns orbit with the determinants of Weyl reflections";
 
+formalOrbit::"usage"="returns the same thing as orbitWithEps, but as formalElement";
+
 positiveRoots::"usage"=
     "positiveRoots[rs_?rootSystemQ] returns positive roots of root system rs";
 
@@ -225,13 +230,13 @@ parabolicSubalgebra::"usage"=
     "parabolicSubalgebra[rs_finiteRootSystem][rootIndices__?NumberQ] returns root system of regular subalgebra obtained by removing all unlisted nodes \n
     from Dynkn diagram of the algebra";
 
+module::"usage"=
+    "module[rs_?rootSystemQ,anomWeights_formalElement,subs_?rootSystemQ,limit_?NumberQ] represents Lie algebra module \n
+    generated by the set of anomalous weights with the additional symmetry of root system subs, \n
+    limit limits number of subtraction in the construction of infinite-dimensional modules"
 
-highestWeightModule::"usage"=
-    "highestWeightModule[rs_?rootSystemQ][hweight_?weightQ,{symgen___Integer},limit_Integer] represents highest weight module \n
-    of algebra fixed by the root system rs with the highest weight hweight and Weyl symmetry generated \n
-    by Weyl reflections {symgen} (i.e. empty list for Verma module, some subset of {1,...,r} for parabolic Verma module\n
[…]

### 2011-06-11 doc/paper.tex
Sum of modules

@@
 The structure of affine Lie algebras allows to extend computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
-The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of algebras and representations was published in 1990.
+The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
 But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
@@
 \ref{sec:theor-backgr}).
-Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and their representations (Sec.
-\ref{sec:core-datastructures} and used in implemented algorithms (Sec.
+Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec.
+\ref{sec:core-datastructures}) and discuss implemented algorithms (Sec.
 \ref{sec:comp-algor}).
@@
 
+In this section we remind necessary definitions and present formulae used in computations.
+
 \subsection{Lie algebras of finite and affine types}
@@
 
-Lie algebra $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called commutator.
-If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the structure constants $C_{ijk}$:
+{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it commutator}.
+If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
 \begin{equation}
@@
 Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
-Weights are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
+{\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
 
@@
 
-Loop algebra $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$ has commutation relations
+{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
 \begin{equation}
@@
 
-\subsection{Weights and roots}
+\subsection{Modules, weights and roots}
 \label{sec:weights-roots}
@@
 \end{equation}
-Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$.
+Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms on vector space $V$ with the commutator as the bracket.
 
@@
 \end{equation}
-It can be encoded by the formal character of module
+Module structure can be encoded by the formal character of module
 \begin{equation}
@@
 
-Roots are weights of adjoint representation of $\gf$ on itself.
+Lie algebra is its own module. The action of generators is called adjoint and it is given by the bracket $ad_{X} Y=[X,Y]$. 
+{\it Roots} are weights of adjoint representation of $\gf$.
 They encode the commutation relations of algebra in the following way.
@@
 \end{align}
-Highest weight of adjoint representation.
 
@@
 
-A positive root is simple if it cannot be written as the sum of positive roots.
-The set of simple roots $\left\{\alpha_{i}\right\}$ is a basis of $\hfg$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive.
+A positive root is {\it simple} if it cannot be written as the sum of positive roots.
+The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis of $\hfg$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive.
 In case of finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to rank of the algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
@@
 Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
+It is also highest weight (See section \ref{sec:high-weight-modul}) of adjoint module.
 {\it Comarcs} are equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
 
-Although the full set of roots $\Delta$ is infinite for affine Lie algebra $\hat\gf$ the number of simple roots is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+Although the full set of roots $\Delta$ is infinite for affine Lie algebra $\hat\gf$ the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
 The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.

### 2011-06-11 src/affine.m

@@ -772,10 +772,6 @@ character[m_module]:=
     Module[{rs=rootSystem[m],subs=subSystem[m],toFC,rh,mults,aw,wgs,fan,tmp},
 	   rh=rho[rs];
 	   fan=Exp[2*rh]*anomalousWeights[rs][zeroWeight[rs]];
-(*	   Print[tmp[weights]];
-	   fan=makeFormalElement[Rest[tmp[weights]],Rest[tmp[multiplicities]]];
-	   Print[fan[weights]];
-	   Print[fan[multiplicities]];*)
 	   If [subs=!=emptyRootSystem[],
 	       toFC=toFundamentalChamber[subs],
 	       toFC=#&;
@@ -787,41 +783,23 @@ character[m_module]:=
 	   Scan[Function[v,
 			 mults[v]=
 			 Plus @@ Map[ If [insideQ[v+#], -fan[#]*mults[toFC[v+#]], 0]&, fan[weights]];
-(*			 Print[{v,mults[v],{v+#,-fan[#]*mults[toFC[v+#]]}&/@fan[weights]}];*)
 			 If [IntegerQ[aw[v]], mults[v]=mults[v]+aw[v]]],
-(*			 Print[aw[v]];
-			 Print[mults[v]]],*)
 		wgs];
 	   makeFormalElement[mults]];
-(*
-,rh,weights,mults,c,insideQ,
-	    fan,
-	    toFC=toFundamentalChamber[rs]},
-	   fan
-	   fan=Map[{rh-#[[1]],#[[2]]}&,Rest[orbitWithEps[rs][rh]]];
-	   weights=Sort[ Rest[Flatten[weightSystem[rs][highestWeight]]], #1.rh>#2.rh&];
-	   mults[highestWeight]=1;
-	   insideQ:=IntegerQ[mults[toFC[#]]]&;
-	   Scan[Function[v,
-			 mults[v]=
-			 Plus@@(fan /. {x_?weightQ,e_Integer}:> If[insideQ[v+x],-e*mults[toFC[v+x]],0])],
-		weights];
-	   makeFormalElement[mults]]
-*)
-freudenthalMultiplicities::"usage"=
-    "freudenthalMultiplicities[rs_finiteRootSystem][highestWeight_finiteWeight] returns hashtable with the multiplicities of 
-    weights in the highest weight module";
-
-racahMultiplicities::"usage"=
-    "racahMultiplicities[rs_?rootSystemQ] returns hashtable with the multiplicities of 
[…]

### 2011-06-16 doc/paper.tex
Minor changes

@@
 \end{equation}
-The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \frak{%
-g}}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
+The weights in $\left\{ \xi \right\} _{\widetilde{\af}\rightarrow \gf}$ are to be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi
 \right\} $ -- and the zero element is to be eliminated:
@@
 
+\subsection{Modules}
+\label{sec:modules}
+
+{\bf Affine.m} can be used to study different kinds of modules, e.g.
+Verma modules, irreducible modules.
+We need datastructure to represent generic module of Lie algebra $\gf$.
+This datastructure is \lstinline{module}.
+Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
+Set of singular weights can have Weyl symmetry.
+It can be symmetry with respect to Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
+Then it is possible to study only main Weyl chamber $C_{\af}$.
+So generic constructor for \lstinline{module} datastructure is \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],opts___?OptionQ]}.
+Here \lstinline{rs} is root system of Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is root system corresponding to Weyl group $W_{\af}$ which is the symmetry of the set of singular weights.
+There are several constructors for different highest weight modules:
+\begin{lstlisting}[mathescape=true]
+vm=makeVermaModule[$B_{2}$][weight[$B_{2}$][2,1]];
+pm=makeParabolicVermaModule[$B_{2}$][weight[$B_{2}$][2,1],{1}];
+im=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
+drawPlaneProjection[2,1,{character[vm],character[pm],character[im]} ]
+\end{lstlisting}
 \section{Computational algorithms}
@@
  $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
- $\gamma_0$ is to be subtracted to get the fan (\ref{fan-defined}):
+ $\gamma_0$ is to be subtracted to get the fan:
  $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
@@
 \item  Calculate the anomalous branching coefficients using the
-recurrent relation (\ref{recurrent-relation}) and select among them those
+recurrent relation (\ref{recurrent-rel}) and select among them those
 corresponding to the weights in the main Weyl
@@
 \begin{figure}[h]
-  \label{freudenthal-racah-times}
+%  \label{freudenthal-racah-times}
   \noindent\centering{
@@
 
-For fundamental representations of simple Lie algebras it is sometimes possible to get analytic result for the dependence of decomposition coefficients on $N$ (See \cite{2011LyakhovskyPostnova}).
+For fundamental representations of simple Lie algebras it is sometimes possible to get analytic result for the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
 Our code give numerical values and can be used to check this analytic results.

### 2011-06-16 src/affine.m

@@ -231,12 +231,12 @@ parabolicSubalgebra::"usage"=
     from Dynkn diagram of the algebra";
 
 module::"usage"=
-    "module[rs_?rootSystemQ,anomWeights_formalElement,subs_?rootSystemQ,limit_?NumberQ] represents Lie algebra module \n
-    generated by the set of anomalous weights with the additional symmetry of root system subs, \n
+    "module[rs_?rootSystemQ,singWeights_formalElement,subs_?rootSystemQ,limit_?NumberQ] represents Lie algebra module \n
+    generated by the set of singular weights with the additional symmetry of root system subs, \n
     limit limits number of subtraction in the construction of infinite-dimensional modules"
 
 makeModule::"usage"=
-    "makeModule[rs_?rootSystemQ][anomWeights_formalElement,subs_?rootSystemQ|emptyRootSystem,opts___?OptionQ] is general construction for modules";
+    "makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem,opts___?OptionQ] is general construction for modules";
 
 makeVermaModule::"usage"="makeVermaModule[rs_?rootSystemQ][hw_?weightQ,opts___?OptionQ] constructs Verma module. \n
     Option 'limit' limits construction with the number of simple root subtractions. By default it is chosen in such a way\n
@@ -269,8 +269,8 @@ racahMultiplicities::"usage"=
     weights in the highest weight module. It uses recurrent relation similar to Racah formula";
 
 
-anomalousWeights::"usage"="
-    anomalousWeights[m_module] returns the formal element, consisting of anomalous weights of module hm";
+singularWeights::"usage"="
+    singularWeights[m_module] returns the formal element, consisting of singular weights of module hm";
 
 character::"usage"=
[…]

### 2011-06-16 tests/debug2.m

@@ -3,7 +3,13 @@ AppendTo[$Path,$InitialDirectory <> "/../src/"];
 Mathematica 8.0 for Linux x86 (64-bit)
 Copyright 1988-2010 Wolfram Research, Inc.
 
+Mathematica 8.0 for Linux x86 (64-bit)
+Copyright 1988-2010 Wolfram Research, Inc.
+
 <<affine.m;
+
+SetDelayed::write: 
+   Tag Times in  ourBranching[m_module, (subs_)?rootSystemQ] is Protected.
 
 b2=makeSimpleRootSystem[B,2];
 vm=makeVermaModule[b2][weight[b2][1,1]];
@@ -11,12 +17,186 @@ pm=makeParabolicVermaModule[b2][weight[b2][1,0],{1}];
 im=makeIrreducibleModule[b2][weight[b2][4,6]];
 
 
+fc=Affine`Private`fullCharacter[im]
+
+Affine`Private`subSystem[im]
+
+ch=character[im2]
+
+Out[22]= formalElement[Affine`Private`table$907]
+
+im2=makeIrreducibleModule[b2][weight[b2][3,1]];
+
+fc=Affine`Private`fullCharacter[im2]
+
+Out[50]= formalElement[Affine`Private`table$1644]
+
+Out[43]= formalElement[Affine`Private`table$1405]
+
+Out[36]= formalElement[Affine`Private`table$1047]
+
+Out[35]= formalElement[Affine`Private`table$1035]
+
+Out[34]= fullCharacter[module[finiteRootSystem[2, 2, 
+ 
+>      {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}], 
+ 
+>     formalElement[Affine`Private`table$1023], 
+ 
+>     finiteRootSystem[2, 2, {finiteWeight[2, {1, -1}], 
+ 
+>       finiteWeight[2, {0, 1}]}], -5]]
+
+ch3=orbit[b2][ch]
+
+Out[26]= formalElement[Affine`Private`table$975]
+
+Export["irrep6.png",drawPlaneProjection[2,1,fc]];
+
+b2=makeSimpleRootSystem[B,2];
+vm=makeVermaModule[b2][weight[b2][2,1]];
+pm=makeParabolicVermaModule[b2][weight[b2][2,1],{1}];
+im=makeIrreducibleModule[b2][weight[b2][2,1]];
+
[…]

### 2011-07-12 src/affine.m
String and branching functions

@@ -190,7 +190,7 @@ zeroWeight::"usage"="zeroWeight[rs_?rootSystemQ] returns zero root of root syste
 
 marks::"usage"="marks[rs_affineRootSystem] returns marks of affine Lie algebra";
 
-marks::"usage"="comarks[rs_affineRootSystem] returns comarks of affine Lie algebra";
+comarks::"usage"="comarks[rs_affineRootSystem] returns comarks of affine Lie algebra";
 
 weight::"usage"=
     "weight[rs_?rootSystemQ][labels__Integer] constructs weight defined by Dynkin labels";
@@ -271,8 +271,8 @@ racahMultiplicities::"usage"=
     weights in the highest weight module. It uses recurrent relation similar to Racah formula";
 
 
-singularWeights::"usage"="
-    singularWeights[m_module] returns the formal element, consisting of singular weights of module hm";
+singularElement::"usage"="
+    singularElement[m_module] returns the formal element, consisting of singular weights of module hm";
 
 character::"usage"=
     "character[m_module] returns character of module as formalElement datastructure";
@@ -328,6 +328,13 @@ weights::"usage"="weights[fe_formalElement] or fe[weights] returns list of weigh
 multiplicities::"usage"="multiplicities[fe_formalElement] or fe[multiplicities] returns list of weight multiplicities in formalElement. List is in the same order as fe[weights] ";
 
 q::"usage"="formal variable for string and branching funcitons";
+
+
+embeddingIndex::"usage"="Calculate index of the embedding";
+
+stringFunctions::"usage"="stringFunctions[rs_affineRootSystem,{ls__?NumberQ}] returns string functions of highest weight irreducible module"
+
[…]

### 2011-07-13 src/affine.m
Weight system fixed, but slow

@@ -74,6 +74,10 @@ makeFiniteRootSystem::"usage"=
     makeFiniteRootSystem[{roots__finiteWeight}] creates  finiteRootSystem structure from the List of simple roots\n
     given as the lists of coordinates";
 
+makeAffineRootSystem::"usage"=
+    "makeAffineRootSystem[roots__List] creates affine root system which extends finite root system specified by simple roots 'roots'";
+
+
 rank::"usage"=
     "rank[rs_?rootSystemQ] or rs[rank] returns rank of root system. Rank of affine root system is equal to rank of underlying \n
     finite-dimensional root system";
@@ -336,6 +340,9 @@ stringFunctions::"usage"="stringFunctions[rs_affineRootSystem,{ls__?NumberQ}] re
 
 branchingFunctions::"usage"="branchingFunctions[rs_affineRootSystem,subs_affineRootSystem,{ls__?NumberQ}] returns string functions of highest weight irreducible module"
 
+textPlot::"usage"=
+    "textPlot[m_module] plots module multiplicities";
+
 Begin["`Private`"]
 
 Expect[ description_, val_, expr_ ] := 
@@ -481,6 +488,8 @@ Subscript[F,n_Integer]=makeSimpleRootSystem[F,n];
 Subscript[G,n_Integer]=makeSimpleRootSystem[G,n];
 
 affineRootSystem/:rs_affineRootSystem[gradeLimit]=10;
+
+finiteRootSystem/:rs_finiteRootSystem[gradeLimit]=10;
 
 checkGrade[rs_][w_finiteWeight]=True;
 checkGrade[rs_][w_affineWeight]:=(Abs[w[grade]]<=rs[gradeLimit]) /. rs[gradeLimit]->10;
@@ -785,8 +794,8 @@ module::"usage"=
     "module[rs_?rootSystemQ,singWeights_formalElement,subs_?rootSystemQ,limit_?NumberQ] represents Lie algebra module \n
     generated by the set of singular weights with the additional symmetry of root system subs"
 *)
-makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|subs_emptyRootSystem,opts___?OptionQ]:=
[…]

### 2011-07-13 doc/paper.tex
Notes from paper added

@@
 %% Text of abstract
-We present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras.
-It can be used to study irreducible, Verma and parabolic Verma modules.
+In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
 Algorithms are based upon the properties of weights and Weyl symmetry.
-Weight multiplicity computation, branching of representation to representations of subalgebra and tensor product decomposition are the most important problems that we treat.
-These problems has numerous applications in physics.
-
+The most important for us problems are computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
+These problems have numerous applications in physics and we provide some examples of these applications.
 The program is implemented in popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
@@
 \end{equation}
-Lie algebra is simple if it contains no non-trivial ideals. Semisimple Lie algebra is a direct sum of simple Lie algebras.
-
-Maximal commutative subalgebra (Cartan subalgebra) of $\gf$ is denoted by $\hfg$.
+Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
+{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
+In present paper we treat simple and semisimple Lie algebras.
+
+Maximal commutative subalgebra ({\it Cartan subalgebra}) of $\gf$ is denoted by $\hfg$.
 We denote the elements of basis of $\hfg$ by $H^{i}$.
@@
 The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- highest root of the algebra $\go$.
+Note that root multiplicity $\mathrm{mult}(\alpha)$ for affine Lie algebra can be greater than one.
 
@@
 \end{equation}
-Note that root multiplicity $\mathrm{mult}(\alpha)$ for affine Lie algebra can be greater than one.
-
 Root system and characters of representation are invariant with respect to the action of Weyl group. Root system can be reconstructed from the set of simple roots with the action of Weyl group.
@@
 Using the definition \eqref{eq:8} it is easy to see that $s_{0}s_{i}s_{0}\cdot \lambda=\lambda+\alpha_{i}$, so Weyl group can be presented as semidirect product of Weyl group $W_{\gf}$ of $\gf$ and translations by the roots of $\hat \gf$.
+Weyl group element can be presented as the product of elementary reflections in multiple ways.
+Number of elementary reflections in shortest sequence representing element $w\in W_{\gf}$ is called {\it length} of $w$ and denoted $l(w)$.
+We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for parity of number of Weyl reflections generating $w$.
 
@@
   \label{eq:20}
-  \langle\omega_i,\alpha_j\rangle=\frac{(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
+  \langle\omega_i,\alpha_j\rangle=\frac{2(\omega_{i},\alpha_{j})}{(\alpha_{j},\alpha_{j})}=\delta_{ij}
 \end{equation}
@@
 We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates weight system of $V$, i.e.
-if $V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
+if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
 
@@
 
-The simplest type of highest weight modules is the Verma module
+The most simple type of highest weight modules is the Verma module
 $M^{\mu}$ who's space can be defined as the space
@@
 Here $\bff_{+}$ is Borel sub-algebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
-Elements of $\gf$ act from the left and we should all the elements of $\bff_{+}$ to the right, so that they can act on the space $D_{\lambda}(\bff_{+})$.
+Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D_{\lambda}(\bff_{+})$.
 
@@
   \label{eq:12}
-  \prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
+  R:=\prod_{\alpha\in \Delta^{+}} \left( 1-e^{-\alpha}\right)^{\mathrm{mult}(\alpha)}=\sum_{w\in W} \epsilon(w) e^{w\rho-\rho},
 \end{equation}
@@
 the parity of number of Weyl reflections generating $w$.
+
+Verma module $M^{\mu}$ has the unique maximal submodule and the
+unique nontrivial simple quotient $L^{\mu}$ which is an
+irreducible highest weight module. Weyl character formula for
+irreducible highest weight modules is
+\begin{equation}
+  \label{eq:13}
+  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
+\end{equation}
+Thus the character of an irreducible highest weight module can be
+seen as the combination of characters of Verma modules. ( This
+fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
+(\cite{bernstein1976category,bernstein1971structure}, see also
+\cite{humphreys2008representations}).)
 
@@
 
-Verma module $M^{\mu}$ has the unique maximal submodule and the
-unique nontrivial simple quotient $L^{\mu}$ which is an
-irreducible highest weight module. Weyl character formula for
-irreducible highest weight modules is
-\begin{equation}
-  \label{eq:13}
-  \mathrm{ch} L^{\mu}=\frac{\sum_{w\in W} \epsilon(w) e^{w(\mu+\rho)-\rho}}{\sum_{w\in W}\epsilon(w) e^{w\rho-\rho}}=\sum_{w\in W} \epsilon(w)\; \mathrm{ch} M^{w(\mu+\rho)-\rho}
-\end{equation}
-Thus the character of an irreducible highest weight module can be
-seen as the combination of characters of Verma modules. ( This
-fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
-(\cite{bernstein1976category,bernstein1971structure}, see also
-\cite{humphreys2008representations}).)
-
 %% Define external border of irreducible representation here
@@
 \alpha_{j},\ j=1,\dots,r_{\af}$.
+
+Each $\gf$-module is also an $\af$-module, although
+$L^{\mu}_{\gf}$ is not irreducible as $\af$-module. It can be
+decomposed into the sum of irreducible $\af$-modules:
+\begin{equation}
+  \label{eq:16}
+  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
+\end{equation}
+Coefficients in this decomposition are called the branching
+coefficients.
+
+Before we proceed to recurrent relation for branching coefficients we need several definitions.
 
@@
 
-Each $\gf$-module is also an $\af$-module, although
-$L^{\mu}_{\gf}$ is not irreducible as $\af$-module. It can be
-decomposed into the sum of irreducible $\af$-modules:
-\begin{equation}
-  \label{eq:16}
-  L^{\mu}_{\gf}=\bigoplus_{\nu}b^{\mu}_{\nu}L^{\nu}_{\af}
-\end{equation}
-Coefficients in this decomposition are called the branching
-coefficients. Using the Weyl character formula we can write a
-recurrent relation \cite{2010arXiv1007.0318L} for branching
+Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
+If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in W_{\af}$.
+
+Now we can use the Weyl character formula to write a
+recurrent relation \cite{2010arXiv1007.0318L} for signed branching
 coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
@@
 mathematical objects, problems and relations we now describe the
-related datastructures introduced in {\bf Affine.m}. Although {\it
+related datastructures of {\bf Affine.m}. Although {\it
 Mathematica} is untyped language it is possible to create
@@
 \begin{lstlisting}[mathescape=true]
-  $B_2$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, -1}], finiteWeight[2,{0, 1}]}]}
+  $B_2$ == makeFiniteRootSystem[ { {1, -1}, {0, 1} }]
 \end{lstlisting}
@@
 \begin{lstlisting}[mathescape=true]
-  $A_1$+$A_1$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 1}]}]
+  $A_1\oplus A_1$ == finiteRootSystem[2, 2, {finiteWeight[2, {1, 0}], finiteWeight[2, {0, 1}]}]
 \end{lstlisting}
@@
 \begin{lstlisting}[label=list:1]
-  rho[b2]
-  finiteWeight[2, {3/2, 1/2}]
+  In[1]  =  rho[b2]
+  Out[1]  =  finiteWeight[2, {3/2, 1/2}]
 \end{lstlisting}
@@
 
-Computation of ShortLex form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching features of {\it Mathematica}.
+Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching features of {\it Mathematica}.
 In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
@@
 
-We represent formal characters of representations by special structure \lstinline{formalElements}.
+We represent formal characters of representations by special structure \lstinline{formalElement}.
 This structure is a hash-table implemented with \lstinline{DownValues}.
@@
   In[3]  = In[1][multiplicities]
-  Out[3]= {8, 8, 2}
+  Out[3] = {8, 8, 2}
 \end{lstlisting}
@@
 
-{\bf Affine.m} can be used to study different kinds of modules, e.g.
-Verma modules, irreducible modules.
-We need datastructure to represent generic module of Lie algebra $\gf$.
-This datastructure is \lstinline{module}.
+{\bf Affine.m} can be used to study different kinds of modules, i.e.
+Verma modules, irreducible modules and parabolic Verma modules .
+We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$.
 Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
@@
 Then it is possible to study only main Weyl chamber $C_{\af}$.
-So generic constructor for \lstinline{module} datastructure is \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],opts___?OptionQ]}.
+To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],opts___?OptionQ]}.
 Here \lstinline{rs} is root system of Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is root system corresponding to Weyl group $W_{\af}$ which is the symmetry of the set of singular weights.
-There are several constructors for different highest weight modules:
+There are several specialized constructors for different types of highest weight modules:
 \begin{lstlisting}[mathescape=true]
+\leabel
 vm=makeVermaModule[$B_{2}$][weight[$B_{2}$][2,1]];
@@
 im=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
-drawPlaneProjection[2,1,{character[vm],character[pm],character[im]} ]
-\end{lstlisting}
+Show[textPlot/@{im,vm,pm}]
+\end{lstlisting}
+\begin{figure}[h]
+  \label{irrep-verma-pverma}
+  \noindent\centering{
+    \includegraphics[width=150mm]{irrep-verma-pverma.pdf}
+  }
+  \caption{Weight diagrams of $B_{2}$ highest weight modules with highest weight $[2,1]$: irreducible, Verma, parabolic Verma. Produced by code of Listing}
+\end{figure}
+
+As we already stated properties of the module are encoded by its singular element.
+Function \lstinline{singularElement[m_module]} returns singular element of module as \lstinline{formalElement} datastructure.
+Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by function \lstinline{character[m_module]}.
+Direct sum of modules is module and we use natural notation
+\begin{lstlisting}[mathescape=true]
+im1=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
+im2=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][1,2]];
+character[im1$\oplus$ im2]
+\end{lstlisting}
+Figure
+
+Tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of present paper.
+
+Computation of weight multiplicities in function and branching coefficients 
 \section{Computational algorithms}

### 2011-07-13 tests/tests.m
Tests for branching

@@ -149,9 +149,11 @@ Module[{b2=makeSimpleRootSystem[B,2]},
 Module[{b2=makeSimpleRootSystem[B,2]},
        Expect["orbit is equivalent to partial orbit",True, partialOrbit[b2][{rho[b2]}]=== orbit[b2][rho[b2]]]]
 
-Module[{b2=makeSimpleRootSystem[B,2]},
-       Expect["Positive roots of B2",True, Union[positiveRoots[b2]]===Union[{makeFiniteWeight[{1,-1}],makeFiniteWeight[{0,1}],
-							       makeFiniteWeight[{1,0}],makeFiniteWeight[{1,1}]}]]]
+
+Expect["Positive roots of B2",True, 
+       Module[{b2=makeSimpleRootSystem[B,2]},
+	      Union[positiveRoots[b2]]===Union[{makeFiniteWeight[{1,-1}],makeFiniteWeight[{0,1}],
+						makeFiniteWeight[{1,0}],makeFiniteWeight[{1,1}]}]]]
 
 Expect["Dimension",5, dimension[{makeFiniteWeight[{1,1}]}][makeFiniteWeight[{2,2}]]]
 
@@ -187,9 +189,7 @@ Module[{b2a=makeAffineExtension[makeSimpleRootSystem[B,2]]},
 								       makeAffineWeight[{0, 1}, 0, 0], 
 								       makeAffineWeight[{1, 1}, 0, 0], 
 								       makeAffineWeight[{1, 0}, 0, 0], 
-								       makeAffineWeight[{0, 0}, 0, 0], 
 								       makeAffineWeight[{0, 0}, 0, 1], 
-								       makeAffineWeight[{0, 0}, 0, 0], 
 								       makeAffineWeight[{0, 0}, 0, 1]}]];
        b2a[gradeLimit]=.;]
 

### 2011-07-14 src/affine.m
weightSystem works for irreducible and Verma modules

@@ -827,16 +827,30 @@ weightSystem[{posroots__?weightQ},{initialWeights__?weightQ}]:=weightSystem[{pos
 dropWhile = Drop[#, LengthWhile[#, #2]] &;
 
 weightSystem[m_module]:=
-    Module[{check,rs=rootSystem[m],res},
-	   check=If [subSystem[m]=!=emptyRootSystem[],
-		     mainChamberQ[subSystem[m]][#] && checkGrade[rs][#] & , 
-		     checkGrade[rs]];
+    Module[{check,rs=rootSystem[m],res,roots},
+	   res=
+	   If [subSystem[m]=!=emptyRootSystem[],
+	       roots=simpleRoots[subSystem[m]];
+	       Select[
+		   Union[Flatten[
+		       FixedPointList[
+			   Function[x,
+				    Complement[Select[
+					Flatten[Outer[If[#1.#2>0 && checkGrade[rs][#2-#1],#2-#1]&,roots,x]],
+						   #=!=Null&],x]],
+			   cSingularWeights[m][weights]]]],
+		   mainChamberQ[subSystem[m]]],
+	       cSingularWeights[m][weights]];
+	   roots=If [subSystem[m]=!=emptyRootSystem[],Complement[simpleRoots[rs],simpleRoots[subSystem[m]]],simpleRoots[rs]];
 	   res=Select[
 	       Flatten[
 		   Function[x,
-			    x-((Plus @@ (simpleRoots[rs]*#) )& /@ Flatten[Permutations/@IntegerPartitions[#,{Length[simpleRoots[rs]]},Range[0,#]]&/@Range[0,limit[m]],2])]/@cSingularWeights[m][weights]],
-	       check];
+			    x-((Plus @@ (roots*#) )& /@ 
+			       Flatten[Permutations/@IntegerPartitions[#,{Length[roots]},Range[0,#]]&/@
+				       Range[0,limit[m]],2])]/@res],
+	       checkGrade[rs]];
 	   makeFormalElement[res,Table[1,{Length[res]}]]];
+
 (*
 weightSystem[m_module]:=Module[{roots,checkLimit,rh,rs=rootSystem[m],res},
 			       roots=simpleRoots[rs];

### 2011-07-14 doc/paper.tex
Some examples added.

@@
 \begin{lstlisting}[mathescape=true]
-\leabel
 vm=makeVermaModule[$B_{2}$][weight[$B_{2}$][2,1]];
@@
 im=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
-Show[textPlot/@{im,vm,pm}]
-\end{lstlisting}
-\begin{figure}[h]
-  \label{irrep-verma-pverma}
-  \noindent\centering{
-    \includegraphics[width=150mm]{irrep-verma-pverma.pdf}
-  }
-  \caption{Weight diagrams of $B_{2}$ highest weight modules with highest weight $[2,1]$: irreducible, Verma, parabolic Verma. Produced by code of Listing}
-\end{figure}
+GraphicsRow[textPlot/@{im,vm,pm}]
+$\includegraphics[width=130mm]{irrep-verma-pverma.pdf}$
+\end{lstlisting}
 
@@
 im2=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][1,2]];
-character[im1$\oplus$ im2]
-\end{lstlisting}
-Figure
+textPlot[im1$\oplus$ im2]
+$\includegraphics[width=60mm]{irrep-sum.pdf}$
+\end{lstlisting}
 
@@
 
-Computation of weight multiplicities in function and branching coefficients 
 \section{Computational algorithms}
@@
 So Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
-But Freudenthal formula is of no use if we are interested in Verma modules.
+Note that Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
+
+We have made some experiments with our implementations of Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts dependence of computation time on number of weights in module.
+
+\begin{figure}[h]
+  \noindent\centering{
+    \includegraphics[width=80mm]{timing.pdf}
+  }
+  \caption{Running time of algorithms based on recurrent formula \eqref{eq:15} (in blue) and \eqref{eq:14} (in red) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
+\label{fig:freudenthal-racah-times}
+
+\end{figure}
 
@@
 In the case of direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than square of number of elements in main Weyl chamber of subalgebra with non-zero branching coefficients.
-To further illustrate this performance issue we include the Figure \ref{fig:branching} where we show the time required for computations.
-
-\subsection{Performance testing}
-\label{sec:performance-testing}
-
-We have made some experiments with our implementations of Freudenthal formula and formula \eqref{eq:15} and have got the following graphs \ref{freudenthal-racah-times}.
+
+To further illustrate this performance issue we include the Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
+
 \begin{figure}[h]
-  \label{freudenthal-racah-times}
   \noindent\centering{
-    \includegraphics[width=80mm]{timing.pdf}
+   \includegraphics[width=100mm]{branching-timing.pdf}
   }
-  \caption{Running time of algorithms based on recurrent formula \eqref{eq:15} (in blue) and \eqref{eq:14} (in red) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
-\end{figure}
-
-\begin{figure}[h]
-%  \label{freudenthal-racah-times}
-  \noindent\centering{
- %   \includegraphics[width=80mm]{figure1.eps}
-  }
-  \caption{Freudenthal run time with the number of weights in $\bar C$.}
-
-  \noindent\centering{
- %   \includegraphics[width=80mm]{figure1.eps}
-  }
-  \caption{Racah run time with the number of weights in $\bar C$.}
-
-  \noindent\centering{
- %   \includegraphics[width=80mm]{figure1.eps}
-  }
-  \caption{Freudenthal run time with rank of the algebra}
-
-  \noindent\centering{
- %   \includegraphics[width=80mm]{figure1.eps}
-  }
-  \caption{Racah run time with rank of the algebra}
-\end{figure}
-
-Measurements for branching computations for $\hat B_{3}\subset \hat B_{4}$ are shown at the Fig. \ref{fig:branching}.
-\begin{figure}[h]
+  \caption{Running time of algorithms based on recurrent formula \eqref{eq:15} (in blue) and \eqref{eq:14} (in red) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
   \label{fig:branching}
-  \noindent\centering{
- %   \includegraphics[width=80mm]{figure1.eps}
-  }
-  \caption{Branching}
 \end{figure}
@@
 
-\begin{figure}[h]
-  \label{tensor-product-decomposition-b2}
-  \noindent\centering{
-    \includegraphics[width=80mm]{branching.pdf}
-  }
-  \caption{Fusion coefficients for $\left(L^{(1,0)}\right)^{\otimes 10}$}
-\end{figure}
+Consider tensor power of $B_{2}$ first fundamental representations $\left(L^{[1,0]}\right)^{\otimes 4}$.
+Decomposition coefficients are just branching coefficients for tensor product module to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$.
+So following code calculates these coefficients:
+\begin{lstlisting}[mathescape=true]
+fm = makeIrreducibleModule[$B_{2}$][1, 0];
+tp = ((fm$\otimes$ ]fm)$\otimes$ fm)$\otimes$]fm;
+subs = makeFiniteRootSystem[
+  {1/4*{1, -1, 1, -1, 1, -1, 1, -1}, 
+   1/4*{0, 1, 0, 1, 0, 1, 0, 1}}];
+bc = branching[tp, subs];
+{bc[#], dynkinLabels[subs][#]} & /@ bc[weights]
+\end{lstlisting}
+It produces list of highest weights and tensor product decomposition coefficients:
+\begin{lstlisting}
+{{1, {4, 0}}, {3, {2, 2}}, {0, {3, 0}}, 
+{2, {0, 4}}, {3, {1, 2}}, {6, {2, 0}}, 
+{6, {0, 2}}, {1, {1, 0}}, {3, {0, 0}}}]
+\end{lstlisting}
+
+Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
 
@@
 \begin{lstlisting}[mathescape=true]
-stringFunciton[$\hat A_2$][weight[$\hat A_{2}$][1,0,0]][weight[$\hat A_{2}$][0,1,0]]
-$1+q^2 +q^{3}+\dots$
+stringFunctions[$\hat A_2$,{1,1,2}]
+{{0, 0, 4}, 
+  $2 q + 10 q^2 + 40 q^3 + 133 q^4 + 398 q^5 + 1084 q^6 + 2760 q^7 + 6632 q^8 + 15214 q^9 + 33508 q^{10}$}, 
+{{0, 3, 1}, 
+  $2 q + 12 q^2 + 49 q^3 + 166 q^4 + 494 q^5 + 1340 q^6 + 3387 q^7 + 8086 q^8 + 18415 q^9 + 40302 q^{10}$}, 
+{{1, 1, 2}, 
+  $1 + 6 q + 27 q^2 + 96 q^3 + 298 q^4 + 836 q^5 + 2173 q^6 + 5310 q^7 + 12341 q^8 + 27486 q^9 + 59029 q^{10}$}, 
+{{2, 2, 0}, 
+  $1 + 8 q + 35 q^2 + 124 q^3 + 379 q^4 + 1052 q^5 + 2700 q^6 + 6536 q^7 + 15047 q^8 + 33248 q^9 + 70877 q^{10}$}, 
+{{3, 0, 1}, 
+  $2 + 12 q + 49 q^2 + 166 q^3 + 494 q^4 + 1340 q^5 + 3387 q^6 + 8086 q^7 + 18415 q^8 + 40302 q^9 + 85226 q^{10}$}
 \end{lstlisting}
@@
 Branching functions of the embedding $\af\subset\gf$ are the partition functions of CFT on the torus.
+
+\begin{lstlisting}[mathescape=true]
+branchingFunctions[$\hat B_{2}$,makeAffineExtension[makeFiniteRootSystem[{{1, 1}}]], {1, 1, 1}]
+
+ {{3, 0}, 
+  $2 + 14 q + 52 q^2 + 154 q^3 + 410 q^4 + 994 q^5 + 2248 q^6 + 4832 q^7 + 9934 q^8 + 19680 q^9 + 37802 q^{10}$},
+ {{2, 1}, 
+  $4 + 20 q + 72 q^2 + 220 q^3 + 584 q^4 + 1424 q^5 + 3248 q^6 + 7012 q^7 + 14488 q^8 + 28844 q^9 + 55616 q^{10}$},
+ {{0, 3}, 
+  $4 q + 20 q^2 + 68 q^3 + 200 q^4 + 516 q^5 + 1224 q^6 + 2736 q^7 + 5808 q^8 + 11820 q^9 + 23236 q^{10}$},
+ {{1, 2}, 
+  $2 + 14 q + 54 q^2 + 168 q^3 + 462 q^4 + 1148 q^5 + 2656 q^6 + 5812 q^7 + 12130 q^8 + 24358 q^9 + 47328 q^{10}$}
+\end{lstlisting}
 

### 2011-07-14 src/affine.m

@@ -299,7 +299,7 @@ directSum::"usage"=
 
 CirclePlus::"usage"=CirclePlus::"usage" <> "\n denotes direct sum of modules";
 
-decomposion::"usage"=
+decomposition::"usage"=
     "Tensor product decomposition"
 
 fan::"usage"=
@@ -440,7 +440,7 @@ finiteRootSystem/:x_finiteRootSystem[finiteRootSystem]=x;
 rank[rs_?rootSystemQ]=rs[rank];
 simpleRoot[rs_?rootSystemQ]=rs[simpleRoot];
 simpleRoots[rs_?rootSystemQ]=rs[simpleRoots];
-dimension[rs_?rootSystemQ]=rs[dimension];
+(*dimension[rs_?rootSystemQ]=rs[dimension];*)
 
 prependZeros[num_Integer,vec_finiteWeight]:=makeFiniteWeight[Join[Table[0,{num}],vec[standardBase]]];
 
@@ -828,27 +828,25 @@ dropWhile = Drop[#, LengthWhile[#, #2]] &;
 
 weightSystem[m_module]:=
     Module[{check,rs=rootSystem[m],res,roots},
-	   res=
-	   If [subSystem[m]=!=emptyRootSystem[],
-	       roots=simpleRoots[subSystem[m]];
-	       Select[
-		   Union[Flatten[
-		       FixedPointList[
-			   Function[x,
-				    Complement[Select[
-					Flatten[Outer[If[#1.#2>0 && checkGrade[rs][#2-#1],#2-#1]&,roots,x]],
-						   #=!=Null&],x]],
-			   cSingularWeights[m][weights]]]],
-		   mainChamberQ[subSystem[m]]],
-	       cSingularWeights[m][weights]];
 	   roots=If [subSystem[m]=!=emptyRootSystem[],Complement[simpleRoots[rs],simpleRoots[subSystem[m]]],simpleRoots[rs]];
 	   res=Select[
 	       Flatten[
 		   Function[x,
 			    x-((Plus @@ (roots*#) )& /@ 
 			       Flatten[Permutations/@IntegerPartitions[#,{Length[roots]},Range[0,#]]&/@
-				       Range[0,limit[m]],2])]/@res],
+				       Range[0,limit[m]],2])]/@cSingularWeights[m][weights]],
 	       checkGrade[rs]];
+	   If [subSystem[m]=!=emptyRootSystem[],
[…]

### 2011-07-14 tests/debug2.m

@@ -2,7 +2,196 @@ AppendTo[$Path,$InitialDirectory <> "/../src/"];
 
 <<affine.m;
 
-[Calculating...]
+b2=makeSimpleRootSystem[B,2];
+vm=makeVermaModule[b2][{2,2},3];
+pm=makeParabolicVermaModule[b2][weight[b2][2,2],{1},3];
+im=makeIrreducibleModule[b2][2,2];
+
+vm=makeModule[b2][makeFormalElement[{weight[b2][2,2]},{1}],emptyRootSystem[],{limit->20}]
+
+
+textPlot[m_module]:=drawPlaneProjection[2,1,character[m],{Axes->False}];
+
+Export["mplot.png",GraphicsRow[textPlot/@{im,vm,pm}]]
+
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
+{5 >= -(Affine`Private`limit -> 
+ 
+>       Min[-10, -finiteRootSystem[2, 2, 
+ 
+>           {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}][gradeLimit]])
+ 
+>    }
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
+{True}
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
+{True}
+
+Out[6]= mplot.png
+
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
+{5 >= -(Affine`Private`limit -> 
+ 
+>       Min[-10, -finiteRootSystem[2, 2, 
+ 
+>           {finiteWeight[2, {1, -1}], finiteWeight[2, {0, 1}]}][gradeLimit]])
+ 
+>    }
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
+{True}
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
+{True}
+
+Out[4]= mplot.png
+
+Out[20]= $Aborted
+
+weightSystem[vm]
+
+Length[Out[18][weights]]
+
+Out[19]= 42436
+
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
+{True}
+
+Out[18]= formalElement[Affine`Private`table$177]
+
+{finiteWeight[2, {-1, 1}], finiteWeight[2, {0, -1}]}
[…]

### 2011-07-15 doc/paper.tex
Examples in paper completed.

@@
 \newcommand{\pf}{\mathfrak{p}}
+\newcommand{\aft}{\widetilde{\mathfrak{a}}}
 
@@
 We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
-We describe the features and limitations of the package in present paper and in the manual \cite{affinemanual}.
-In present paper we also provide representation-theoretical background of implemented algorithms and present some examples of computations relevant to physics.
+We describe the features and limitations of the package in present paper.
+We also provide representation-theoretical background of implemented algorithms and present some examples of computations relevant to physics.
 
@@
 defined for finite and affine weights. The complete list can be
-found in the user manual \cite{affinemanual}. The most important
+found in package online help. The most important
 are the definitions of addition, multiplication by number and
@@
 GraphicsRow[textPlot/@{im,vm,pm}]
-$\includegraphics[width=130mm]{irrep-verma-pverma.pdf}$
+$\includegraphics[width=130mm]{figures/irrep-verma-pverma.pdf}$
 \end{lstlisting}
@@
 textPlot[im1$\oplus$ im2]
-$\includegraphics[width=60mm]{irrep-sum.pdf}$
+$\includegraphics[width=60mm]{figures/irrep-sum.pdf}$
 \end{lstlisting}
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{timing.pdf}
+    \includegraphics[width=80mm]{figures/timing.pdf}
   }
@@
   \noindent\centering{
-   \includegraphics[width=100mm]{branching-timing.pdf}
+   \includegraphics[width=100mm]{figures/branching-timing.pdf}
   }
@@
 
-We illustrate the connection of branching with generalized BGG-resolution with the sequence of parabolic Verma modules which appear in the study of branching of irreducible $B_{2}$-modules to the modules of subalgebra $A_{1}$.
-Root of the subalgebra $A_{1}$ in this case is equal to the highest root $\Theta$ of algebra $B_{2}$.
-In this case orthogonal sub-algebra $\afb$ gives rise to the parabolic Verma modules \cite{2011arXiv1102.1702L}.
+We illustrate generalized BGG-resolution with the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
+\begin{equation}
+\mathrm{ch}\left( L^{\mu }\right) =\sum_{u\in U}\;e^{\mu _{\aft}\left(
+u\right) }\epsilon (u)\mathrm{ch}M_{I}^{\mu _{\frak{a}_{\perp }}\left(
+u\right) }.  \label{char-in-gen-verma-mod}
+\end{equation}
+Character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
+Characters in upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in lower row with negative.
 
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{branching.pdf}
+    \includegraphics[width=80mm]{figures/G2-irrep.pdf}
   }
-  \caption{Parabolic Verma modules from branching}
+  \caption{Character of irreducible $G_{2}$-module $L^{[1,1]}$}
+\end{figure}
+\begin{figure}[h]
+  \label{g2-pverma}
+  \noindent\centering{
+    \includegraphics[width=150mm]{figures/G2-pverma.pdf}
+  }
+  \caption{Character of $G_{2}$ generalized Verma modules appearing in decomposition of $L^{[1,1]}$}
 \end{figure}
@@
 
-Branching functions of the embedding $\af\subset\gf$ are the partition functions of CFT on the torus.
-
+Branching functions of the embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).
+
+As first example we show computation of branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to tenth grade:
 \begin{lstlisting}[mathescape=true]
@@
 
-\begin{figure}[h]
-  \label{branching-b4-b2}
-  \noindent\centering{
-    \includegraphics[width=80mm]{branching.pdf}
-  }
-  \caption{Branching coefficients of module $L^{\left[0,1,0,2\right]}$ for regular embedding $B_{2}\subset B_{4}$ displayed in the basis $\left\{e_3,e_4\right\}$}
-\end{figure}
+Another example is computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
+\begin{lstlisting}[mathescape=true]
+sub=makeAffineExtension[parabolicSubalgebra[$C_{3}$][2,3]];
+branchingFunctions[$\hat C_{3}$,sub, {2, 0, 0, 0}]
+
+{{0, 1, 0}, 
+  $2 q - 20 q^3 + 24 q^4 + 82 q^5 - 320 q^6 + 108 q^7$}, 
+{{1, 0, 0}, 
+  $1 - q - 8 q^2 + 19 q^3 + 16 q^4 - 156 q^5 + 205 q^6 + 640 q^7$}, 
+{{0, 0, 1}, 
+  $q - 5 q^3 + 7 q^5$}
+\end{lstlisting}
 
@@
 \label{sec:conclusion}
-We present the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
-The package is available from {\it github} and is also submitted to the library.
+We have presented the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
+It can be used to study Weyl groups, roots systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
+In present paper we have also discussed main ideas used for implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
+
+We have demonstrated that recurrent approach based upon Weyl character formula is not only useful for calculations but also allows to see connection with (generalized) Bernstein-Bernstein-Gelfand resolution.
+
+Also we have presented examples of computations with this package connected with problems of physics and mathematics.
+
+\section*{Acknowledgements}
+\label{sec:acknowledgements}
+The work is supported by the Chebyshev Laboratory
+(Department of Mathematics and Mechanics, Saint-Petersburg State
+University) under the grant 11.G34.31.0026 of the Government of the
+Russian Federation.
 
@@
 \label{package}
-The package can be freely downloaded from {\it github}. Latest release can be found here. To get the development code use the command
+The package can be freely downloaded from \url{http://github.com/naa/Affine}. To get the development code use the command
 \begin{lstlisting}[language=bash]
@@
         demo.nb                                demo notebook
-        paper.nb                               code from the paper
+        paper.nb                               code for the paper
       doc/                                 documentation folder
-        figures/                             figures in paper and manual
+        figures/                             figures in paper 
           timing.pdf                           diagram showing performance
-          branching.pdf                        branching coefficients
+          branching-timing.pdf                 ...  for branching coefficients  
+          irrep-sum.pdf                        sum of B2 irreps
+          irrep-verma-pverma.pdf               irrep, Verma, (p)Verma for B2
+          G2-irrep.pdf                         irrep for G2
+          G2-pverma.pdf                        parabolic Verma for G2
         bibliography.bib                     bibliographic database
-        manual.pdf                           manual
-        manual.tex                           manual source
-        paper.pdf                            paper
+        paper.pdf                            present paper
         paper.tex                            paper source
@@
         tests.m                              unit tests
-      README.markdown                      short description of software
+      README.markdown                      installation and usage notes
 \end{verbatim}

### 2011-07-15 src/affine.m

@@ -7,7 +7,7 @@ standardBase::"usage"=
     E.g. simple roots for B2 are standardBase[1,-1] and standardBase[0,1]";
 
 finiteWeight::"usage"=
-    "finiteWeight[dimension_?NumberQ,coordinates_standardBase] represents\ 
+    "finiteWeight[dimension_?NumericQ,coordinates_standardBase] represents\ 
     vector in weight space of finite-dimensional Lie algebra.\n 
     finiteWeight[dimension] returns dimension of the space, where weight vector is embedded\ 
     (i.e. for sl_n it is n+1).\n 
@@ -23,7 +23,7 @@ standardBase::"usage"=
     "standardBase[wg_?weightQ] returns coorinates of finite part of finite part of weight in standard (Bourbaki) basis";
 
 makeFiniteWeight::"usage"=
-    "makeFiniteWeight[{coordinates__?NumberQ}] creates finiteWeight with given coordinates in standard base";
+    "makeFiniteWeight[{coordinates__?NumericQ}] creates finiteWeight with given coordinates in standard base";
 
 Dot::"usage"=Dot::"usage" <> "\n It is defined for weights of finite and affine Lie algebras";
 
@@ -35,7 +35,7 @@ Times::"usage"=Times::"usage"<>"\n\n Mutliplication by numbers is defined for th
     \n For example makeFiniteWeight[{1,2,3}]*2==makeFiniteWeight[{2,4,6}]]";
 
 affineWeight::"usage"=
-    "affineWeight[dimension_?NumberQ,fw_finiteWeigt,level_?NumberQ, grade_?NumberQ] represents\ 
+    "affineWeight[dimension_?NumericQ,fw_finiteWeigt,level_?NumericQ, grade_?NumericQ] represents\ 
     vector in weight space of affine Lie algebra.\n 
     affineWeight[dimension] returns dimension of the space of real roots, where finite weight vector is embedded\ 
     (i.e. for sl_n it is n+1).\n 
@@ -50,8 +50,8 @@ grade::"usage"=
     "grade[w_affineWeight] or w[grade] returns grade of weight of affine Lie algebra";
 
 makeAffineWeight::"usage"= 
[…]

### 2011-07-22 doc/paper.tex
References to Figures are fixed.
Paper corrections before arXiv submission.

@@
 %%
-\documentclass[preprint,12pt]{elsarticle}
+\documentclass[preprint,review,12pt]{elsarticle}
 
@@
 Algorithms are based upon the properties of weights and Weyl symmetry.
-The most important for us problems are computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
+The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
 These problems have numerous applications in physics and we provide some examples of these applications.
@@
 We describe the features and limitations of the package in present paper.
-We also provide representation-theoretical background of implemented algorithms and present some examples of computations relevant to physics.
-
-The paper is started with an overview of Lie algebras and their representation theory (Sec.
+We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physics.
+
+The paper starts with an overview of Lie algebras and their representation theory (Sec.
 \ref{sec:theor-backgr}).
@@
 
-{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it commutator}.
+{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
 If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
@@
 \end{equation}
-This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
-
-Sometimes we denote affine Lie algebra by $\gf$ then corresponding finite-dimensional Lie algebra is denoted by $\go$.
+This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+
+We do not treat twisted affine Lie algebras in present paper.
 
@@
 Eigenvalues $\nu^{i}_{j}$ of Cartan generators on element of basis $v_{j}$ determine weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Vector $v\in V$ is called weight vector of weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$ , weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+Vector $v\in V$ is called weight vector of weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+Weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
 Weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of weight subspace.
@@
 Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-Character can be specialized by taking its value on some element $\xi$ of $\hf$:
+Character can be specialized by taking its value on some element $\xi$ of $\hf$.
 
@@
 In case of finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to rank of the algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-By numbering simple roots with an index $i$ we introduce an ordering on the root system $\Delta$.
+By numbering simple roots with an index $i$ we introduce lexicographic ordering on the root system $\Delta$.
 Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
@@
 
-Sub-algebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for $\alpha\in \Delta^{+}$ positive is called Borel sub-algebra.
+Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called Borel subalgebra.
 
@@
 
-The Weyl group $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
+The {\it Weyl group} $W_{\gf}$ is generated by reflections $\{s_{i}:\hfg^{*}\to\hfg^{*}\}$ corresponding to simple roots $\{\alpha_{i}\}$:
 \begin{equation}
@@
 
-Consider an action of element $s_{0}s_{i}s_{0}$ of Weyl group of affine Lie algebra  $\hat\gf$.
-Using the definition \eqref{eq:8} it is easy to see that $s_{0}s_{i}s_{0}\cdot \lambda=\lambda+\alpha_{i}$, so Weyl group can be presented as semidirect product of Weyl group $W_{\gf}$ of $\gf$ and translations by the roots of $\hat \gf$.
+Consider an action of element $s_{\alpha}s_{\alpha+\delta}$ of Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ simple root of underlying finite-dimensional Lie algebra $\gf$.
+Using the definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+So Weyl group can be presented as semidirect product of Weyl group $W_{\gf}$ of $\gf$ and translations corresponding to the roots of $\gf$.
+
 Weyl group element can be presented as the product of elementary reflections in multiple ways.
@@
 
-The Cartan matrix $A$ is defined by products of simple roots
+The {\it Cartan matrix} $A$ is defined by products of simple roots
 \begin{equation}
@@
 The form \eqref{eq:9} induces the basis dual  to the simple
-roots basis. It is called the fundamental weights basis. We denote
+roots basis. It is called the {\it fundamental weights basis}. We denote
 its elements by $\omega_i$:
@@
 For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \lambda_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of finite-dimensional Lie algebra $\go$.
-
-We need to introduce Weyl vector denoted by $\rho=\sum_{i} \omega_{i}$. It is of importance for the construction of algebra modules.
+Other fundamental weights are equal to $\omega_i=a_i^v \lambda_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of finite-dimensional Lie algebra $\gf$.
+
+{\it Weyl vector} is equal to the sum of fundamental weights $\rho=\sum_{i} \omega_{i}$. It is of importance for the construction of algebra modules.
 
@@
 where $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
-Here $\bff_{+}$ is Borel sub-algebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
+Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
 Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D_{\lambda}(\bff_{+})$.
@@
 unique nontrivial simple quotient $L^{\mu}$ which is an
-irreducible highest weight module. Weyl character formula for
+{\it irreducible highest weight module}.
+
+Irreducible highest weight modules have no non-trivial submodules. 
+Weyl character formula for
 irreducible highest weight modules is
@@
 
-We can use Weyl character formula to obtain recurrent relation on weight multiplicities which can be used for calculations \cite{il2010folded,kulish4sfa}:
+We can use Weyl character formula to obtain recurrent relation on weight multiplicities which can be used for calculations \cite{il2010folded,kulish4sfa}.
+
+For irreducible highest-weight modules recurrent relation has form
 \begin{equation}
@@
 \end{equation}
+Formulae for Verma and generalized Verma modules differs only in second term on the right-hand side.
+In case of Verma module it is just $\delta_{\xi,\mu}$.
+For generalized Verma module summation in second term on the right-hand side \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
 
@@
 It is called the Freudenthal multiplicity formula.
+Note that it is applicable only to irreducible only to irreducible modules.
+
+We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
 
@@
 
-Before we proceed to recurrent relation for branching coefficients we need several definitions.
+It is possible to calculate branching coefficients by the construction and repeated subtraction of characters of modules $L^{\nu}_{\af}$.
+This traditional approach has serious limitations especially in case of affine Lie algebras.
+We discuss them in the end of section \ref{sec:comp-algor}.
+
+Now we describe alternative approach which is based upon recurrent relation on branching coefficients. 
+But before we proceed to this recurrent relation we need several definitions.
 
@@
 
-For $\af$ and $\afb$ consider the
+Cartan subalgebra can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+\frak{h}_{\afb}\oplus \frak{h}_{\perp }$
+
+We also introduce notation
+\begin{eqnarray}
+\widetilde{\frak{a}_{\perp }} :=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
+\qquad
+\widetilde{\frak{a}} :=\frak{a}\oplus \frak{h}_{\perp }.
+\end{eqnarray}
+
+For $\af$ and $\afb$ we consider the
 corresponding Weyl vectors, $\rho _{\af}$ and $\rho _{\af_{\perp
-}} $.
-
-Compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
+}} $ and compose the so called ''defects'' $\mathcal{D}_{\af}$ and $\mathcal{%
 D}_{\afb}$ of the injection:
@@
 \end{equation}
-The recursion is goverened by the set $\Gamma _{\widetilde{\af}\rightarrow \gf}$ called the injection fan. The latter is defined by the
+The recursion is governed by the set $\Gamma _{\af\rightarrow \gf}$ called the injection fan. The latter is defined by the
 carrier set $\left\{ \xi \right\} _{\af\rightarrow \gf}$ for the
@@
 \begin{equation}
-\Gamma _{\widetilde{\af}\rightarrow \gf}=\left\{ \xi -\gamma
+\Gamma _{\af\rightarrow \gf}=\left\{ \xi -\gamma
 _{0}|\xi \in \left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
@@
 equivalent to branching problem for the diagonal subalgebra
-$\gf\subset \gf\otimes \gf$ (see \cite{LyakhovskyPostnova2011}).
+$\gf\subset \gf\otimes \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
 
@@
 \end{align}
-
 String and branching functions have  modular and analytic properties which are important for conformal field theory, especially in  coset models and the study of CFT on higher genus surfaces \cite{kac1988modular}, \cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}.
+
+{\bf Affine.m}  calculates weight multiplicities and branching coefficients for affine Lie algebras up to some finite grade.
+We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
+Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
 
@@
 \lstinline{Head} \lstinline{finiteWeight}, its components are the
-coordinates of the weight in the orthogonal basis of
+coordinates of the weight in the orthogonal basis of Bourbaki 
 \cite{bourbaki2002lie}.
@@
 defined for finite and affine weights. The complete list can be
-found in package online help. The most important
+found in  online help of the package. The most important
 are the definitions of addition, multiplication by number and
@@
 \end{lstlisting}
-We use typographic features of {\it Mathematica} frontend to offer traditional mathematical notation for simple Lie algebras:
+We use typographic features of {\it Mathematica} frontend to offer mathematical notation for simple Lie algebras:
 
@@
 
-Elements of Weyl group are specified by the set of indices of reflections, so element of Weyl group of algebra $B_{2}$ which is equal to $w=s_{1}s_{2}s_{1}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
+Elements of Weyl group are specified by the set of indices of reflections, so element  $w=s_{1}s_{2}s_{1}$ of Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
 Then it can be applied to the weights:
@@
 
-Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching features of {\it Mathematica}.
+Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching in {\it Mathematica}.
 In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
@@
 Then it is possible to study only main Weyl chamber $C_{\af}$.
-To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],opts___?OptionQ]}.
+To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
 Here \lstinline{rs} is root system of Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is root system corresponding to Weyl group $W_{\af}$ which is the symmetry of the set of singular weights.
+Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
 There are several specialized constructors for different types of highest weight modules:
 \begin{lstlisting}[mathescape=true]
-vm=makeVermaModule[$B_{2}$][weight[$B_{2}$][2,1]];
+vm=makeVermaModule[$B_{2}$][{2,1}];
 pm=makeParabolicVermaModule[$B_{2}$][weight[$B_{2}$][2,1],{1}];
-im=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
+im=makeIrreducibleModule[$B_{2}$][2,1];
 GraphicsRow[textPlot/@{im,vm,pm}]
@@
 Tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of present paper.
-
+\begin{lstlisting}[mathescape=true]
+textPlot[makeIrreducibleModule[$A_{1}$][5]$\otimes$ makeIrreducibleModule[$A_{1}$][3]];
+$\includegraphics[width=60mm]{figures/tensor-product.pdf}$
+\end{lstlisting}
 \section{Computational algorithms}
@@
 The difference in performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
-For recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in Weyl group (if we are far from the boundary of representation diagram).
+For  Weyl formula-based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in Weyl group (if we are far from the boundary of representation diagram).
 When Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
@@
   }
-  \caption{Running time of algorithms based on recurrent formula \eqref{eq:15} (in blue) and \eqref{eq:14} (in red) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
+  \caption{Running time of algorithms based on Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
 \label{fig:freudenthal-racah-times}
@@
   }
-  \caption{Running time of algorithms based on recurrent formula \eqref{eq:15} (in blue) and \eqref{eq:14} (in red) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
+  \caption{Running time of algorithms based on Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
   \label{fig:branching}
@@
 
-\subsection{Branchig and parabolic Verma modules}
+\subsection{Branching and parabolic Verma modules}
 \label{sec:branch-parab-verma}
@@
 \begin{figure}[h]
-  \label{branching-bgg}
   \noindent\centering{
@@
   \caption{Character of irreducible $G_{2}$-module $L^{[1,1]}$}
+  \label{branching-bgg}
 \end{figure}
 \begin{figure}[h]
-  \label{g2-pverma}
   \noindent\centering{
@@
   }
-  \caption{Character of $G_{2}$ generalized Verma modules appearing in decomposition of $L^{[1,1]}$}
+  \caption{Character of $G_{2}$ generalized Verma modules appearing in decomposition of $L^{[1,1]}$.
+Parabolic Verma modules in upper row appear in decomposition with positive sign, in lower row -- with negative.}
+  \label{g2-pverma}
 \end{figure}
@@
 \bibliography{bibliography}
-\bibliographystyle{elsarticle-num}
+\bibliographystyle{phcpc}
 %\bibliographystyle{model1-num-names}

### 2011-07-22 src/affine.m

@@ -242,16 +242,16 @@ module::"usage"=
     limit limits number of subtraction in the construction of infinite-dimensional modules"
 
 makeModule::"usage"=
-    "makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem,opts___?OptionQ] is general construction for modules";
+    "makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem,limit:10] is general construction for modules";
 
-makeVermaModule::"usage"="makeVermaModule[rs_?rootSystemQ][hw_?weightQ,opts___?OptionQ] constructs Verma module. \n
-    Option 'limit' limits construction with the number of simple root subtractions. By default it is chosen in such a way\n
+makeVermaModule::"usage"="makeVermaModule[rs_?rootSystemQ][hw_?weightQ,limit:10] constructs Verma module. \n
+    Parameter 'limit' limits construction with the number of simple root subtractions. By default it is chosen in such a way\n
     that Verma module includes corresponding irreducible module";
 
 makeParabolicVermaModule::"usage"=
-    "makeParabolicVermaModule[rs_?rootSystemQ][hw_?weightQ,{symgen___Integer},opts___?OptionQ] constructs parabolic Verma module. \n
+    "makeParabolicVermaModule[rs_?rootSystemQ][hw_?weightQ,{symgen___Integer},limit:10] constructs parabolic Verma module. \n
     {symgen} is the list of root indices of parabolic subalgbra. \n
-    Option 'limit' limits construction with the number of simple root subtractions. By default it is chosen in such a way\n
+    Parameter 'limit' limits construction with the number of simple root subtractions. By default it is chosen in such a way\n
     that Verma module includes corresponding irreducible module";
 
 makeIrreducibleModule::"usage"=
@@ -1104,7 +1104,7 @@ drawPlaneProjection[axe1_,axe2_,f_formalElement,opts___?OptionQ]:=
 draw3dProjection[axe1_,axe2_,axe3_,f_formalElement,opts___?OptionQ]:=
     Graphics3D[(Text[f[#],{#[standardBase][[axe1]],#[standardBase][[axe2]], #[standardBase][[axe3]]}]) & /@ f[weights],opts]
 
-textPlot[m_module]:=drawPlaneProjection[1,2,character[m],{Axes->False}];
[…]

### 2011-07-23 doc/paper.tex
G2 norm fixed, paper mostly finished.

@@
 %%
-\documentclass[preprint,review,12pt]{elsarticle}
+\documentclass[preprint,12pt]{elsarticle}
 
@@
 
-String functions can be given physical meaning if we consider coset models of two-dimensional conformal field theory \cite{Goddard198588}, \cite{difrancesco1997cft}.
-String functions of $\hat\gf$ are equal to branching functions in the case of subalgebra $\hat{u(1)}$ and can be seen as the partition functions of $\hat\gf/\hat{u(1)}$ coset model on the torus.
-
 {\bf Affine.m} produces power series decomposition for string functions.
@@
 \end{lstlisting}
+Similarly for affine Lie algebra $\hat G_{2}$ we get
+\begin{lstlisting}[mathescape=true]
+stringFunctions[$\hat G_2$,{1,1,0}]
+{{2, 0, 0}, 
+  $1 + 8 q + 37 q^2 + 138 q^3 + 431 q^4 + 1227 q^5 + 3208 q^6 + 7901 q^7$}, 
+{{0, 0, 1}, 
+  $3 q + 18 q^2 + 73 q^3 + 247 q^4 + 736 q^5 + 2000 q^6 + 5070 q^7$}, 
+{{1, 1, 0},
+  $1 + 7 q + 32 q^2 + 117 q^3 + 370 q^4 + 1055 q^5 + 2780 q^6 + 6880 q^7$}, 
+{{0, 2, 0}, 
+  $3 q + 15 q^2 + 63 q^3 + 210 q^4 + 633 q^5 + 1725 q^6 + 4407 q^7$}
+\end{lstlisting}
 
@@
 
+In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decomposition.
+
 \section*{Acknowledgements}
 \label{sec:acknowledgements}
+I thank V.D. Lyakhovsky and O.Postnova for discussions and helpful comments.
+
 The work is supported by the Chebyshev Laboratory
@@
           G2-pverma.pdf                        parabolic Verma for G2
+          tensor-product.pdf                   tensor product of A1-modules
         bibliography.bib                     bibliographic database

### 2011-07-23 src/affine.m

@@ -367,10 +367,10 @@ standardBase[wg_?weightQ]=wg[finitePart][standardBase];
 (*makeFiniteWeight[{coordinates__?NumericQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}*)
 makeFiniteWeight[{coordinates__}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}
 
-finiteWeight/:x_finiteWeight . y_finiteWeight:=x[standardBase].y[standardBase]
+finiteWeight/:x_finiteWeight . y_finiteWeight:=Simplify[x[standardBase].y[standardBase]]
 
 finiteWeight/:Plus[wgs__finiteWeight]:=
-    makeFiniteWeight[Plus @@ (#[standardBase]&/@ {wgs})]
+    makeFiniteWeight[Simplify[Plus @@ (#[standardBase]&/@ {wgs})]]
     
 finiteWeight/:x_finiteWeight==y_finiteWeight:=x[standardBase]==y[standardBase]
 
@@ -460,7 +460,7 @@ makeSimpleRootSystem[E,rank_Integer]/; (rank>=3) && (rank<=8) :=makeFiniteRootSy
 								   {1,1,0,0,0,0,0,0}},
 								  Table[{If [ j==i-2, 1, If [j==j-2, -1, 0]]},{i,3,rank},{j,1,8}]]];
 makeSimpleRootSystem[F,4]:=makeFiniteRootSystem[{{1,-1,0,0},{0,1,-1,0},{0,0,1,0},1/2*{1,-1,-1,-1}}];
-makeSimpleRootSystem[G,2]:=makeFiniteRootSystem[{{1,-1,0},{-2,1,1}}];
+makeSimpleRootSystem[G,2]:=makeFiniteRootSystem[{1/Sqrt[3]*{1,-1,0},1/Sqrt[3]*{-2,1,1}}];
 							   
 (*
 elif L='E' and r>2 and r<9 then

### 2011-08-11 src/affine.m
A1 root length fix

@@ -169,6 +169,9 @@ formalOrbit::"usage"="returns the same thing as orbitWithEps, but as formalEleme
 positiveRoots::"usage"=
     "positiveRoots[rs_?rootSystemQ] returns positive roots of root system rs";
 
+roots::"usage"=
+    "roots[rs_?rootSystemQ] returns all roots of root system rs (up to gradeLimit for affine Lie algebra)";
+
 highestRoot::"usage"="returns highest root of root system";
 
 makeAffineExtension::"usage"=
@@ -451,14 +454,15 @@ finiteRootSystem/:CirclePlus[x_finiteRootSystem,y_finiteRootSystem]:=makeFiniteR
 
 affineRootSystem/:CirclePlus[x_affineRootSystem,y_affineRootSystem]:=makeAffineExtension[CirclePlus[x[finiteRootSystem],y[finiteRootSystem]]];
 
-makeSimpleRootSystem[A,1]:=makeFiniteRootSystem[{{1}}];
+(*makeSimpleRootSystem[A,1]:=makeFiniteRootSystem[{{1}}];*)
 makeSimpleRootSystem[A,r_Integer]:=makeFiniteRootSystem[makeFiniteWeight /@ Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,r},{j,1,r+1}]];
 makeSimpleRootSystem[B,rank_Integer]:=makeFiniteRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],1]]];
 makeSimpleRootSystem[C,rank_Integer]:=makeFiniteRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],2]]];
 makeSimpleRootSystem[D,rank_Integer]:=makeFiniteRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Append[Table[0,{rank-2}],1],1]]];
-makeSimpleRootSystem[E,rank_Integer]/; (rank>=3) && (rank<=8) :=makeFiniteRootSystem[Append[{1/2*{1,-1,-1,-1,-1,-1,-1,1},
[…]

### 2011-08-13 doc/paper.tex
Demo prepared, Readme updated

@@
 In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
-Algorithms are based upon the properties of weights and Weyl symmetry.
+Algorithms are based on the properties of weights and Weyl symmetry.
 The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
@@
 Representation theory of Lie algebras is of central importance for different areas of physics and mathematics.
-In physics Lie algebras are used for the description of symmetries of quantum and classical systems.
+In physics Lie algebras are used to describe symmetries of quantum and classical systems.
 Computational methods in representation theory have a long history \cite{belinfante1989survey}, there exist numerous software packages for computations related to Lie algebras \cite{simplie}, \cite{vanleeuwen1994lsp}, \cite{stembridge1995mps,coxweyl}, \cite{fischbacher2002ilp}, \cite{Fuchs:1996dd}.
@@
 The third problem is most computation-intensive.
-There are two different recurrent algorithms which are based on Weyl character formula and Freudenthal multiplicity formula.
-In this paper we analyze them.
-
-Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and study of  integrable systems.
-But infinite-dimensional algebras are much harder to study and number of available computer programs is much smaller.
+There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula.
+In this paper we analyze them both.
+
+Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and in a study of  integrable systems.
+But infinite-dimensional algebras are much harder to investigate and the number of available computer programs is much smaller in this case.
 
 Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras.
-They are constructed as the central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in the study of Wess-Zumino-Witten and coset models of conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
-
-The structure of affine Lie algebras allows to extend computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
+They are constructed as central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in a study of Wess-Zumino-Witten and coset models in conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
+
+The structure of affine Lie algebras allows to adapt for them computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
 The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
@@
 We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
-We describe the features and limitations of the package in present paper.
-We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physics.
+We describe the features and limitations of the package in the present paper.
+We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physical applications.
 
@@
 {\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
-In present paper we treat simple and semisimple Lie algebras.
-
-Maximal commutative subalgebra ({\it Cartan subalgebra}) of $\gf$ is denoted by $\hfg$.
+In the present paper we treat simple and semisimple Lie algebras.
+
+{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
 We denote the elements of basis of $\hfg$ by $H^{i}$.
@@
 \end{equation}
-Central extension leads to the appearance of additional term
+Central extension leads to the appearance of an additional term
 \begin{equation}
@@
 
-We do not treat twisted affine Lie algebras in present paper.
+We do not treat twisted affine Lie algebras in the present paper.
 
@@
 
-Let $\gf$ be finite-dimensional or affine Lie algebra.
+Let $\gf$ be a inite-dimensional or an affine Lie algebra.
 
@@
 \end{equation}
-Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms on vector space $V$ with the commutator as the bracket.
-
-For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by special choice of basis $\{v_{j}\}$ in $V$:
+Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
+
+For an arbitrary representation it is possible to diagonalize the operators corresponding to Cartan generators $H^{i}$ simultaneously by a special choice of basis $\{v_{j}\}$ in $V$:
 \begin{equation}
@@
 \end{equation}
-Eigenvalues $\nu^{i}_{j}$ of Cartan generators on element of basis $v_{j}$ determine weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Vector $v\in V$ is called weight vector of weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
-Weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
-Weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of weight subspace.
-
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on a weight vectors is
+Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
+Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
+The weight multiplicity $m_{\lambda}=\mathrm{mult}(\lambda)=\mathrm{dim} V_{\lambda}$ is the dimension of the weight subspace.
+
+The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
 \begin{equation}
@@
 \end{equation}
-Module structure can be encoded by the formal character of module
+Module structure can be encoded by the formal character of a module
 \begin{equation}
@@
 Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-Character can be specialized by taking its value on some element $\xi$ of $\hf$.
-
-Lie algebra is its own module. The action of generators is called adjoint and it is given by the bracket $ad_{X} Y=[X,Y]$. 
-{\it Roots} are weights of adjoint representation of $\gf$.
+A character can be specialized by taking its value on some element $\xi$ of $\hf$.
+
+Lie algebra is its own module with respect to a special kind of representation. The action that
+defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
+{\it Roots} are weights of the adjoint representation of $\gf$.
 They encode the commutation relations of algebra in the following way.
 Denote by $\Delta$ the set of roots.
-For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and generators $E^{\alpha}, E^{-\alpha}$ such that
+For each $\alpha\in \Delta$ there exist a root $-\alpha\in \Delta$ and the generators $E^{\alpha}, E^{-\alpha}$ such that
 \begin{align}
@@
 
-Given a root system $\Delta$ we can choose a set of positive roots.
+Given the root system $\Delta$ we can choose the set of positive roots.
 This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
@@
 
-A positive root is {\it simple} if it cannot be written as the sum of positive roots.
-The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis of $\hfg$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive.
-In case of finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to rank of the algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-By numbering simple roots with an index $i$ we introduce lexicographic ordering on the root system $\Delta$.
+A positive root is {\it simple} if it cannot be written as a sum of positive roots.
+The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
+In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
 Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
-It is also highest weight (See section \ref{sec:high-weight-modul}) of adjoint module.
-{\it Comarcs} are equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
-
-Although the full set of roots $\Delta$ is infinite for affine Lie algebra $\hat\gf$ the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+$\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
+{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+
+Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
 The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
-The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- highest root of the algebra $\go$.
-Note that root multiplicity $\mathrm{mult}(\alpha)$ for affine Lie algebra can be greater than one.
-
-Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called Borel subalgebra.
+The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
+Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
+
+Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
 
@@
 It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
-
-{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ which is a subset of set of simple roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{\Theta\}$ with the addition of highest root.
+{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
 
@@
 \end{equation}
-Root system and characters of representation are invariant with respect to the action of Weyl group. Root system can be reconstructed from the set of simple roots with the action of Weyl group.
+Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
 
@@
 
-Consider an action of element $s_{\alpha}s_{\alpha+\delta}$ of Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ simple root of underlying finite-dimensional Lie algebra $\gf$.
-Using the definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-So Weyl group can be presented as semidirect product of Weyl group $W_{\gf}$ of $\gf$ and translations corresponding to the roots of $\gf$.
-
-Weyl group element can be presented as the product of elementary reflections in multiple ways.
-Number of elementary reflections in shortest sequence representing element $w\in W_{\gf}$ is called {\it length} of $w$ and denoted $l(w)$.
-We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for parity of number of Weyl reflections generating $w$.
-
-Fundamental domain $\bar{C}$ for the action of Weyl group $W_{\gf}$ on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
-It is called {\it main Weyl chamber}.
+Consider an action of the element $s_{\alpha}s_{\alpha+\delta}$ of the Weyl group of affine Lie algebra  $\hat\gf$ for $\alpha$ being a simple root of the underlying finite-dimensional Lie algebra $\gf$.
+Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
+So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
+
+A Weyl group element can be presented as a product of elementary reflections in multiple ways.
+Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
+We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
+
+Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
+It is called a {\it main Weyl chamber}.
 
@@
 \end{equation}
-and can be used for compact description of Lie algebra commutation relations in Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
-
-The form \eqref{eq:9} induces the basis dual  to the simple
+and can be used for a compact description of Lie algebra commutation relations in the Chevalley basis \cite{humphreys1997introduction}, \cite{fulton1991representation}, \cite{bourbaki2002lie}.
+
+Form \eqref{eq:9} induces a basis dual  to the simple
 roots basis. It is called the {\it fundamental weights basis}. We denote
@@
 \end{equation}
-For finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
+For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
 For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \lambda_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of finite-dimensional Lie algebra $\gf$.
-
-{\it Weyl vector} is equal to the sum of fundamental weights $\rho=\sum_{i} \omega_{i}$. It is of importance for the construction of algebra modules.
+Other fundamental weights are equal to $\omega_i=a_i^v \lambda_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
+
+ The sum of fundamental weights $\rho=\sum_{i} \omega_{i}$ is called a {\it Weyl vector}. It is an important tool in representation theory.
 
@@
 
-We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates weight system of $V$, i.e.
+We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
 if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
 
-Highest weight module $V^{\mu}$ contains one highest weight $\mu$, all other weights are obtained by the subtraction of linear combination of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z}_{+}$.
+Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
 
 The most simple type of highest weight modules is the Verma module
-$M^{\mu}$ who's space can be defined as the space
+$M^{\mu}$. Its space can be defined as a module
 \begin{equation}
@@
 \end{equation}
-with respect to the multiplication in $U(\gf)$,
-where $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
+with respect to a multiplication in $U(\gf)$ and
+$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
 Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
-Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D_{\lambda}(\bff_{+})$.
-
-Weight multiplicities in Verma module can be found from the Weyl
+Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
+
+Weight multiplicities in Verma modules can be found by applying the Weyl
 character formula
@@
 and $\epsilon \left( w\right) :=\det \left( w\right)$ is equal to 
-the parity of number of Weyl reflections generating $w$.
+the parity of the sequence of Weyl reflections generating $w$.
 
@@
 Irreducible highest weight modules have no non-trivial submodules. 
-Weyl character formula for
+The Weyl character formula for
 irreducible highest weight modules is
@@
 Thus the character of an irreducible highest weight module can be
-seen as the combination of characters of Verma modules. ( This
+seen as a combination of characters of Verma modules. ( This
 fact is a consequence of the Bernstein-Gelfand-Gelfand resolution
@@
 
-Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by the representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
+Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
 \begin{equation*}
@@
 \end{equation*}
-Denote a formal element $R_{I}:=\prod_{\alpha \in \Delta
+Introduce a formal element $R_{I}:=\prod_{\alpha \in \Delta
 ^{+}\setminus \Delta _{\pf_{I}}^{+}}\left( 1-e^{-\alpha }\right)
-^{\mathrm{mult}(\alpha )}$. Then the character of generalized
+^{\mathrm{mult}(\alpha )}$. Then the character of a generalized
 Verma module can be written as
@@
 
-We can use Weyl character formula to obtain recurrent relation on weight multiplicities which can be used for calculations \cite{il2010folded,kulish4sfa}.
-
-For irreducible highest-weight modules recurrent relation has form
+We can use the Weyl character formula to obtain recurrent relations for weight multiplicities -- important tools for calculations \cite{il2010folded,kulish4sfa}.
+
+For irreducible highest-weight modules recurrent relations have the following form
 \begin{equation}
@@
 \end{equation}
-Formulae for Verma and generalized Verma modules differs only in second term on the right-hand side.
+Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
 In case of Verma module it is just $\delta_{\xi,\mu}$.
-For generalized Verma module summation in second term on the right-hand side \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
-
-Other recurrent formula can be obtained from the study of Casimir
+For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
+
+Other recurrent formula can be obtained from a study of Casimir
 elements action on irreducible highest weight modules
@@
 It is called the Freudenthal multiplicity formula.
-Note that it is applicable only to irreducible only to irreducible modules.
+Note that it is applicable only to irreducible modules.
 
@@
 $\af\subset \gf$. Simple roots $\beta_{i}$ of the subalgebra $\af$
-can be presented as linear combinations of algebra roots
+can be presented as linear combinations of $\gf$-algebra roots
 $\alpha_{j}$: $\beta_{i}=\sum_{j=1,\dots,r_{\gf}}k_{j}
@@
 
-Each $\gf$-module is also an $\af$-module, although
-$L^{\mu}_{\gf}$ is not irreducible as $\af$-module. It can be
-decomposed into the sum of irreducible $\af$-modules:
+Each irreducible $\gf$-module is also an $\af$-module, although
+$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
+It can be
+decomposed into a direct sum of irreducible $\af$-modules:
 \begin{equation}
@@
 \end{equation}
-Coefficients in this decomposition are called the branching
+Coefficients in such a decomposition are called branching
 coefficients.
 
-It is possible to calculate branching coefficients by the construction and repeated subtraction of characters of modules $L^{\nu}_{\af}$.
-This traditional approach has serious limitations especially in case of affine Lie algebras.
-We discuss them in the end of section \ref{sec:comp-algor}.
-
-Now we describe alternative approach which is based upon recurrent relation on branching coefficients. 
-But before we proceed to this recurrent relation we need several definitions.
-
-For a subalgebra $\af\subset \gf$ we introduce a subalgebra
+It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. (The characters were not involved yet!)
+This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
+
+Now we describe an alternative approach which is based on recurrent properties of branching coefficients. 
+But before we proceed to these recurrent relations we need several additional definitions.
+
+For a subalgebra $\af\subset \gf$ we introduce the subalgebra
 $\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
-orthogonal to $\af$,
+orthogonal to $\hf_{\af}$,
 \begin{equation*}
@@
 and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to $\af$,
+to roots of $\af$,
 \begin{eqnarray}
@@
 \end{eqnarray}
-Let $W_{\afb}$ be the subgroup of $W$ generated by the
+Let $W_{\afb}$ be a subgroup of $W$ generated by
 reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
-}}^{+}$. The subsystem $\Delta _{\afb}$ determines the
+}}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
 subalgebra $\afb$ with the Cartan subalgebra $\hf_{\af%
@@
 
-Cartan subalgebra can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
+The Cartan subalgebra $\frak{h}$ can be decomposed in the following way:  $\frak{h}=\frak{\frak{h}_{\af}}\oplus
 \frak{h}_{\afb}\oplus \frak{h}_{\perp }$
 
-We also introduce notation
+We also introduce the notations
 \begin{eqnarray}
@@
 \end{equation}
-The formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
+Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
 
@@
 Another particular case of this formula is connected with tensor
-product decomposition. Consider the tensor product of two
+product decompositions. Consider the tensor product of two
 irreducible $\gf$-modules $L^{\mu}\otimes L^{\nu}$. It is also a
@@
 equivalent to branching problem for the diagonal subalgebra
-$\gf\subset \gf\otimes \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
+$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
 
@@
 \lstinline{Head} \lstinline{finiteWeight}, its components are the
-coordinates of the weight in the orthogonal basis of Bourbaki 
+coordinates of the weight in the orthogonal Bourbaki  basis
 \cite{bourbaki2002lie}.
@@
 found in  online help of the package. The most important
-are the definitions of addition, multiplication by number and
+are definitions of addition, multiplication by a number and a
 scalar product (bilinear form) for weights. These definitions
@@
 Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}.
-For affine Lie algebra this and related functions return the list up to fixed grade.
+For an affine Lie algebra this and related functions return the list up to fixed grade.
 This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default.
@@
 
-It is possible to specify a weight of Lie algebra by its Dynkin label
+It is possible to specify a weight of a Lie algebra by its Dynkin labels
 \begin{lstlisting}
@@
 
-Elements of Weyl group are specified by the set of indices of reflections, so element  $w=s_{1}s_{2}s_{1}$ of Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
+Elements of Weyl group are specified by the set of indices of reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
 Then it can be applied to the weights:
@@
 This structure is a hash-table implemented with \lstinline{DownValues}.
-The keys are weights at the exponents and the values are corresponding multiplicities.
+The keys are weights at the exponents and the values are the  corresponding multiplicities.
 \lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
-creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of formal algebra $\mathcal{E}$.
-The operations of formal algebra $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by number or exponent of weight.
-There is also multiplication of formal elements but no division.
+creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$.
+The operations in $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight.
+There exists also a multiplication of formal elements but no division.
 \begin{lstlisting}[mathescape=true]
@@
 {\bf Affine.m} can be used to study different kinds of modules, i.e.
-Verma modules, irreducible modules and parabolic Verma modules .
+Verma modules, irreducible modules and parabolic Verma modules.
 We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$.
@@
 Set of singular weights can have Weyl symmetry.
-It can be symmetry with respect to Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
-Then it is possible to study only main Weyl chamber $C_{\af}$.
+It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
+Then it is possible to study only the main Weyl chamber $C_{\af}$.
 To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
-Here \lstinline{rs} is root system of Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is root system corresponding to Weyl group $W_{\af}$ which is the symmetry of the set of singular weights.
+Here \lstinline{rs} is the root system of the Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights.
 Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
@@
 
-As we already stated properties of the module are encoded by its singular element.
-Function \lstinline{singularElement[m_module]} returns singular element of module as \lstinline{formalElement} datastructure.
-Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by function \lstinline{character[m_module]}.
-Direct sum of modules is module and we use natural notation
+As we already stated properties of a module are encoded by its singular element.
+Function \lstinline{singularElement[m_module]} returns singular element of a module as \lstinline{formalElement} datastructure.
+Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}.
+Direct sum of modules is a module and we use natural notation
 \begin{lstlisting}[mathescape=true]
@@
 
-Tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of present paper.
+The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
 \begin{lstlisting}[mathescape=true]
@@
 \begin{enumerate}
-\item Create the list of weights in main Weyl chamber by subtraction of all possible combinations of simple roots from the highest weight (e.g.
+\item Create the list of weights in the main Weyl chamber by subtracting all possible combinations of simple roots from the highest weight (e.g.
 for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
-\item Sort the list of weights by their product with Weyl vector.
-\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use Weyl symmetry.
+\item Sort the list of weights by their product with the Weyl vector.
+\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use the Weyl symmetry.
 \end{enumerate}
-The difference in performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
-For  Weyl formula-based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in Weyl group (if we are far from the boundary of representation diagram).
-When Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
-So Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
-Note that Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
-
-We have made some experiments with our implementations of Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts dependence of computation time on number of weights in module.
+The difference in the performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
+For  the Weyl formula based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
+When the Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
+So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
+Note that the Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
+
+We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
 
@@
   }
-  \caption{Running time of algorithms based on Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
+  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
 \label{fig:freudenthal-racah-times}
@@
 
-In the calculation of branching coefficients use of Freudenthal formula requires full construction of formal characters of algebra representation and all the representations of subalgebra.
-It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebra.
-
-Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L} proceeds as follows:
-It contains the following steps:
+In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of formal characters of an algebra module and all the representations of a subalgebra.
+It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebras.
+
+Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L}  contains the following steps:
 
@@
 
-\item  Select all positive roots $\alpha \in \Delta ^{+}$ orthogonal
+\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal
 to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
@@
 
-\item  Calculate the anomalous branching coefficients using the
+\item  Calculate the anomalous branching coefficients using 
 recurrent relation (\ref{recurrent-rel}) and select among them those
@@
 Consider the regular embedding $B_{2}\subset B_{4}$.
-In this case fan consists of 24 elements.
-In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of subalgebra $B_{2}$.
-Full set of singular weights consists of 384 elements.
-Required subset contains at most 48 elements.
-So time of the construction of required subset is negligible if the number of branching coefficients is greater than that.
-We may estimate the total number of required operations for the computation of branching coefficients as the product of number of elements in main Weyl chamber of subalgebra with non-zero branching coefficients and number of elements in fan.
-In the case of direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than square of number of elements in main Weyl chamber of subalgebra with non-zero branching coefficients.
-
-To further illustrate this performance issue we include the Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
+In this case the fan consists of 24 elements.
+In order to decompose $B_{4}$ module we need to construct the subset of singular weights of the module which projects to the main Weyl chamber of the subalgebra $B_{2}$.
+The full set of singular weights consists of 384 elements.
+The required subset contains at most 48 elements.
+So the time for the construction of this required subset is negligible if the number of branching coefficients is greater than that.
+We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients and the number of elements in the fan.
+In the case of a direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than the square of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients.
+
+To further illustrate this performance issue we include Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
 
@@
   }
-  \caption{Running time of algorithms based on Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
+  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
   \label{fig:branching}
@@
 Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
-For example, we can consider spin of composite system such as atom.
-Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of Lie algebra $\gf$ with $\gf$-invariant Hamiltonian $H$, describing nearest-neighbour spin-spin interaction.
-In order to solve such system, i.e.
-find eigenstates of Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
-
-For fundamental representations of simple Lie algebras it is sometimes possible to get analytic result for the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
-Our code give numerical values and can be used to check this analytic results.
-
-Consider tensor power of $B_{2}$ first fundamental representations $\left(L^{[1,0]}\right)^{\otimes 4}$.
-Decomposition coefficients are just branching coefficients for tensor product module to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$.
-So following code calculates these coefficients:
+For example, we can consider the spin of a composite system such as an atom.
+Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
+In order to solve such a system, i.e.
+to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
+
+For fundamental representations of simple Lie algebras it is sometimes possible to get an analytic result describing the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
+Our code provides numerical values and can be used to check this analytic results.
+
+Consider a tensor power of $B_{2}$ the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$. Decomposition coefficients are just the branching
+ coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
 \begin{lstlisting}[mathescape=true]
@@
 \end{lstlisting}
-It produces list of highest weights and tensor product decomposition coefficients:
+It produces a list of highest weights and tensor product decomposition coefficients:
 \begin{lstlisting}
@@
 
-Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
+Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
 
@@
 
-We illustrate generalized BGG-resolution with the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
+We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
 \begin{equation}
@@
 \end{equation}
-Character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
-Characters in upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in lower row with negative.
+The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of the generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
+Characters in the upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in the lower row -- with negative.
 
@@
   }
-  \caption{Character of irreducible $G_{2}$-module $L^{[1,1]}$}
+  \caption{Character of the irreducible $G_{2}$-module $L^{[1,1]}$}
   \label{branching-bgg}
@@
   }
-  \caption{Character of $G_{2}$ generalized Verma modules appearing in decomposition of $L^{[1,1]}$.
-Parabolic Verma modules in upper row appear in decomposition with positive sign, in lower row -- with negative.}
+  \caption{Characters of $G_{2}$ generalized Verma modules appearing in the decomposition of $L^{[1,1]}$.
+Parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
   \label{g2-pverma}
@@
 
-String functions can be used to present the formal character of affine Lie algebra highest weight representation.
+String functions can be used to present formal characters of affine Lie algebra highest weight representation.
 They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.
@@
 {\bf Affine.m} produces power series decomposition for string functions.
-Consider affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ highest weight module $L^{(1,0,0)}$.
-To get string functions we can use the code:
+Consider an affine Lie algebra $\hat{sl(3)}=\hat A_{2}$ and its highest weight module $L^{(1,0,0)}$.
+To get the string functions we can use the code:
 \begin{lstlisting}[mathescape=true]
@@
 \end{lstlisting}
-Similarly for affine Lie algebra $\hat G_{2}$ we get
+Similarly for the affine Lie algebra $\hat G_{2}$ we get
 \begin{lstlisting}[mathescape=true]
@@
 
-More complex models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$. These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
-
-Branching functions of the embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).
-
-As first example we show computation of branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to tenth grade:
+It is believed that most rational models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$.
+These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
+
+Branching functions for an embedding $\af\subset\gf$ are the partition functions of CFT on the torus (see \cite{difrancesco1997cft}).
+
+As a first example we show how to construct branching functions for the embedding $\hat A_{1}\to \hat B_{2}$ up to the tenth grade:
 \begin{lstlisting}[mathescape=true]
@@
 
-Another example is computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
+Another example demonstrates the computation of branching functions for the regular embedding $\hat B_{2}\subset \hat C_{3}$:
 \begin{lstlisting}[mathescape=true]
@@
 We have presented the package {\bf Affine.m} for computations in representation theory of finite-dimensional and affine Lie algebras.
-It can be used to study Weyl groups, roots systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
-In present paper we have also discussed main ideas used for implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
-
-We have demonstrated that recurrent approach based upon Weyl character formula is not only useful for calculations but also allows to see connection with (generalized) Bernstein-Bernstein-Gelfand resolution.
+It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
+In the present paper we have also discussed main ideas used for an implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
+
+We have demonstrated that recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
 
@@
 
-In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decomposition.
+In future versions of our software we are going to treat twisted affine Lie algebras, extended affine Lie algebras and provide more direct support for tensor product decompositions.
 

### 2011-08-13 tests/debug2.m

@@ -219,6 +219,953 @@ fcc3=Affine`Private`fullCharacter[im]
 
 Export["affineCharacter4.png",Graphics[(Text[fcc3[#],{#[grade],#[finitePart][[2]][[1]]}])&/@fcc3[weights]]]
 
+
+a2a=makeAffineExtension[makeSimpleRootSystem[A,2]];
+
+im=makeIrreducibleModule[a2a][
+
+b2a=makeAffineExtension[makeSimpleRootSystem[B,2]];
+im=makeIrreducibleModule[b2a][1,0,0];
+se=singularElement[im];
+
+Export["b2sing.pdf",Graphics[Text[se[#],{grade[#]*10+#[finitePart][standardBase][[1]],#[finitePart][standardBase][[2]]}]&/@ Select[se[weights],grade[#]>-5&],{Frame->True,GridLines->Automatic}]]
+
+
+
+a1a1=makeAffineExtension[CirclePlus[makeSimpleRootSystem[A,1],makeSimpleRootSystem[A,1]]]
+
+imaa=makeIrreducibleModule[a1a1][1,0,0];
+se=singularElement[imaa];
+
+Export["a1a1sing.pdf",Graphics[Text[se[#],{grade[#]*10+#[finitePart][standardBase][[1]],#[finitePart][standardBase][[2]]}]&/@ Select[se[weights],grade[#]>-8&],{Frame->True,GridLines->Automatic}]]
+
+b2a
+
+dynkinLabels[b2a] @ (weylGroupElement[b2a][1,2,1] @ weight[b2a][1,1,1])
+
+a1=makeSimpleRootSystem[A,1]
+
+Out[65]= finiteRootSystem[1, 1, {finiteWeight[1, {1}]}]
+
+imm=CircleTimes[makeIrreducibleModule[a1][5],makeIrreducibleModule[a1][3]]
+
+Export["tensor-product.pdf",textPlot[imm,{Axes->True}]]
+
+g2a=makeAffineExtension[makeSimpleRootSystem[G,2]]
+
+makeAffineExtension[makeSimpleRootSystem[G,2]]
+
+g2=makeSimpleRootSystem[G,2]
+
+partialOrbit[g2][{weight[g2][1,-1]}]
+
+g2[simpleRoots]
+
+
+
[…]

### 2011-08-13 tests/tests.m

@@ -122,7 +122,7 @@ Expect["Weyl reflection s1 s2 s1 in algebra B2",True,
 
 Expect["Fundamental weights for B2", True, {makeFiniteWeight[{1,0}],makeFiniteWeight[{1/2,1/2}]}===fundamentalWeights[makeSimpleRootSystem[B,2]]]
 
-Expect["Fundamental weights for A1", True, {makeFiniteWeight[{1/2}]}===fundamentalWeights[makeSimpleRootSystem[A,1]]]
+Expect["Fundamental weights for A1", True, {makeFiniteWeight[{1/2,-1/2}]}===fundamentalWeights[makeSimpleRootSystem[A,1]]]
 
 Expect["Fundamental weights for A2", True, {makeFiniteWeight[{2/3,-1/3,-1/3}],makeFiniteWeight[{1/3,1/3,-2/3}]}===fundamentalWeights[makeSimpleRootSystem[A,2]]]
 
@@ -157,7 +157,7 @@ Expect["Positive roots of B2",True,
 
 Expect["Dimension",5, dimension[{makeFiniteWeight[{1,1}]}][makeFiniteWeight[{2,2}]]]
 
-Expect["Dimension",5, dimension[makeSimpleRootSystem[A,1]][makeFiniteWeight[{2}]]]
+Expect["Dimension",5, dimension[makeSimpleRootSystem[A,1]][makeFiniteWeight[{2,-2}]]]
 
 Module[{b2=makeSimpleRootSystem[B,2]},
        Expect["Weights of [2,1] module of B2",True, Union[weightSystem[b2][makeFiniteWeight[{2,1}]]]===
@@ -180,10 +180,10 @@ Module[{b2=makeSimpleRootSystem[B,2],fm,rm},
 
 Expect["Highest root for B2",makeFiniteWeight[{1, 1}],highestRoot[makeSimpleRootSystem[B,2]]]
 
-Expect["simpleRoots of affine Lie algebra A1",True, OverHat[Subscript[A,1]][simpleRoot][1]===makeAffineWeight[{1},0,0]]
+Expect["simpleRoots of affine Lie algebra A1",True, OverHat[Subscript[A,1]][simpleRoot][1]===makeAffineWeight[{1,-1},0,0]]
 
 Module[{b2a=makeAffineExtension[makeSimpleRootSystem[B,2]]},
-       b2a[gradeLimit]=1;
+       b2a[gradeLimit]=0;
[…]

### 2011-08-22 doc/paper.tex
Demo colored, some optimisation of affine.m, misprints in paper

@@
 For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \lambda_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
+Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
 
@@
 Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
+%% !!! \Delta_{p}?!
 \begin{equation*}
@@
 
-It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. (The characters were not involved yet!)
+It is possible to calculate branching coefficients by constructing and successively  subtracting the submodules $L^{\nu}_{\af}$. 
 This traditional approach has serious limitations especially in case of affine Lie algebras. We discuss them in the end of section \ref{sec:comp-algor}.
@@
 
+%%!!! Define P^+
 For $\mu \in P^{+}$ consider the linked weights $\left\{ \left(
@@
 Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
-If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in W_{\af}$.
+If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
 
@@
 GraphicsRow[textPlot/@{im,vm,pm}]
-$\includegraphics[width=130mm]{figures/irrep-verma-pverma.pdf}$
+$\includegraphics[width=130mm]{irrep-verma-pverma.pdf}$
 \end{lstlisting}
@@
 textPlot[im1$\oplus$ im2]
-$\includegraphics[width=60mm]{figures/irrep-sum.pdf}$
+$\includegraphics[width=60mm]{irrep-sum.pdf}$
 \end{lstlisting}
@@
 textPlot[makeIrreducibleModule[$A_{1}$][5]$\otimes$ makeIrreducibleModule[$A_{1}$][3]];
-$\includegraphics[width=60mm]{figures/tensor-product.pdf}$
+$\includegraphics[width=60mm]{tensor-product.pdf}$
 \end{lstlisting}
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{figures/timing.pdf}
+    \includegraphics[width=80mm]{timing.pdf}
   }
@@
   \noindent\centering{
-   \includegraphics[width=100mm]{figures/branching-timing.pdf}
+   \includegraphics[width=100mm]{branching-timing.pdf}
   }
@@
   \noindent\centering{
-    \includegraphics[width=80mm]{figures/G2-irrep.pdf}
+    \includegraphics[width=80mm]{G2-irrep.pdf}
   }
@@
   \noindent\centering{
-    \includegraphics[width=150mm]{figures/G2-pverma.pdf}
+    \includegraphics[width=150mm]{G2-pverma.pdf}
   }

### 2011-08-22 src/affine.m

@@ -381,7 +381,7 @@ finiteWeight/:0*y_finiteWeight:=makeFiniteWeight[0*y[standardBase]];
 
 finiteWeight/:x_?NumericQ*y_finiteWeight:=makeFiniteWeight[x*y[standardBase]];
 
-affineWeight/:x_affineWeight[dimension]:=x[[1]];
+ affineWeight/:x_affineWeight[dimension]:=x[[1]];
 affineWeight/:x_affineWeight[finitePart]:=x[[2]];
 affineWeight/:x_affineWeight[level]:=x[[3]];
 affineWeight/:x_affineWeight[grade]:=x[[4]];
@@ -885,13 +885,33 @@ weightSystem[m_module]:=Module[{minusRoots, checkChamber, rs=rootSystem[m],res,r
 				   x]],m[[2]][weights],#=!={}&]];
 			       makeFormalElement[res,Table[1,{Length[res]}]]];
 *)
+
+
 partialCharacter[m_module]:=
-    Module[{rs=rootSystem[m],subs=subSystem[m],toFC,rh,mults,aw,wgs,fan,tmp,gamma0},
+    Module[{rs=rootSystem[m],subs=subSystem[m],toFC,rh,mults,aw,wgs,fan,tmp,gamma0,fw},
 	   rh=rho[rs];
 	   fan=makeFormalElement @@ Transpose[Map[{rh-#[[1]],#[[2]]}&,Rest[orbitWithEps[rs][rh]]]];
-(*	   fan=singularElement[rs][zeroWeight[rs]];
-	   gamma0=Sort[fan[weights],#1.rh>#2.rh&][[1]];
-	   fan=fan*Exp[-gamma0];*)
+	   If [subs=!=emptyRootSystem[],
+	       toFC=toFundamentalChamber[subs],
+	       toFC=#&;
+	      ];
+	   wgs=Sort[weightSystem[m][weights],#1.rh>#2.rh&];
+	   aw=singularElement[m];
+	   mults=makeHashtable[{},{}];
+	   insideQ=IntegerQ[mults[toFC[#]]]&;
+	   fw=Sort[fan[weights],grade[#1]<grade[#2]&];
+	   Scan[Function[v,
+			 mults[v]=
+			 Plus @@ Map[ If [insideQ[v+#], -fan[#]*mults[toFC[v+#]], 0]&, TakeWhile[fw,grade[#]+grade[v]<=0&]];
[…]

### 2011-08-29 doc/paper.tex
Paper.nb is rewritten

--- 2011-08-13 doc/paper.tex
@@
 \end{lstlisting}
+%% The problem is here
 
@@
 \begin{lstlisting}
-  weight[b2][1,2,3] == makeFiniteWeight[{2, 1}]
+  weight[b2][1,2] == makeFiniteWeight[{2, 1}]
 \end{lstlisting}

### 2011-08-29 src/affine.m

@@ -454,7 +454,7 @@ finiteRootSystem/:CirclePlus[x_finiteRootSystem,y_finiteRootSystem]:=makeFiniteR
 
 affineRootSystem/:CirclePlus[x_affineRootSystem,y_affineRootSystem]:=makeAffineExtension[CirclePlus[x[finiteRootSystem],y[finiteRootSystem]]];
 
-(*makeSimpleRootSystem[A,1]:=makeFiniteRootSystem[{{1}}];*)
+makeSimpleRootSystem[A,1]:=makeFiniteRootSystem[{{1}}];
 makeSimpleRootSystem[A,r_Integer]:=makeFiniteRootSystem[makeFiniteWeight /@ Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,r},{j,1,r+1}]];
 makeSimpleRootSystem[B,rank_Integer]:=makeFiniteRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],1]]];
 makeSimpleRootSystem[C,rank_Integer]:=makeFiniteRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Table[0,{rank-1}],2]]];

### 2012-06-11 src/affine.m
Added notes from CPC, minor change in code.

@@ -939,10 +939,19 @@ directSum[ms__module]:=makeModule[rootSystem[{ms}[[1]]]][Plus @@ (singularElemen
 CirclePlus[ms__module]=directSum[ms];
 
 simpleBranching[m_module,subs_?rootSystemQ]:=
-    Module[{mults,pmults,rh=rho[subs],res,wgs},
+    Module[{mults,pmults,rh=rho[subs],res,wgs,rs=rootSystem[m]},
 	   mults=character[m];
 	   Scan[(mults[hashtable][#]=mults[toFundamentalChamber[rs][#]])&,Flatten[orbit[rs][mults[weights]]]];
 	   pmults=projection[subs][mults];
+	   res=makeFormalElement[makeHashtable[{},{}]];
+	   wgs=Select[Sort[pmults[weights],#1.rh>#2.rh&],mainChamberQ[subs]];
+	   Scan[(res[hashtable][#]=pmults[#];pmults=pmults - pmults[#]*freudenthalMultiplicities[subs][#])&, wgs];
+	   res];
+
+
+simpleBranching[fe_formalElement,subs_?rootSystemQ]:=
+    Module[{pmults,rh=rho[subs],res,wgs},
+	   pmults=projection[subs][fe];
 	   res=makeFormalElement[makeHashtable[{},{}]];
 	   wgs=Select[Sort[pmults[weights],#1.rh>#2.rh&],mainChamberQ[subs]];
 	   Scan[(res[hashtable][#]=pmults[#];pmults=pmults - pmults[#]*freudenthalMultiplicities[subs][#])&, wgs];

### 2012-06-11 doc/paper.tex
Added modified bibtex style to fix the references. Some grammar changes in paper text.

@@
 %% Text of abstract
-In this paper we present {\bf Affine.m} -- program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
-Algorithms are based on the properties of weights and Weyl symmetry.
+In this paper we present {\bf Affine.m} -- a program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
+The algorithms are based on the properties of weights and Weyl symmetry.
 The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
@@
 Representations of affine Lie algebras appear in string theories and two-dimensional conformal field theory used for the description of critical phenomena in two-dimensional systems.
-Also Lie symmetries play major role in study of quantum integrable systems.
+Also Lie symmetries play major role in a study of quantum integrable systems.
    \\
@@
 There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
-The third problem is most computation-intensive.
+The third problem is the most computation-intensive.
 There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula.
@@
 
-The structure of affine Lie algebras allows to adapt for them computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
+The structure of affine Lie algebras allows to adapt for them the computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
 The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
@@
 \ref{sec:comp-algor}).
-Next section consists of physically interesting examples (Sec.
+The next section consists of physically interesting examples (Sec.
 \ref{sec:examples}).
@@
 
-{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called {\it Lie bracket}.
+{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called a {\it Lie bracket}.
 If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
@@
 
-{\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
+A {\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
 We denote the elements of basis of $\hfg$ by $H^{i}$.
 
-Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
+The Killing form on $\gf$ gives a non-degenerate bilinear form $(\cdot,\cdot)$ on $\hfg$ which can be used to identify $\hfg$ with the subspace of the dual space $\hfg^{*}$ of linear functionals on $\hfg$.
 {\it Weights} are the elements of $\hfg^{*}$ and are denoted by Greek letters $\mu,\nu, \omega, \lambda\dots$
 
-Special choice of basis gives compact description of commutation relations (\ref{eq:1}).
+A special choice of basis gives compact description of commutation relations (\ref{eq:1}).
 This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
 
-{\it Loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
+The {\it loop algebra} $L\gf=\gf\otimes \mathbb{C}[t,t^{-1}]$, corresponding to semisimple Lie algebra $\gf$, has commutation relations
 \begin{equation}
@@
 \end{lstlisting}
-There are constructors for root systems of simple finite-dimensional Lie algebras:
+There are constructors for the root systems of simple finite-dimensional Lie algebras:
 \begin{lstlisting}
@@
 
-The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
+The tensor product is also implemented but only for the finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
 \begin{lstlisting}[mathescape=true]
@@
 \item Create the list of weights in the main Weyl chamber by subtracting all possible combinations of simple roots from the highest weight (e.g.
-for finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
+for a finite-dimensional algebra subtract $\alpha_{1}$ from $\mu$ while inside $\bar C$, then subtract $\alpha_{2}$ from all the weights already obtained etc).
 \item Sort the list of weights by their product with the Weyl vector.
@@
 It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
-In the present paper we have also discussed main ideas used for an implementation of the package and described most important notions of representation theory required to use {\bf Affine.m}.
+In the present paper we have also discussed main ideas used for an implementation of the package and described the most important notions of representation theory required to use {\bf Affine.m}.
 
@@
 \bibliography{bibliography}
-\bibliographystyle{phcpc}
-%\bibliographystyle{model1-num-names}
+%\bibliographystyle{utphys}
+%\bibliographystyle{h-elsevier-hyperref}
+\bibliographystyle{model1-num-names-arxiv-modified}
 

### 2012-06-14 doc/paper.tex
Minor changes

@@
 %% Text of abstract
-In this paper we present {\bf Affine.m} -- a program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
+In this paper we present {\bf Affine.m} -- a program for computations in representation theory of finite-dimensional and affine Lie algebras and describe the implemented algorithms.
 The algorithms are based on the properties of weights and Weyl symmetry.
@@
 These problems have numerous applications in physics and we provide some examples of these applications.
-The program is implemented in popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
+The program is implemented in the popular computer algebra system {\it Mathematica} and works with finite-dimensional and affine Lie algebras.
 
@@
   %Describe any restrictions on the complexity of the problem here.
-Computational complexity grows fast  with the rank of algebra, so computations for algebra of rank greater than 8 are non practical.
+Computational complexity grows fast  with the rank of an algebra, so computations for algebras of ranks greater than 8 are not practical.
    \\
@@
   %Describe any unusual features of the program/problem here.
-We offer the possibility to use traditional mathematical notation for objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in {\it Mathematica} notebook interface.
+We offer the possibility to use a traditional mathematical notation for the objects in representation theory of Lie algebras in computations if {\bf Affine.m} is used in the {\it Mathematica} notebook interface.
    \\
@@
   %Give an indication of the typical running time here.
-From seconds to days depending on rank of algebra and complexity of representations.
+From seconds to days depending on the rank of an algebra and the complexity of a representation.
    \\
@@
 \begin{enumerate}
-\item Construction of root system which determine the properties of Lie algebra including its commutation relations.
+\item Construction of a root system which determines the properties of Lie algebra including its commutation relations.
 \item Weyl group traversal which is important due to Weyl symmetry of root system and characters of representations.

### 2012-06-16 doc/paper.tex
Changes in grammar

@@
 
-Affine Lie algebras \cite{kac1990idl} constitute important and tractable class of infinite-dimensional Lie algebras.
+Affine Lie algebras \cite{kac1990idl} constitute an important and tractable class of infinite-dimensional Lie algebras.
 They are constructed as central extensions of loop algebras of (semi-simple) finite-dimensional Lie algebras and appear naturally in a study of Wess-Zumino-Witten and coset models in conformal field theory \cite{Walton:1999xc}, \cite{difrancesco1997cft}, \cite{Goddard198588}, \cite{Dunbar:1992gh}.
@@
 We describe the features and limitations of the package in the present paper.
-We also provide representation-theoretical background of implemented algorithms and present examples of computations relevant to physical applications.
+We also provide a representation-theoretical background of the implemented algorithms and present the examples of computations relevant to physical applications.
 
@@
 \ref{sec:theor-backgr}).
-Then we describe datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec.
-\ref{sec:core-datastructures}) and discuss implemented algorithms (Sec.
+Then we describe the datastructures of {\bf Affine.m} used to present different objects related to Lie algebras and representations (Sec.
+\ref{sec:core-datastructures}) and discuss the implemented algorithms (Sec.
 \ref{sec:comp-algor}).
@@
 
-{\it Lie algebra} $\gf$ is a vector space with bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called a {\it Lie bracket}.
-If we choose the basis $X_{i}$ in $\gf$ we can specify commutation relations by the {\it structure constants} $C_{ijk}$:
+A {\it Lie algebra} $\gf$ is a vector space with a bilinear operation $[\cdot,\cdot]:\gf\otimes\gf\to \gf$, which is called a {\it Lie bracket}.
+If we choose a basis $X_{i}$ in $\gf$ we can specify the commutation relations by the {\it structure constants} $C_{ijk}$:
 \begin{equation}
@@
 \end{equation}
-Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to commutator.
-{\it Semisimple} Lie algebra is a direct sum of simple Lie algebras.
+A Lie algebra is {\it simple} if it contains no non-trivial ideals with respect to a commutator.
+A {\it semisimple} Lie algebra is a direct sum of simple Lie algebras.
 In the present paper we treat simple and semisimple Lie algebras.
@@
 A {\it Cartan subalgebra}  $\hfg$ is a nilpotent subalgebra of  $\gf$ that coincides with its normalizer. 
-We denote the elements of basis of $\hfg$ by $H^{i}$.
+We denote the elements of a basis of $\hfg$ by $H^{i}$.
 
@@
 
-A special choice of basis gives compact description of commutation relations (\ref{eq:1}).
+A special choice of a basis gives a compact description of the commutation relations (\ref{eq:1}).
 This basis can be encoded by the root system which is discussed in Section \ref{sec:weights-roots} (See also \cite{humphreys1997introduction,humphreys1992reflection}).
@@
 
-Let $\gf$ be a inite-dimensional or an affine Lie algebra.
+Let $\gf$ be a finite-dimensional or an affine Lie algebra.
 
@@
 \end{equation}
-Representation of algebra $\gf$ on a vector space $V$ is the homomorphism $\gf\to gl(V)$ from $\gf$ to Lie algebra of endomorphisms of the  vector space $V$ with the commutator as a bracket.
+A representation of an algebra $\gf$ on a vector space $V$ is a homomorphism $\gf\to gl(V)$ from $\gf$ to a Lie algebra of endomorphisms of the  vector space $V$ with the commutator as the bracket.
 
@@
 \end{equation}
-Eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
-Vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
+The eigenvalues $\nu^{i}_{j}$ of Cartan generators on an element of basis $v_{j}$ determine a weight $\nu_{j}\in \hfg^{*}$ such that $\nu_{j}(H^{i})=\nu_{j}^{i}$.
+A vector $v\in V$ is called the weight vector of the weight $\lambda$ if $H v=\lambda_{j}(H)v,\; \forall H\in \hf$.
 The  weight subspace consists of all weight vectors $V_{\lambda}=\{v\in V: H v=\lambda_{j}(H)v,\; \forall H\in \hf\}$.
@@
 
-The structure of module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
+The structure of a module is determined by the set of weights since the action of generators $E^{\alpha}$ on weight vectors is
 \begin{equation}
@@
 \end{equation}
-Module structure can be encoded by the formal character of a module
+The module structure can be encoded by the formal character of the module
 \begin{equation}
@@
 \end{equation}
-Character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+A character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
 A character can be specialized by taking its value on some element $\xi$ of $\hf$.
 
-Lie algebra is its own module with respect to a special kind of representation. The action that
-defines this representation is called adjoint and is given by the bracket $ad_{X} Y=[X,Y]$. 
+Any Lie algebra is its own module with respect to a special kind of representation. The action that
+defines this representation is called {\it adjoint} and is given by the bracket $ad_{X} Y=[X,Y]$. 
 {\it Roots} are weights of the adjoint representation of $\gf$.
@@
 This is a subset  $\Delta^{+}\subset \Delta$ such that for each root $\alpha\in\Delta$ exactly one of the roots $\alpha, -\alpha$ is contained in $\Delta^{+}$ and for any two distinct positive roots $\alpha, \beta\in \Delta^{+}$ such that $\alpha+\beta\in \Delta$ their sum is also positive $\alpha+\beta\in\Delta^{+}$.
-Elements of $-\Delta^{+}$ are called negative roots.
+The elements of $-\Delta^{+}$ are called negative roots.
 
@@
 In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
-By numbering simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
-Highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, coefficients $a_i$ are called {\it marks}.
+Enumerating simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
+The highest root with respect to this ordering is denoted by  $\theta=\sum_{i=1,\dots,r} a_i \alpha_i$, the coefficients $a_i$ are called {\it marks}.
 $\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
@@
 
-Although for affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
+Although for an affine Lie algebra $\hat\gf$ the set of roots $\Delta$ is infinite the set of simple roots $\Phi$ is finite and its elements are denoted by $\alpha_{0},\dots \alpha_{r}$ where $r=\mathrm{rank}(\gf)$.
 The roots $\alpha_1,\dots, \alpha_r$ are the roots of the underlying finite-dimensional Lie algebra $\go$.
-The root $\alpha_0=\delta-\theta$ is the difference of {\it imaginary root} $\delta$ and $\theta$ -- the highest root of the algebra $\go$.
+The root $\alpha_0=\delta-\theta$ is the difference of the {\it imaginary root} $\delta$ and the highest root  $\theta$ of the algebra $\go$.
 Note that root multiplicity $\mathrm{mult}(\alpha)$ for an affine Lie algebra root can be greater than one.
 
-Subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called the Borel subalgebra.
-
-{\it Parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+A subalgebra  $\bff_{+}\subset \gf$ spanned by the generators $H^{i}, E^{\alpha}$ for positive roots $\alpha\in \Delta^{+}$ is called a {\it Borel subalgebra}.
+
+A {\it parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
 It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
-{\it Regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
+A {\it regular subalgebra} $\af\subset\gf$ is determined by the root system $\Delta_{\af}$ with the set of simple roots $\{\beta_{i}, i=1,\dots,r_{\af}\}$ being a subset of the set of roots $\{\alpha_{1},\dots,\alpha_{r}\}\cup \{-\theta\}$ .
 
@@
 \end{equation}
-Root system and characters of representation are invariant with respect to the Weyl group  action. Root system can be reconstructed from the set of simple roots by the Weyl group transformations.
+Root system and characters of representation are invariant with respect to the Weyl group  action. A root system can be reconstructed from the set of simple roots by the Weyl group transformations.
 
@@
 Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-So the Weyl group can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to roots of $\gf$.
+So the Weyl group $W_{\gfh}$ can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to the roots of $\gf$.
 
 A Weyl group element can be presented as a product of elementary reflections in multiple ways.
-Number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
+The number of elementary reflections in the shortest sequence representing an element $w\in W_{\gf}$ is called the {\it length} of $w$ and is denoted by $l(w)$.
 We also use the notation $\epsilon(w)=(-1)^{l(w)}$ for the parity of the number of Weyl reflections generating $w$.
 
-Fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
-It is called a {\it main Weyl chamber}.
-
-The {\it Cartan matrix} $A$ is defined by products of simple roots
+A fundamental domain $\bar{C}$ for the Weyl group $W_{\gf}$ action  on $\hfg^{*}$ is determined by the requirement $\xi\in \bar{C}\Leftrightarrow (\xi,\alpha_{i})\geq 0$ for all simple roots $\alpha_{i}$.
+It is called the {\it main Weyl chamber}.
+
+A {\it Cartan matrix} $A$ is defined by products of simple roots
 \begin{equation}
@@
 
-Form \eqref{eq:9} induces a basis dual  to the simple
+The form \eqref{eq:9} induces a basis dual  to the simple
 roots basis. It is called the {\it fundamental weights basis}. We denote
@@
 For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
-For affine Lie algebra we have additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
-Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is the fundamental weight of the finite-dimensional Lie algebra $\gf$.
+For affine Lie algebra we have an additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is a fundamental weight of the finite-dimensional Lie algebra $\gf$.
 
@@
 
-Highest weight module $V^{\mu}$ contains a single highest weight $\mu$, all the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
+A highest weight module $V^{\mu}$ contains a single highest weight $\mu$,  the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
 
@@
 $\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
-Here $\bff_{+}$ is Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
+Here $\bff_{+}$ is the Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
 Elements of $\gf$ act from the left and we should commute all the elements of $\bff_{+}$ to the right, so that they can act on the space $D^{\lambda}(\bff_{+})$.
 
-Weight multiplicities in Verma modules can be found by applying the Weyl
+Weight multiplicities in Verma modules can be found using the Weyl
 character formula
@@
 
-Verma module $M^{\mu}$ has the unique maximal submodule and the
+A Verma module $M^{\mu}$ has the unique maximal submodule and the
 unique nontrivial simple quotient $L^{\mu}$ which is an
@@
 Irreducible highest weight modules have no non-trivial submodules. 
-The Weyl character formula for
-irreducible highest weight modules is
+The Weyl character formula for an irreducible highest weight module $L^{\mu}$ is
 \begin{equation}
@@
 
-Construction of generalized Verma modules is analogous to (\ref{eq:17}), but representation of Borel subalgebra is substituted by a representation of parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
-%% !!! \Delta_{p}?!
+Construction of a generalized Verma module is analogous to (\ref{eq:17}), but the representation of the Borel subalgebra is substituted by a representation of a parabolic subalgebra $\pf_{I}\supset \bff_{+}$ generated by some subset $\{\alpha_{I}\}$ of simple roots $I\subset \{1,\dots, r\}$:
 \begin{equation*}
@@
 
-For irreducible highest-weight modules recurrent relations have the following form
+For irreducible highest-weight modules the recurrent relation has the following form
 \begin{equation}
@@
 In case of Verma module it is just $\delta_{\xi,\mu}$.
-For generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by reflections corresponding to roots $\{\alpha_{I}\}$.
-
-Other recurrent formula can be obtained from a study of Casimir
+For a generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by the reflections corresponding to the roots $\{\alpha_{I}\}$.
+
+Another recurrent formula can be obtained from a study of Casimir
 elements action on irreducible highest weight modules
@@
 
-We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for computations in section \ref{sec:comp-algor}.
+We discuss the use of formulae \eqref{eq:14} and \eqref{eq:15} for the computations in section \ref{sec:comp-algor}.
 
@@
 Each irreducible $\gf$-module is also an $\af$-module, although
-$L^{\mu}_{\gf}$ is in general not irreducible as $\af$-module. 
+$L^{\mu}_{\gf}$ is in general not irreducible as an $\af$-module. 
 It can be
@@
 \end{equation}
-Coefficients in such a decomposition are called branching
-coefficients.
+The coefficients this decomposition are called branching coefficients.
 
@@
 For a subalgebra $\af\subset \gf$ we introduce the subalgebra
-$\afb$. Consider the root subspace $\hf_{\perp \af}^{\ast }$
+$\afb$. Consider a root subspace $\hf_{\perp \af}^{\ast }$
 orthogonal to $\hf_{\af}$,
@@
 and the roots (correspondingly -- positive roots) of $\gf$ orthogonal
-to roots of $\af$,
+to the roots of $\af$,
 \begin{eqnarray}

### 2012-06-17 doc/paper.tex
Grammar

@@
 Using definition \eqref{eq:8} it is easy to see that $s_{\alpha}s_{\alpha+\delta} \cdot \lambda=\lambda+\frac{2}{(\alpha,\alpha)}\alpha+\left(\frac{(\alpha,\alpha)}{2 (\lambda,\delta)}+(\lambda,\alpha)\right) \delta$.
-So the Weyl group $W_{\gfh}$ can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to the roots of $\gf$.
+So the Weyl group $W_{\hat\gf}$ can be presented as a semidirect product of the Weyl group $W_{\gf}$ of $\gf$ and the set of translations corresponding to the roots of $\gf$.
 
@@
 Let $W_{\afb}$ be a subgroup of $W$ generated by
-reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
+the reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\af_{\perp
 }}^{+}$. The subsystem $\Delta _{\afb}$ determines a 
@@
 
-Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients.
-If $\xi\in \bar C_{\af}$ is in main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$ otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
+Denote by  $k_{\xi }^{\left( \mu \right) }$ signed branching coefficients defined as follows.
+If $\xi\in \bar C_{\af}$ is in the main Weyl chamber $k_{\xi}^{(\mu)}=b^{(\mu)}_{\xi}$, otherwise $k_{\xi}^{(\mu)}=\epsilon(w) b^{(\mu)}_{w (\xi+\rho_{\af})-\rho_{\af}}$ where $w\in W_{\af}$ is such that $w (\xi+\rho_{\af})-\rho_{\af}\in \bar C_{\af}$.
 
 Now we can use the Weyl character formula to write a
-recurrent relation \cite{2010arXiv1007.0318L} for signed branching
+recurrent relation \cite{2010arXiv1007.0318L} for the signed branching
 coefficients $k_{\xi }^{\left( \mu \right) }$ corresponding to an
@@
 \end{equation}
-Formula (\ref{eq:14}) is a particular case of recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of Cartan subalgebra $\af=\hfg$.
+The formula (\ref{eq:14}) is a particular case of the recurrent relation for branching coefficients (\ref{recurrent-rel}) in the case of a Cartan subalgebra $\af=\hfg$.
 
@@
 \end{equation}
-The coefficients $f^{\mu\nu}_{\gamma}$ are called fusion
+The coefficients $f^{\mu\nu}_{\gamma}$ are called the fusion
 coefficients. The problem of computation of fusion coefficients is
-equivalent to branching problem for the diagonal subalgebra
-$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
-
-In the case of affine Lie algebras $\gf, \af$  the multiplicities
-$m_{\nu}$ and the corresponding branching coefficients $b_{\nu}$
-can be regarded as the coefficients in power series decomposition
+equivalent to a branching problem for the diagonal subalgebra
+$\gf\subset \gf\oplus \gf$ (see \cite{LyakhovskyPostnova2011}). So our implementation of a recurrent algorithm can be used to decompose tensor products (See Section \ref{sec:tens-prod-decomp}).
+
+In a case of affine Lie algebras $\gf, \af$  the multiplicities
+$m_{\nu}$ and the branching coefficients $b^{(\mu)}_{\nu}$
+can be regarded as the coefficients in the power series decomposition
 of string and branching functions correspondingly:
@@
 We present examples of computations in Sections \ref{sec:string-funct-affine}, \ref{sec:branch-funct-coset}.
-Now we proceed to the description of datastructures and algorithms implemented in {\bf Affine.m}.
+Now we proceed to the description of the datastructures and the algorithms implemented in {\bf Affine.m}.
 
@@
 Mathematica} is untyped language it is possible to create
-structured objects and do type checks with patterns
+structured objects and do the type checks with patterns
 \cite{shifrinmathematica}, \cite{maeder2000computer}.
@@
 
-Weights are represented  by two data-structures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.
+Weights are represented  by two datastructures: \lstinline{finiteWeight} for finite-dimensional Lie algebras and \lstinline{affineWeight}  for affine.
 
@@
 
-Affine weight is an extension of a finite weight by supplying it
-with level and grade coordinates. There is a set of functions
+An affine weight is an extension of a finite weight by supplying it
+with the level and grade coordinates. There is a set of functions
 defined for finite and affine weights. The complete list can be
-found in  online help of the package. The most important
-are definitions of addition, multiplication by a number and a
+found in the  online help of the package. The most important
+are the definitions of an addition, a multiplication by a number and a
 scalar product (bilinear form) for weights. These definitions
-allow to use traditional notation when working with {\bf
-Affine.m}:
+allow us to use a traditional notation with {\bf Affine.m}:
 \begin{lstlisting}
@@
 
-The use of orthogonal basis in the internal structure of weights allows us to work with weights without complete specification of root system which is useful for study of branching, since roots of the subalgebra can be specified by hand.
+The use of an orthogonal basis in the internal structure of weights allows us to work with weights without a complete specification of a root system which is useful for a study of branching, since the roots of the subalgebra can be specified by hand.
 
@@
 \end{lstlisting}
-We use typographic features of {\it Mathematica} frontend to offer mathematical notation for simple Lie algebras:
+We use the typographic features of the {\it Mathematica} frontend to offer a mathematical notation for simple Lie algebras:
 
@@
 
-Non-twisted affine root systems can be created as affine extensions of finte root systems, e.g.
+Non-twisted affine root systems can be created as the affine extensions of finte root systems, e.g.
 \begin{lstlisting}
@@
 \end{lstlisting}
-In notebook interface this can be written simply as $\hat{B}_2$.
-
-Semisimple Lie algebras can be created as sums of simple:
+In the notebook interface this can be written simply as $\hat{B}_2$.
+
+Semisimple Lie algebras can be created as the sums of simple ones:
 \begin{lstlisting}[mathescape=true]
@@
 
-Predicate \lstinline{rootSystemQ} checks if the object is root systems of finite or affine type.
-
-List of simple roots is the property of root system so it is accessed as \lstinline{rs[simpleRoots]}.
-
-We have implemented several functions to get major properties of root systems. Weyl vector is given by the function \lstinline{rho[rs_?rootSystemQ]}:
+The predicate \lstinline{rootSystemQ} checks if the object is a root systems of finite or affine type.
+
+The list of simple roots is the property of root system so it is accessed as the field \lstinline{rs[simpleRoots]}.
+
+We have implemented several functions to get major properties of root systems. Weyl vector is computed by the function \lstinline{rho[rs_?rootSystemQ]}:
 \begin{lstlisting}[label=list:1]
@@
 \end{lstlisting}
-Positive roots can be constructed with \lstinline{positiveRoots[rs_?rootSystemQ]}.
-For an affine Lie algebra this and related functions return the list up to fixed grade.
-This grade limit is set through the value of \lstinline{rs[gradeLimit]} which is equal to 10 by default.
-List of roots (up to \lstinline{gradeLimit}) is returned by \lstinline{roots[rs]}.
-Cartan matrix and fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
+The list of positive roots can be constructed with the function \lstinline{positiveRoots[rs_?rootSystemQ]}.
+For an affine Lie algebra this and related functions return the list up to some fixed grade.
+This grade limit is set as the value of the field \lstinline{rs[gradeLimit]} which is equal to 10 by default.
+The list of roots (up to \lstinline{gradeLimit}) is returned by the function \lstinline{roots[rs]}.
+Cartan matrix and the fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
 
@@
 \end{lstlisting}
-The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of weight \lstinline{wg} in the root system \lstinline{rs}.
-
-Elements of Weyl group are specified by the set of indices of reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
+The function \lstinline{dynkinLabels[rs_?rootSystemQ][wg_?weightQ]} returns Dynkin labels of a weight \lstinline{wg} in the root system \lstinline{rs}.
+
+An element of the Weyl group can be specified by the set of the indices of the reflections, so the element  $w=s_{1}s_{2}s_{1}$ of the Weyl group of algebra $B_{2}$ is constructed with \lstinline{weylGroupElement[b2][1,2,1]}.
 Then it can be applied to the weights:
@@
 
-Computation of lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for Weyl group elements can be conveniently implemented through the use of pattern-matching in {\it Mathematica}.
-In \cite{KallenShortlex} rewrite rules for simple finite dimensional and affine Lie algebras are presented as {\it Mathematica} patterns.
-Our presentation of Weyl group elements is compatible with the code of \cite{KallenShortlex}
+A computation of a lexicographically minimal form \cite{casselman1994machine,casselman1995automata} for the Weyl group elements can be conveniently implemented using pattern-matching in {\it Mathematica}.
+In \cite{KallenShortlex} the rewrite rules for simple finite dimensional and affine Lie algebras are presented as the {\it Mathematica} patterns.
+Our presentation of the Weyl group elements is compatible with the code of \cite{KallenShortlex}:
 \begin{lstlisting}[mathescape=true]
@@
 
-We represent formal characters of representations by special structure \lstinline{formalElement}.
+We represent the formal characters of modules by a special structure \lstinline{formalElement}.
+The constructor \lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
+creates a datastructure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$.
 This structure is a hash-table implemented with \lstinline{DownValues}.
 The keys are weights at the exponents and the values are the  corresponding multiplicities.
-\lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
-creates data-structure which represents the element $\sum_{i=1}^{n} m_{i} e^{\gamma_{i}}$ of the formal algebra $\mathcal{E}$.
-The operations in $\mathcal{E}$ are implemented for \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight.
+The operations in $\mathcal{E}$ are implemented for the \lstinline{formalElement} data-type: formal elements can be added, multiplied by a number or by an exponent of a weight.
 There exists also a multiplication of formal elements but no division.
@@
 Verma modules, irreducible modules and parabolic Verma modules.
-We need datastructure \lstinline{module} to represent generic module of Lie algebra $\gf$.
-Module properties can be deduced from its set of singular weights using Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
-Set of singular weights can have Weyl symmetry.
-It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subalgebra $W_{\af}$ as in the case of parabolic Verma modules.
+We need the datastructure \lstinline{module} to represent a generic module of a Lie algebra $\gf$.
+Module properties can be deduced from its set of singular weights using the Weyl character formulae \eqref{eq:11},\eqref{eq:12},\eqref{eq:18},\eqref{eq:13}.
+A set of singular weights can have Weyl symmetry.
+It can be a symmetry with respect to the Weyl group $W_{\gf}$ or with respect to some subgroup $W_{\af}$ as in the case of parabolic Verma modules.
 Then it is possible to study only the main Weyl chamber $C_{\af}$.
-To use this symmetry generic constructor for \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
-Here \lstinline{rs} is the root system of the Lie algebra $\gf$,\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights.
-Parameter \lstinline{limit} limits computation for infinite-dimensional modules such as Verma or parabolic Verma.
+To use this symmetry a generic constructor for the \lstinline{module} datastructure accepts several parameters \lstinline{makeModule[rs_?rootSystemQ][singWeights_formalElement,subs_?rootSystemQ|emptyRootSystem[],limit:10}.
+Here \lstinline{rs} is the root system of a Lie algebra $\gf$, \;\lstinline{singWeights} is the set of singular weights,  \lstinline{subs} is the root system corresponding to the Weyl group $W_{\af}$ which is the (anti-)symmetry of the set of singular weights.
+The parameter \lstinline{limit} limits the computation for infinite-dimensional representations such as Verma or parabolic Verma modules.
 There are several specialized constructors for different types of highest weight modules:
@@
 
-As we already stated properties of a module are encoded by its singular element.
-Function \lstinline{singularElement[m_module]} returns singular element of a module as \lstinline{formalElement} datastructure.
-Character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}.
-Direct sum of modules is a module and we use natural notation
+As we have already stated the properties of a module are encoded by its singular element.
+The function \lstinline{singularElement[m_module]} returns the singular element of a module as a \lstinline{formalElement} datastructure.
+The character (up to \lstinline{limit} for (parabolic) Verma modules) is returned by the function \lstinline{character[m_module]}.
+A direct sum of modules is a module and we use natural notation
 \begin{lstlisting}[mathescape=true]
-im1=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
+In[1] := im1=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][2,1]];
          im2=makeIrreducibleModule[$B_{2}$][weight[$B_{2}$][1,2]];
-textPlot[im1$\oplus$ im2]
+         Head[im1$\oplus$ im2]
+Out[1] = module
+In[2] := textPlot[im1$\oplus$ im2]
 $\includegraphics[width=60mm]{figures/irrep-sum.pdf}$
@@
 
-The tensor product is also implemented but only for the finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
+The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
 \begin{lstlisting}[mathescape=true]
@@
 
-As we have already stated in section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules.
+As we have already stated in the section \ref{sec:high-weight-modul} there exist two recurrent relations which can be used to calculate weight multiplicities in irreducible modules.
 Both algorithms proceed in the following way to calculate weight multiplicities:
@@
 \item Sort the list of weights by their product with the Weyl vector.
-\item Use a recurrent formula. If the weight required for recurrent computation is outside the main chamber use the Weyl symmetry.
+\item Use a recurrent formula. If the weight required for the recurrent computation is outside the main chamber use the Weyl symmetry.
 \end{enumerate}
-The difference in the performance of algorithms is in the number of previous values required to get the multiplicity of weight under consideration.
-For  the Weyl formula based recurrent relation \eqref{eq:14} it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
-When the Freudenthal formula \eqref{eq:15} is used number of previous values grows with the distance from the external border of representation.
+The difference in the performance of algorithms comes from the number of previous values required to compute the multiplicity of a weight under consideration.
+For  the  recurrent relation \eqref{eq:14} based on the Weyl formula it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
+When the Freudenthal formula \eqref{eq:15} is used the number of the previous values grows with the distance from the external border of representation.
 So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
-Note that the Freudenthal formula is valid for irreducible modules only, so it can not be used to study (generalized) Verma modules.
-
-We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and have got Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
+Note that the Freudenthal formula is valid for the irreducible modules only, so it can not be used to study (generalized) Verma modules.
+
+We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and prepared the Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
 
@@
   }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{eq:14} (solid) with the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
+  \caption{The dependence of the running time of the algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and the recurrent relation \eqref{eq:14} (solid) on the number of weights in $\bar C$ for calculation of multiplicities in representations of $B_{2}$.}
 \label{fig:freudenthal-racah-times}
@@
 
-In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of formal characters of an algebra module and all the representations of a subalgebra.
-It is impractical when the rank of algebra and subalgebra are big, for example for maximal subalgebras.
-
-Alternative algorithm which was presented in the paper \cite{2010arXiv1007.0318L}  contains the following steps:
+In the calculation of branching coefficients the application of the Freudenthal formula requires a complete construction of the formal characters of an algebra module and all the representations of a subalgebra.
+It is impractical if the ranks of an algebra and a subalgebra are big, for example for the maximal subalgebras.
+
+An alternative algorithm was presented in the paper \cite{2010arXiv1007.0318L}. It contains the following steps:
 
 \begin{enumerate}
-\item  Construct the root system $\Delta _{\af}$ for the embedding $%
-\af\rightarrow \frak{g}$.
-
-\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal
-to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
-
-\item  Construct the set $\Gamma _{\af\rightarrow \frak{g}}$. Relation
- (\ref{eq:6}) defines the sign function
- $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$ where the lowest weight
- $\gamma_0$ is to be subtracted to get the fan:
+\item  Construct the root system $\Delta _{\af}$ for the an embedding $\af\rightarrow \gf$.
+\item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
+\item  Construct the set $\Gamma _{\af\rightarrow \gf}$. The relation (\ref{eq:6}) defines the sign function
+ $s(\gamma)$ and the set $\Phi_{\af\subset \frak{g}}$. The lowest weight
+ $\gamma_0$ is subtracted to get the fan:
  $\Gamma _{\af\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi _{%
@@
 \af_{\perp }}}}\right\} $. Since the set $\Delta_{\afb }^{+}$ is fixed
-we can easily check wether the weight $\mu _{\widetilde{\af_{\perp }}%
+we can easily check that the weight $\mu _{\widetilde{\af_{\perp }}%
 }\left( w\right) $ belongs to the main Weyl chamber $\overline{C_{\widetilde{%
 \af_{\perp }}}}$ (by computing its scalar product with the fundamental
-weights of $\afb^{+}$).
+weights of $\afb$).
 
@@
 
-\item  Calculate the anomalous branching coefficients using 
-recurrent relation (\ref{recurrent-rel}) and select among them those
+\item  Calculate the signed branching coefficients using 
+the recurrent relation (\ref{recurrent-rel}) and select among them those
 corresponding to the weights in the main Weyl
@@
 We can speed up the algorithm by
-one-time computation of the representatives of the conjugate classes $%
-W/W_{\afb }$.
+one-time computation of the representatives of conjugate classes $W/W_{\afb }$.
 
@@
 The required subset contains at most 48 elements.
-So the time for the construction of this required subset is negligible if the number of branching coefficients is greater than that.
-We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients and the number of elements in the fan.
-In the case of a direct algorithm we need to compute the multiplicities for each module in the decomposition, so the number of operations grows faster than the square of the number of elements in the main Weyl chamber of a subalgebra with non-zero branching coefficients.
-
-To further illustrate this performance issue we include Figure \ref{fig:branching} where we show the time required for computations of branching coefficients for $B_{3}\subset B_{4}$.
+The time for the construction of this required subset is negligible if the number of branching coefficients is greater than that.
+
+ We may estimate the total number of required operations for the computation of branching coefficients as the product of the number of elements with non-zero branching coefficients  in the main Weyl chamber of a subalgebra  and the number of elements in the fan.
+So we have a linear growth.
+If we use a direct algorithm we need to compute the multiplicities for each module in the decomposition.
+So the number of operations grows faster than the square of the number of elements with non-zero branching coefficients in the main Weyl chamber of a subalgebra.
+
+To illustrate this performance issue we present the Figure \ref{fig:branching} where we show the time required to compute the branching coefficients for $B_{3}\subset B_{4}$.
 
@@
   }
-  \caption{Running time of algorithms based on the Freudenthal formula \eqref{eq:15} (dashed) and recurrent relation \eqref{recurrent-rel} (solid) with the number of weights in $\bar C$ for calculation of branching coefficients for $B_{3}\subset B_{4}$.}
+  \caption{Dependence of the time required to compute branching coefficients for $B_{3}\subset B_{4}$ on  the number of weights in $\bar C$.
+Dashed line corresponds to the direct  algorithm based on the Freudenthal formula \eqref{eq:15}, solid one -- to the use of recurrent relation \eqref{recurrent-rel}.}
   \label{fig:branching}
@@
 \label{sec:examples}
-In this section we present some examples of computations available with {\bf Affine.m} with the code required to produce these results.
+In this section we present some examples of computations available with {\bf Affine.m} and the code required to produce these results.
 
@@
 For example, we can consider the spin of a composite system such as an atom.
-Another interesting example is integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
+Another interesting example is the integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
 In order to solve such a system, i.e.
-to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
-
-For fundamental representations of simple Lie algebras it is sometimes possible to get an analytic result describing the dependence of decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
-Our code provides numerical values and can be used to check this analytic results.
-
-Consider a tensor power of $B_{2}$ the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$. Decomposition coefficients are just the branching
+to find eigenstates of the Hamiltonian, we need to decompose $L^{\otimes N}$ into the direct sum of the irreducible $\gf$-modules of lower dimension and diagonalize the Hamiltonian on these modules.
+
+For the fundamental representations of simple Lie algebras it is sometimes possible to get an analytic formula for the dependence of the decomposition coefficients on $N$ (See \cite{LyakhovskyPostnova2011}).
+Our code provides the numerical values and can be used to check the analytic results.
+
+Consider for example a fourth tensor power the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$ of algebra $B_{2}$ . Decomposition coefficients are just the branching
  coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
@@
 
-Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing operator in space of dimension $625$ we can diagonalize operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
+Returning to the problem of spin chain Hamiltonian diagonalization we can see that instead of diagonalizing the operator in a space of dimension $625$ we can diagonalize the operators in the spaces of dimensions $55, 81, 30, 35, 35, 14, 10, 5, 1$.
 
@@
 
-We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of irreducible module $L^{[1,1]}_{G_{2}}$:
+We illustrate the generalized BGG-resolution by the diagrams of $G_{2}$ parabolic Verma modules which appear in the decomposition of the irreducible module $L^{[1,1]}_{G_{2}}$:
 \begin{equation}
@@
 \end{equation}
-The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, characters of the generalized Verma modules in decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
-Characters in the upper row appear in \eqref{char-in-gen-verma-mod} with positive sign and in the lower row -- with negative.
+The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, the characters of the generalized Verma modules in the decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
+The characters in the upper row appear in \eqref{char-in-gen-verma-mod} with a positive sign and in the lower row -- with a negative.
 
@@
   }
-  \caption{Characters of $G_{2}$ generalized Verma modules appearing in the decomposition of $L^{[1,1]}$.
-Parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
+  \caption{The characters  generalized Verma modules of $G_{2}$ appearing in the decomposition of $L^{[1,1]}$.
+The parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
   \label{g2-pverma}
@@
 
-String functions can be used to present formal characters of affine Lie algebra highest weight representation.
+String functions can be used to present a formal character of an affine Lie algebra highest weight representation.
 They have interesting analytic and modular properties \cite{kac1990idl,kac1988modular,kac1984infinite}.
@@
 
-It is believed that most rational models of CFT can be obtained from cosets $G/A$ corresponding to the embedding $\af\subset\gf$.
+It is believed that most rational models of CFT can be obtained from the cosets $G/A$ corresponding to the embedding $\af\subset\gf$.
 These models can be studied as gauge theories \cite{Hwang:1994yr, hwang1993brst}.
@@
 It can be used to study Weyl symmetry, root systems, irreducible, Verma and parabolic Verma modules of finite-dimensional and affine Lie algebras.
-In the present paper we have also discussed main ideas used for an implementation of the package and described the most important notions of representation theory required to use {\bf Affine.m}.
-
-We have demonstrated that recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
-
-Also we have presented examples of computations with this package connected with problems of physics and mathematics.
+In the present paper we have also discussed main ideas used for the implementation of the package and described the most important notions of representation theory required to use {\bf Affine.m}.
+
+We have demonstrated that the recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
+
+Also we have presented examples of computations connected with problems of physics and mathematics.
 

### 2012-06-17 doc/paper.tex
More grammar improvements.

@@
 %% Text of abstract
-In this paper we present {\bf Affine.m} -- a program for computations in representation theory of finite-dimensional and affine Lie algebras and describe the implemented algorithms.
+In this paper we present {\bf Affine.m} -- a program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
 The algorithms are based on the properties of weights and Weyl symmetry.
-The most important problems for us are the ones, concerning computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition.
+Computation of weight multiplicities in irreducible and Verma modules, branching of representations and tensor product decomposition are the most important problems for us.
 These problems have numerous applications in physics and we provide some examples of these applications.
@@
 \end{equation}
-Central extension leads to the appearance of an additional term
+The central extension leads to the appearance of an additional term
 \begin{equation}
@@
 \end{equation}
-A character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
-A character can be specialized by taking its value on some element $\xi$ of $\hf$.
+The character  $\mathrm{ch}V\in \mathcal{E}$ is an element of algebra $\mathcal{E}$ generated by formal exponents of weights.
+The character can be specialized by taking its value on some element $\xi$ of $\hf$.
 

### 2012-06-19 doc/paper.tex
Minor grammar change

@@
 
-A highest weight module $V^{\mu}$ contains a single highest weight $\mu$,  the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
+A highest weight module $V^{\mu}$ contains single highest weight $\mu$,  the other weights are obtained by subtractions of linear combinations of simple roots $\lambda=\mu-n_{1}\alpha_{1}-\dots-n_{r}\alpha_{r},\; n_{k}\in \mathbb{Z} _{+}$.
 

### 2012-08-08 doc/paper.tex
Paper source and PDF updated to match published version

--- 2012-06-17 doc/paper.tex
@@
 %% Text of abstract
-In this paper we present {\bf Affine.m} -- a program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
+In this paper we present {\bf Affine.m} --- a program for computations in representation theory of finite-dimensional and affine Lie algebras and describe implemented algorithms.
 The algorithms are based on the properties of weights and Weyl symmetry.
@@
   %Leave blank, supplied by Elsevier.
-{\em Catalogue identifier:}                                   \\
+{\em Catalogue identifier:}  AENA\textunderscore v1\textunderscore 0                                 \\
   %Leave blank, supplied by Elsevier.
-{\em Licensing provisions:}none                                   \\
+{\em Licensing provisions:}Standard CPC licence, \url{http://cpc.cs.qub.ac.uk/licence/licence.html}                                   \\
   %enter "none" if CPC non-profit use license is sufficient.
+
+{\em No. of lines in distributed program, including test data, etc.:} 24 844\\
+{\em No. of bytes in distributed program, including test data, etc.:} 1 045 908\\
+{\em Distribution format:} tar.gz\\
+
 {\em Programming language:}Mathematica                                   \\
@@
   %Computer(s) for which program has been designed.
-{\em Operating system:} Linux, Windows, MacOS, Solaris                                       \\
+{\em Operating system:} Linux, Windows, Mac OS, Solaris                                       \\
   %Operating system(s) for which program has been designed.
@@
 Central problems which are the computations of weight multiplicities, branching and fusion coefficients are solved using one general recurrent algorithm based on generalization of Weyl character formula.
-We also offer alternative implementation based on Freudenthal multiplicity formula which can be faster in some cases.
+We also offer alternative implementation based on the Freudenthal multiplicity formula which can be faster in some cases.
    \\
@@
   %Give an indication of the typical running time here.
-From seconds to days depending on the rank of an algebra and the complexity of a representation.
+From seconds to days depending on the rank of the algebra and the complexity of the representation.
    \\
@@
 There are well-known algorithms for these tasks \cite{moody1982fast}, \cite{stembridge2001computational}, \cite{belinfante1989survey}, \cite{casselman1994machine}.
-The third problem is the most computation-intensive.
+The third problem is the most computation intensive.
 There are two different recurrent algorithms which are based on the Weyl character formula and the Freudenthal multiplicity formula.
@@
 
-Infinite-dimensional Lie algebras also have growing number of applications in physics for example in conformal field theory and in a study of  integrable systems.
+Infinite-dimensional Lie algebras also have a growing number of applications in physics for example in conformal field theory and in a study of  integrable systems.
 But infinite-dimensional algebras are much harder to investigate and the number of available computer programs is much smaller in this case.
@@
 
-The structure of affine Lie algebras allows to adapt for them the computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
+The structure of affine Lie algebras allows us to adapt for them the computational algorithms created for finite-dimensional Lie algebras  \cite{Fuchs:1996dd}, \cite{gannon2001algorithms}, \cite{kass1990ala}.
 The book \cite{kass1990ala} with the tables of multiplicities and other computed characteristics of affine Lie algebras and representations was published in 1990.
 But we are not aware of software packages for popular computer algebra systems which can be used to extend these results.
-We address this issue and present {\bf Affine.m} -- {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
+We address this issue and present {\bf Affine.m} -- a {\it Mathematica} package for computations in representation theory of affine and finite-dimensional Lie algebras.
 We describe the features and limitations of the package in the present paper.
@@
 
-In this section we remind necessary definitions and present formulae used in computations.
+In this section we recall necessary definitions and present formulae used in computations.
 
@@
 \end{equation}
-This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
+This algebra $\hat\gf=\gf\otimes\mathbb{C}[t,t^{-1}]\oplus\mathbb{C}c$ is called a non-twisted {\it affine Lie algebra} \cite{kac1990idl}, \cite{wakimoto2001idl,wakimoto2001lectures}, \cite{kass1990ala}.
 
@@
 
-Then $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
+Then the $\gf$-module is a vector space $V$ together with a bilinear map $\gf \times V\to V$ such that
 \begin{equation}
@@
 The set of simple roots $\Phi=\left\{\alpha_{i}\right\}$ is a basis in $\hfg^{*}$ and each root can be written as $\alpha=\sum_{i}n_{i}\alpha_{i}$ with all $n_{i}$ non-negative or non-positive simultaneously.
-In case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
+In the case of a finite-dimensional Lie algebra $\gf$ simple roots are numbered from 1 to the rank of the algebra $i=1,\dots,r,\quad r=\mathrm{rank}(\gf)$.
 Enumerating simple roots with an index $i$ we introduce lexicographic ordering in the root system $\Delta$.
@@
 $\theta$ is also the highest weight  of the adjoint module (See section \ref{sec:high-weight-modul}).
-{\it Comarcs} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
+{\it Comarks} are the numbers equal to $a_i^{\vee}=\frac{(\alpha_i,\alpha_i)}{2} a_i$.
 
@@
 
-A {\it parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
+A {\it parabolic subalgebra}  $\pf_{I}\supset \bff_{+}$ contains a Borel subalgebra and is  generated by some subset of simple roots $\{\alpha_{j}:j\in I, I\subset \{1\dots r\}\}$.
 It is spanned by the subset of generators $\{H^{i}\}\cup \{E^{\alpha}:\alpha\in \Delta^{+}\}\cup \{E^{-\alpha}: \alpha\in\Delta^{+}, \alpha=\sum_{j\in I} n_{j} \alpha_{j}\}$.
@@
 \end{equation}
-Root system and characters of representation are invariant with respect to the Weyl group  action. A root system can be reconstructed from the set of simple roots by the Weyl group transformations.
-
-Weyl groups are finite for finite-dimensional Lie algebras and finitely-generated for affine Lie algebras.
+The root system and characters of representation are invariant with respect to the Weyl group  action.
+A root system can be reconstructed from the set of simple roots by the Weyl group transformations.
+
+Weyl groups are finite for finite-dimensional Lie algebras and finitely generated for affine Lie algebras.
 
@@
 For a finite-dimensional Lie algebra there are $r$ fundamental weights, $i=1,\dots, r$.
-For affine Lie algebra we have an additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
+For an affine Lie algebra we have an additional fundamental weight $\omega_0=\lambda$, $(\lambda,\delta)=1, \; (\lambda,\lambda)=(\delta,\delta)=0$.
 Other fundamental weights are equal to $\omega_i=a_i^v \omega_0 +\co{\omega_i}$, where $\co{\omega_i}$ is a fundamental weight of the finite-dimensional Lie algebra $\gf$.
@@
 
-We consider finitely-generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite-dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
+We consider finitely generated $\gf$-modules $V$ such that $V=\bigoplus_{\xi\in \hfg^{*}} V_{\xi}$, where each $V_{\xi}$ is finite dimensional and there exists a finite set of weights $\lambda_{1},\dots \lambda_{s}$ which generates the weight system of $V$, i.e.
 if $\mathrm{dim}V_{\xi}\neq 0$ then $\xi=\lambda_{i}-\sum_{k=1,\dots, r} n_{k}\alpha_{k}$ where $n_{k}\in \mathbb{Z}_{+}$ (See \cite{humphreys2008representations}, \cite{carter2005lie}).
@@
 
-The most simple type of highest weight modules is the Verma module
+The simplest type of highest weight modules is the Verma module
 $M^{\mu}$. Its space can be defined as a module
@@
 with respect to a multiplication in $U(\gf)$ and
-$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of tensor product onto the right part.
+$\underset{U(\bff_{+})}{\otimes}$ means that the action of elements of $U(\bff_{+})$ ``falls through'' the left part of the tensor product onto the right part.
 Here $\bff_{+}$ is the Borel subalgebra, $D^{\mu}(\bff_{+})$ is a representation of $\bff_{+}$ such that $D(E^{\alpha})=0,\; D(H)=\mu(H)$ for any positive root $\alpha$.
@@
 Formulae for Verma and generalized Verma modules differ only in the second term on the right-hand side.
-In case of Verma module it is just $\delta_{\xi,\mu}$.
+In the case of Verma module it is just $\delta_{\xi,\mu}$.
 For a generalized Verma module the summation in the second term on the right-hand side of \eqref{eq:14} is over the Weyl subgroup generated by the reflections corresponding to the roots $\{\alpha_{I}\}$.
@@
 Another recurrent formula can be obtained from a study of Casimir
-elements action on irreducible highest weight modules
+element action on irreducible highest weight modules
 \cite{humphreys1997introduction}:
@@
 relation (\ref{recurrent-rel}) is connected with the generalized
-Bernstein-Bernstein-Gelfand resolution for parabolic Verma modules
+Bernstein-Gelfand-Gelfand resolution for parabolic Verma modules
 \cite{2011arXiv1102.1702L}.
@@
 
-In a case of affine Lie algebras $\gf, \af$  the multiplicities
+In the case of affine Lie algebras $\gf, \af$  the multiplicities
 $m_{\nu}$ and the branching coefficients $b^{(\mu)}_{\nu}$
@@
 
-Non-twisted affine root systems can be created as the affine extensions of finte root systems, e.g.
+Non-twisted affine root systems can be created as the affine extensions of finite root systems, e.g.
 \begin{lstlisting}
@@
 
-The predicate \lstinline{rootSystemQ} checks if the object is a root systems of finite or affine type.
-
-The list of simple roots is the property of root system so it is accessed as the field \lstinline{rs[simpleRoots]}.
-
-We have implemented several functions to get major properties of root systems. Weyl vector is computed by the function \lstinline{rho[rs_?rootSystemQ]}:
+The predicate \lstinline{rootSystemQ} checks if the object is a root system of finite or affine type.
+
+The list of simple roots is a property of the root system so it is accessed as the field \lstinline{rs[simpleRoots]}.
+
+We have implemented several functions to get major properties of root systems. The Weyl vector is computed by the function \lstinline{rho[rs_?rootSystemQ]}:
 \begin{lstlisting}[label=list:1]
@@
 The list of roots (up to \lstinline{gradeLimit}) is returned by the function \lstinline{roots[rs]}.
-Cartan matrix and the fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
-
-It is possible to specify a weight of a Lie algebra by its Dynkin labels
+The Cartan matrix and the fundamental weights are calculated by the functions \lstinline{cartanMatrix} and \lstinline{fundamentalWeights} correspondingly.
+
+It is possible to specify the weight of a Lie algebra by its Dynkin labels
 \begin{lstlisting}
@@
 
-We represent the formal characters of modules by a special structure \lstinline{formalElement}.
+We represent formal characters of modules by a special structure \lstinline{formalElement}.
 The constructor \lstinline[mathescape=true]!makeFormalElement[{$\gamma_{1},\dots,\gamma_{n}$},{$m_{1},\dots,m_{n}$}]!
@@
 
-The tensor product is also implemented but only for finite-dimensional Lie algebras, since tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
+The tensor product is also implemented but only for finite-dimensional Lie algebras, since the tensor product of affine Lie algebra modules leads to rich new structures \cite{kazhdan1994tensor3,kazhdan1993tensor1,kazhdan1993tensor2} which are out of the scope of the present paper.
 \begin{lstlisting}[mathescape=true]
@@
 The difference in the performance of algorithms comes from the number of previous values required to compute the multiplicity of a weight under consideration.
-For  the  recurrent relation \eqref{eq:14} based on the Weyl formula it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of representation diagram).
-When the Freudenthal formula \eqref{eq:15} is used the number of the previous values grows with the distance from the external border of representation.
-So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of Weyl group is large \cite{moody1982fast}.
+For  the  recurrent relation \eqref{eq:14} based on the Weyl formula it is constant and equal to the number of elements in the Weyl group (if we are far from the boundary of the representation diagram).
+When the Freudenthal formula \eqref{eq:15} is used the number of previous values grows with the distance from the external border of representation.
+So the Freudenthal formula is faster if the weight is close to the border or the rank of the algebra and the size of the Weyl group is large \cite{moody1982fast}.
 Note that the Freudenthal formula is valid for the irreducible modules only, so it can not be used to study (generalized) Verma modules.
 
-We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and prepared the Figure  \ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
+We have made some experiments with our implementations of the Freudenthal formula and formula \eqref{eq:15} and prepared the Fig.
+\ref{fig:freudenthal-racah-times}, which depicts the dependence of the computation time on the number of weights in a module.
 
@@
 \begin{enumerate}
-\item  Construct the root system $\Delta _{\af}$ for the an embedding $\af\rightarrow \gf$.
+\item  Construct the root system $\Delta _{\af}$ for an embedding $\af\rightarrow \gf$.
 \item  Select all the positive roots $\alpha \in \Delta ^{+}$ orthogonal to  $\af$, i.e. form the set $\Delta_{\afb }^{+}$.
@@
   \caption{Dependence of the time required to compute branching coefficients for $B_{3}\subset B_{4}$ on  the number of weights in $\bar C$.
-Dashed line corresponds to the direct  algorithm based on the Freudenthal formula \eqref{eq:15}, solid one -- to the use of recurrent relation \eqref{recurrent-rel}.}
+The dashed line corresponds to the direct  algorithm based on the Freudenthal formula \eqref{eq:15}, the solid one to the use of recurrent relation \eqref{recurrent-rel}.}
   \label{fig:branching}
@@
 
-Computation of fusion coefficients for the decomposition of tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
+Computation of fusion coefficients for decomposition of the tensor product of highest-weight modules to the direct sum of irreducible modules has numerous applications in physics.
 For example, we can consider the spin of a composite system such as an atom.
-Another interesting example is the integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing the nearest-neighbour spin-spin interaction.
+Another interesting example is the integrable spin chain consisting of $N$ particles with the spins living in some representation $L$ of a Lie algebra $\gf$ with a $\gf$-invariant Hamiltonian $H$, describing nearest-neighbour spin-spin interaction.
 In order to solve such a system, i.e.
@@
 
-Consider for example a fourth tensor power the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$ of algebra $B_{2}$ . Decomposition coefficients are just the branching
+Consider for example a fourth tensor power of the first fundamental representation $\left(L^{[1,0]}\right)^{\otimes 4}$ of algebra $B_{2}$ . Decomposition coefficients are just the branching
  coefficients for the tensor power module reduced to the diagonal subalgebra $B_{2}\subset B_{2}\oplus B_{2}\oplus B_{2}\oplus B_{2}$. So the following code calculates these coefficients:
@@
 The character of $L^{[1,1]}$ is presented in Figure \ref{branching-bgg}, the characters of the generalized Verma modules in the decomposition \eqref{char-in-gen-verma-mod} are shown in Figure \ref{g2-pverma}.
-The characters in the upper row appear in \eqref{char-in-gen-verma-mod} with a positive sign and in the lower row -- with a negative.
+The characters in the upper row appear in \eqref{char-in-gen-verma-mod} with a positive sign and in the lower row with a negative.
 
@@
   }
-  \caption{The characters  generalized Verma modules of $G_{2}$ appearing in the decomposition of $L^{[1,1]}$.
-The parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in the lower row -- with a negative.}
+  \caption{The characters of  generalized Verma modules of $G_{2}$ appearing in the decomposition of $L^{[1,1]}$.
+The parabolic Verma modules in the upper row appear in the decomposition with a positive sign, in  lower row with a negative.}
   \label{g2-pverma}
@@
 
-We have demonstrated that the recurrent approach based on the Weyl character formula is not only useful for calculations but also allows to establish connections with the (generalized) Bernstein-Bernstein-Gelfand resolution.
+We have demonstrated that the recurrent approach based on the Weyl character formula is not only useful for calculations but also allows us to establish connections with the (generalized) Bernstein-Gelfand-Gelfand resolution.
 

### 2013-02-20 src/affine.m
Added generic simple branching function and minimalCharacters function to compute Virasoro characters in minimal CFT

@@ -199,6 +199,10 @@ marks::"usage"="marks[rs_affineRootSystem] returns marks of affine Lie algebra";
 
 comarks::"usage"="comarks[rs_affineRootSystem] returns comarks of affine Lie algebra";
 
+coxeterNumber::"usage"="returns Coxeter number for root system of Lie algebra";
+
+dualCoxeterNumber::"usage"="returns dual Coxeter number for root system of Lie algebra";
+
 weight::"usage"=
     "weight[rs_?rootSystemQ][labels__Integer] constructs weight defined by Dynkin labels";
 
@@ -345,6 +349,16 @@ branchingFunctions::"usage"="branchingFunctions[rs_affineRootSystem,subs_affineR
 
 textPlot::"usage"=
     "textPlot[m_module] plots module multiplicities";
+
+genericBranching::"usage"=
+    "genericBranching[subs_?rootSystemQ, pr_, {ms__module}] calculates branching coefficients of projection pr_ of direct product of modules ms__\n to irreducible modules of algebra with root system subs_";
+
+
+conformalWeight::"usage"=
+    "conformalWeight[rs_affineRootSystem][ls__?NumericQ] calculates conformal weight of primary field of WZNW model labeled by Dynkin labels";
+
+minimalCharacters::"usage"=
+    "minimalCharacters[{ls1__},{ls2__}] computes characters in su(2) x su(2)/su(2) minimal model for modules specified by Dynkin labels ls1__ and ls2__";
 
 Begin["`Private`"]
 
@@ -613,6 +627,7 @@ freudenthalMultiplicities[rs_?rootSystemQ][highestWeight_?weightQ]:=
 orbitWithEps[rs_?rootSystemQ][weight_?weightQ]:=Flatten[MapIndexed[Function[{x,i},Map[{#,(-1)^(i[[1]]+1)}&,x]],orbit[rs][weight]],1];
 
 racahMultiplicities[rs_?rootSystemQ][highestWeight_?weightQ]:=
+    racahMultiplicities[rs][highestWeight]=
     Module[{rh=rho[rs],weights,mults,c,insideQ,
 	    fan,
[…]

### 2013-02-20 src/affine.m
ourBranching[{ms__module},...] works for diagonal embedding

@@ -797,10 +797,10 @@ simpleBranching[rs_?rootSystemQ,subs_?rootSystemQ][highestWeight_?weightQ]:=
 singularElement[rs_?rootSystemQ][hweight_?weightQ]:=
     makeFormalElement @@ Transpose[{#[[1]]-rho[rs],#[[2]]}& /@ orbitWithEps[rs][hweight+rho[rs]]]
 
-fan[rs_?rootSystemQ,subs_?rootSystemQ]:=
-    Module[{pr,r,roots,ei},
-	   ei=embeddingIndex[rs,subs];
-	   roots=Select[projection[subs][positiveRoots[rs],ei],#=!= zeroWeight[subs]&];
+
+fan[{posroots__?weightQ},subs_?rootSystemQ]:=
+    Module[{pr,r,roots},
+	   roots=Select[{posroots},#=!= zeroWeight[subs]&];
 	   pr=makeFormalElement[roots] - makeFormalElement[positiveRoots[subs]];
 	   r=makeFormalElement[{zeroWeight[subs]}];
 	   Scan[Function[w,
@@ -809,6 +809,9 @@ fan[rs_?rootSystemQ,subs_?rootSystemQ]:=
 			],
 		pr[weights]];
 	   r];
+
+fan[rs_?rootSystemQ,subs_?rootSystemQ]:=fan[projection[subs][positiveRoots[rs]],subs];
+
 (*	   r=Fold[Expand[#1*(1-Exp[#2])^(pr[#2])]&,makeFormalElement[{zeroWeight[subs]}],pr[weights]];
 	   subElement[r,Select[r[weights],checkGrade[rs]]]];*)
 (* !!!!!!!!!!!!!!!!!!!!!                      ^^^^^^^^ This can be negative *)
@@ -1074,6 +1077,43 @@ ourBranching[m_module,subs_?rootSystemQ]:=
 	   makeFormalElement[keys[res],values[res]]
 	  ]
 
+ourBranching[{ms__module},subs_?rootSystemQ,proj_]:=
+    Module[{singW,selW,selWM,fn,reprw,res,toFC,rh,subrh,gamma0,sgamma0,hw,posroots,zeroes,singElts,smults},
+	   zeroes=zeroWeight[rootSystem[#]]&/@{ms};
+	   posroots=Flatten[MapIndexed[ (Map[ Function[x, proj@@ReplacePart[zeroes,#2->x]], 
[…]

### 2013-02-20 src/affine.m
decomposition now supports affine Lie algebra modules

@@ -1023,9 +1023,12 @@ affineRootSystem/:CirclePlus[x_affineRootSystem,y_affineRootSystem]:=makeAffineE
 
 CircleTimes[m1_module,m2_module]=tensorProduct[m1,m2];
 
-decomposition[m__module]:=ourBranching[Fold[tensorProduct,First[{m}],Rest[{m}]],
+
+decompositionOld[m__module]:=ourBranching[Fold[tensorProduct,First[{m}],Rest[{m}]],
 						    makeFiniteRootSystem[1/Length[{m}]*Fold[Plus,0,simpleRoots[rootSystem[#]]&/@{m}]]]
-					     
+
+
+decomposition[m__module]:=ourBranching[{m},rootSystem[First[{m}]],Plus]
 					     
 
 embeddingIndex[rs_?rootSystemQ,subs_?rootSystemQ]:=

### 2013-02-20 src/affine.m
Misprint fixed

@@ -378,7 +378,7 @@ finiteWeight/:x_finiteWeight[standardBase]:=x[[2]];
 finiteWeight/:x_finiteWeight[finitePart]:=x;
 
 finitePart[wg_?weightQ]=wg[finitePart];
-imension[wg_?weightQ]=wg[dimension];
+dimension[wg_?weightQ]=wg[dimension];
 standardBase[wg_?weightQ]=wg[finitePart][standardBase];
 
 (*makeFiniteWeight[{coordinates__?NumericQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}*)

### 2013-02-20 src/affine.m
Misprint fixed

@@ -364,7 +364,7 @@ finiteWeight/:x_finiteWeight[standardBase]:=x[[2]];
 finiteWeight/:x_finiteWeight[finitePart]:=x;
 
 finitePart[wg_?weightQ]=wg[finitePart];
-imension[wg_?weightQ]=wg[dimension];
+dimension[wg_?weightQ]=wg[dimension];
 standardBase[wg_?weightQ]=wg[finitePart][standardBase];
 
 (*makeFiniteWeight[{coordinates__?NumericQ}]:=finiteWeight @@ {Length[{coordinates}],{coordinates}}*)

### 2013-02-21 demo/g2-a2.m
New demo

@@ -1,0 +1,69 @@
+AppendTo[$Path,$InitialDirectory <> "/../src/"];
+<<affine.m;
+
+
+g2a = makeAffineExtension[makeSimpleRootSystem[G,2]];
+g2=makeSimpleRootSystem[G,2];
+rts=Extract[Select[positiveRoots[g2],#.#==2&],{{1},{2}}];
+a2a = makeAffineExtension[makeFiniteRootSystem[rts]];
+a2a[gradeLimit]=5;
+g2a[gradeLimit]=5;
+hw=weight[g2a][0,1,0];
+rtv1=simpleBranching[makeIrreducibleModule[g2a][hw],a2a];
+zg=Select[rtv1[weights],grade[#]==0&];
+{dynkinLabels[a2a][#],conformalWeight[g2a][hw]-conformalWeight[a2a][#],Affine`Private`stringSelector[rtv1,#,15]}&/@zg
+
+                                                                                 
+                      2               2      3      4      5
+Out[20]= {{{1, 0, 0}, -, 1 + 2 q + 2 q  + 4 q  + 5 q  + 8 q }, 
+                      5
+ 
+                 1              2      3      4      5
+>    {{0, 1, 0}, --, 1 + q + 2 q  + 3 q  + 5 q  + 7 q }, 
+                 15
+ 
+                 1              2      3      4      5
+>    {{0, 0, 1}, --, 1 + q + 2 q  + 3 q  + 5 q  + 7 q }}
+                 15
+
+
+a2a=makeAffineExtension[makeSimpleRootSystem[A,2]];
+a2a[gradeLimit]=5;
+hw1=weight[a2a][0,1,0];
+hw2=weight[a2a][0,1,0];
+rtv1=branching[{makeIrreducibleModule[a2a][hw1],makeIrreducibleModule[a2a][hw2]},a2a,Plus];
+zg=Select[rtv1[weights],grade[#]==0&];
+{dynkinLabels[a2a][#],conformalWeight[a2a][hw1]+conformalWeight[a2a][hw2]-conformalWeight[a2a][#],Affine`Private`stringSelector[rtv1,#,15]}&/@zg
+
+                                                      
+                              2      3      4      5      6
+Out[21]= {{{0, 2, 0}, 0, 1 + q  + 2 q  + 3 q  + 4 q  + 5 q }, 
+ 
+                 2               2      3      4      5       6
[…]

### 2013-02-21 src/affine.m
Support for diagonal coset models extended

@@ -357,6 +357,9 @@ genericBranching::"usage"=
 conformalWeight::"usage"=
     "conformalWeight[rs_affineRootSystem][ls__?NumericQ] calculates conformal weight of primary field of WZNW model labeled by Dynkin labels";
 
+centralCharge::"usage"=
+    "centralCharge[rs_affineRootSystem][level_?NumericQ] calculates central charge of WZNW model of given level";
+
 minimalCharacters::"usage"=
     "minimalCharacters[{ls1__},{ls2__}] computes characters in su(2) x su(2)/su(2) minimal model for modules specified by Dynkin labels ls1__ and ls2__";
 
@@ -1071,7 +1074,6 @@ ourBranching[m_module,subs_?rootSystemQ]:=
 	   res=makeHashtable[reprw,Table[0,{Length[reprw]}]];
 	   insideQ:=NumericQ[res[toFC[#][[1]]]]&;
 	   Scan[Function[v,
-(*			 Print[v];*)
 			 res[v]=-1/sgamma0*(
 			     -selWM[v-gamma0]+
 			     Plus@@(fn[weights] /. x_?weightQ :> If[insideQ[v+x],fn[x]*res[toFC[v+x][[1]]]*toFC[v+x][[2]],0]));
@@ -1081,14 +1083,16 @@ ourBranching[m_module,subs_?rootSystemQ]:=
 	  ]
 
 ourBranching[{ms__module},subs_?rootSystemQ,proj_]:=
-    Module[{singW,selW,selWM,fn,reprw,res,toFC,rh,subrh,gamma0,sgamma0,hw,posroots,zeroes,singElts,smults},
+    Module[{singW,selW,selWM,fn,reprw,res,toFC,rh,subrh,gamma0,sgamma0,hw,posroots,zeroes,singElts,smults,orth},
 	   zeroes=zeroWeight[rootSystem[#]]&/@{ms};
 	   posroots=Flatten[MapIndexed[ (Map[ Function[x, proj@@ReplacePart[zeroes,#2->x]], 
 					      positiveRoots[rootSystem[#1]]])&,
 					{ms}],1];
 (*	   orth=orthogonalSubsystem[rs,subs]; No orthogonal subsystem here *)
 
-	   singElts = singularElement /@ {ms};
+	   singElts = MapIndexed[extendSingularElement[singularElement[#1],
[…]

### 2013-06-25 src/affine.m
Fixed bug in F4 and E6-8 root systems, added tests. Tests for A1 fixed for the new normalization 1/Sqrt[2]

@@ -478,9 +478,9 @@ makeSimpleRootSystem[C,rank_Integer]:=makeFiniteRootSystem[Append[Table[If[i==j,
 makeSimpleRootSystem[D,rank_Integer]:=makeFiniteRootSystem[Append[Table[If[i==j,1,If[i==j-1,-1,0]],{i,1,rank-1},{j,1,rank}],Append[Append[Table[0,{rank-2}],1],1]]];
 makeSimpleRootSystem[E,rank_Integer]/; (rank>=3) && (rank<=8) :=makeFiniteRootSystem[Join[{1/2*{1,-1,-1,-1,-1,-1,-1,1},
 								   {1,1,0,0,0,0,0,0}},
-								  Table[If [ j==i-2, 1, If [j==i-1, -1, 0]],{i,3,rank},{j,1,8}]]];
+								  Table[If [ j==i-2, -1, If [j==i-1, 1, 0]],{i,3,rank},{j,1,8}]]];
 
-makeSimpleRootSystem[F,4]:=makeFiniteRootSystem[{{1,-1,0,0},{0,1,-1,0},{0,0,1,0},1/2*{1,-1,-1,-1}}];
+makeSimpleRootSystem[F,4]:=makeFiniteRootSystem[{{0,1,-1,0},{0,0,1,-1},{0,0,0,1},1/2*{1,-1,-1,-1}}];
 makeSimpleRootSystem[G,2]:=makeFiniteRootSystem[{1/Sqrt[3]*{1,-1,0},1/Sqrt[3]*{-2,1,1}}];
 							   
 (*

### 2013-06-25 doc/paper.tex
Paper source and PDF updated to latest arXiv version (v2).

--- 2012-08-08 doc/paper.tex
@@
 {\em Program Title:}Affine.m                                          \\
-{\em Journal Reference:}                                      \\
-  %Leave blank, supplied by Elsevier.
 {\em Catalogue identifier:}  AENA\textunderscore v1\textunderscore 0                                 \\
@@
 {\em Licensing provisions:}Standard CPC licence, \url{http://cpc.cs.qub.ac.uk/licence/licence.html}                                   \\
-  %enter "none" if CPC non-profit use license is sufficient.
-
 {\em No. of lines in distributed program, including test data, etc.:} 24 844\\ 
@@
 {\em Distribution format:} tar.gz\\
-
 {\em Programming language:}Mathematica                                   \\
